### 2018-09-23 docs/rupee.tex
nar tex files

\documentclass[a4,center,fleqn]{NAR}

\usepackage{lmodern}

% Enter dates of publication
\copyrightyear{2018}
\pubdate{?? ?????? ????}
\pubyear{????}
\jvolume{??}
\jissue{??}

%\articlesubtype{This is the article type (optional)}

\begin{document}

\title{Article title}

\author{%
Corresponding Author\,$^{1,*}$,
First Co-Author\,$^{2}$
and Second Co-Author\,$^2$%
\footnote{To whom correspondence should be addressed.
Tel: +44 000 0000000; Fax: +44 000 0000000; Email: xxx@yyyy.ac.zz}}

\address{%
$^{1}$Affiliation of Corresponding Author
and
$^{2}$Affiliation of Both Co-Authors}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

\history{%
Received ?????? ??, ????;
Revised ?????? ??, ????;
Accepted ?????? ??, ????}

\maketitle

\begin{abstract}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.
\end{abstract}

\section{Introduction}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
\begin{align*}
&\mathrm{Ascorbate} + \mathrm{EDTA} \cdot \mathrm{Fe}^{3+} \to
\hbox{Oxidized ascorbate}
\\
&\mathrm{EDTA} \cdot \mathrm{Fe}^{2+} + \mathrm{H}_2
\mathrm{O}_2 \to
\mathrm{EDTA} \cdot \mathrm{Fe}^{3+} + \cdot
\mathrm{OH} + \mathrm{OH}^-
\end{align*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text.
Text.

\section{MATERIALS AND METHODS}

\subsection{Materials subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsubsection{Materials subsubsection one.}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text:
\begin{align}
\mathrm{LD}^r = \frac{\mathrm{LD}}{A_\mathrm{iso}}
= 1.5 S \left( 3 \cos^2 \alpha_i - 1 \right)
\end{align}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Materials subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text
(see Figure \ref{NAR-fig1}).

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.
\begin{equation*}
\mathrm{LD} \left( t \right) =
\sum\limits_i
a_i \exp \left( \frac{-t}{\tau_i} \right)
\end{equation*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

\begin{figure}[t]
\begin{center}
\includegraphics{NAR-fig1.eps}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

\section{RESULTS}

\subsection{Results subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

\begin{table}[b]
\tableparts{%
\caption{This is a table caption}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}lllll@{}}
\toprule
Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
\\
& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & --
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2
\\
\botrule
\end{tabular*}%
}
{This is a table footnote}
\end{table}

\subsection{Results subsection two}

Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Table \ref{table:01}).

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Figure \ref{NAR-fig2}a).

Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\begin{figure*}[t]
\begin{center}
\includegraphics{NAR-fig2.eps}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

\subsection{Results subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\section{DISCUSSION}

\subsection{Discussion subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

\section{CONCLUSION}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\subsubsection{Conflict of interest statement.} None declared.
\newpage

\nocite{Ayoub2017}
\nocite{BioJava2012}
\bibliography{rupee}
\bibliographystyle{NAR-natbib}

\end{document}

### 2018-09-24 docs/rupee.tex
mod

@@
 %\articlesubtype{This is the article type (optional)}
+
+\newcommand{\ca}{$\alpha$-carbon\xspace}
+\newcommand{\cas}{$\alpha$-carbons\xspace}
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
-Text.
+Proteins represent the functional end-product within the central dogma of molecular biology \citep{Crick1970}.
+As such, understanding protein structure is a central goal within structural bioinformatics. 
+Protein structure determination, prediction, alignment, and search all serve to advance this understanding. 
+Below, we present our new approach to a fast, scalable, and purely geometric protein structure search we refer to with the cumbersome but catchy acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-\begin{align*}
-&\mathrm{Ascorbate} + \mathrm{EDTA} \cdot \mathrm{Fe}^{3+} \to
-\hbox{Oxidized ascorbate}
-\\
-&\mathrm{EDTA} \cdot \mathrm{Fe}^{2+} + \mathrm{H}_2
-\mathrm{O}_2 \to
-\mathrm{EDTA} \cdot \mathrm{Fe}^{3+} + \cdot
-\mathrm{OH} + \mathrm{OH}^-
-\end{align*}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+For comparisons, we examine results from the CATHEDRAL structural scan \citep{Redfern2007} available at the CATH website \citep{Sillitoe2015}.
+In addition to recognizing domains in multidomain proteins, CATHEDRAL also can be used to find structural neighbors among CATH domains for an uploaded protein data bank (PDB) file, that is, where an identifier is not provided that can be used for retrieval of pre-calculated results.
+CATHEDRAL is effective at this task but can take upwards of 10 minutes to produce results against CATH s35 representatives.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Restricting our initial approach to protein domains, we have indexed CATH v4.1 domains, consisting of 308,999 structures, and developed a feature similar to CATHEDRAL that performs a protein structure search based on a PDB file, returning results in seconds rather than minutes.
+To evaluate RUPEE, we have made comparisons to the output of CATHEDRAL along two dimensions, quality of results and response times. 
+In both cases, RUPEE performs better on average for the domains we evaluated.
+
+Besides our approach to protein structure search, we introduce a polar plot for torsion angles that may have wider applicability in the study of protein structure. 
+Further, the \emph{run position encoding} heuristic introduced below may have wider applicability to algorithms for character sequences containing long runs of repeats.
+
+For the remainder of this paper, we first discuss some related work to provide context for our approach followed by a description of our method. 
+We end with the results of evaluation with CATHEDRAL along with an analysis and conclusion.
+
 % **************************************************************
@@
 
-Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
-Text.
+\section{METHODS}
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text.
+Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features amenable to big data processing.
+Protein structure searches that use linear encodings are not unique \citep{Carpentier2005,Daniluk2011,Ritchie2012}.
+The novelty of our approach lies in its remarkable performance given its simplicity. 
+Additionally, elements of our approach can be isolated and found to be useful in their own right.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text.
-Text.
-
-\section{MATERIALS AND METHODS}
-
-\subsection{Materials subsection one}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-\subsubsection{Materials subsubsection one.}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text:
-\begin{align}
-\mathrm{LD}^r = \frac{\mathrm{LD}}{A_\mathrm{iso}}
-= 1.5 S \left( 3 \cos^2 \alpha_i - 1 \right)
-\end{align}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-\subsection{Materials subsection two}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text
-(see Figure \ref{NAR-fig1}).
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text.
-\begin{equation*}
-\mathrm{LD} \left( t \right) =
-\sum\limits_i
-a_i \exp \left( \frac{-t}{\tau_i} \right)
-\end{equation*}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
+\subsection{Regions of Torsion Angles}
 
@@
 \begin{center}
-\includegraphics{NAR-fig1.eps}
+\includegraphics{ramachandran}
 \end{center}
-\caption{Caption for figure within column.}
-\label{NAR-fig1}
+\caption{Ramachandran plot of randomly sampled torsion angles}
+\label{fig:ramachandran}
 \end{figure}
+
+Our first step towards a linear encoding of protein structure is to identify separable regions of permissible torsion angles,
+but first we introduce a new plot of torsion angles better suited to this effort.
+
+Despite their utility and familiarity, Ramachandran plots \citep{Ramachandran1968} represent angular data using a square plot better suited for scalar data.
+This leads to the unwieldy arrangement where the top part of the plot is continuous with the bottom and the left is continuous with the right.
+
+To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution, CATH s35 representatives to account for precision and redundancy, respectively. 
+A Ramachandran plot of the sampled torsions angles is shown in \figurename~\ref{fig:ramachandran}. 
+As can be seen, a single cluster of residues, consisting primarily of $\beta$-strands, appears at all 4 corners of the Ramachandran plot.
+
+This continuity problem was partially addressed in \citet{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
+Both wrapped and mirrored plots take advantage of the sparsely populated areas of the Ramachandran plot at $\phi = 0\degree$ and $\psi = -120\degree$.
+However, with larger samples of torsion angles, the area at $\psi = -120\degree$ becomes less sparse. 
+The use of a polar plot resolves this elegantly by only requiring one break in continuity at $\phi = 0\degree$.
+
+\figurename~\ref{fig:torsion} plots the same torsion angles appearing in \figurename~\ref{fig:ramachandran} using a polar plot. 
+In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
+Notice the residues appearing at the 4 corners of the Ramachandran plot now appear in one continuous region of the polar plot centered at $\phi = \pm180\degree$ and $\psi = \pm180\degree$.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics{torsion}
+\end{center}
+\caption{Polar plot of randomly sampled torsion angles}
+\label{fig:torsion}
+\end{figure}
+
+\subsection{Linear Encoding of Protein Structure}
+
+The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
+The eight DSSP secondary structure assignment codes defined in \citet{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
+
+Polar plots for each group of DSSP assignment codes along with defined regions and descriptor designations are shown in \figurename~\ref{fig:torsion_refs}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
+For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
+The only exception is found in the bends and coil plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.
+
+%\begin{figure}[t]
+%\begin{center}
+%\includegraphics{torsion_refs}
+%\end{center}
+%\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
+%\label{fig:torsion_refs}
+%\end{figure}
+
+\tablename~\ref{tab:codes} summarizes the mapping between region and secondary structure assignment combinations and ranges of integer valued descriptors.  
+The specific mapping was arrived at primarily based on quality of results.
+
+\begin{table}[!t]
+    \caption{DSSP Code/Descriptor Map}
+    \label{tab:codes}
+\centering
+\begin{tabular}{lll}
+\toprule
+    \head{DSSP Codes} & \head{SS} & \head{Descriptors}\\
+\midrule
+    G, H, I & helix & 1-4\\
+    E & strand & 5-7\\
+    S, C & bend, coil & 8-10\\
+    T & turn & 11\\
+    B & bridge & 12\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Our initial use of Ramachandran plots to identify regions resulted in the frequent case of highly similar domains from the same CATH s95 clusters being considered significantly different. 
+Alignment of these domains in PyMOL \citep{PyMOL} and the development of a script to label residues with their descriptors showed that slight differences in structure often resulted in distinct descriptors being assigned to aligned residues.
+Once we defined regions using the less confusing polar plots, this discrepancy was no longer observed.
+
+As an example of our linear encoding, the following sequence of descriptors represents a $\beta$-turn-$\beta$ motif followed by bends and coil.
+\begin{gather}\label{E:descrseq} 
+    [\, 5, 5, 5, 5, 5, 11, 11, 5, 5, 5, 5, 5, 8, 8, 10, 9 \,]
+\end{gather}
+
+Secondary structure assignments for termini are not always consistent among the variety of secondary structure assignment tools \citep{Martin2005}. 
+We also observed this to be the case for DSSP assignments across homologous domains. 
+Here, we introduce a heuristic we call \emph{secondary structure extension} (SSE) to address this variance.
+
+SSE iterates a sequence of descriptors once in both the forward and backward directions. 
+Whenever a helix or strand descriptor is encountered, the next descriptor receives the same assignment as the preceding residue if its torsion angles match the region of the preceding residue, regardless of its own secondary structure assignment.
+
+SSE performed on the sequence found in (\ref{E:descrseq}) gives the sequence in (\ref{E:extdescrseq}).
+Notice, the subsequence $[\, 8, 8 \,]$ in (\ref{E:descrseq}), corresponding to bends with torsion angles falling in the densest region of $\beta$-strand residues, becomes $[\, 5, 5 \,]$ in (\ref{E:extdescrseq}).
+\begin{gather}\label{E:extdescrseq} 
+    [\, 5, 5, 5, 5, 5, 11, 11, 5, 5, 5, 5, 5, 5, 5, 10, 9 \,]
+\end{gather}
+
+Though \citet{Martin2005} lends some support to this heuristic, we use it primarily based on its performance.
+
+\subsection{Bag representation of protein structure}
+
+Once a linear encoding for a protein structure is obtained, it needs to be further transformed into a representation suitable for fast and scalable similarity comparisons to other structures.
+The processing of text documents within Information Retrieval~(IR) has long been used to satisfy these requirements using bag representations.
+There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \citep{Aungand2004,Zhang2010,Budowski2010}.
+
+We have adapted the syntactic approach to document similarity, often referred to as shingling \citep{Broder1997a}, to our linear encoding of protein structure. 
+We transform a linear sequence of descriptors into a multiset of shingles consisting of 4 consecutive descriptors.
+The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
+
+By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
+As an example, the sequence in (\ref{E:extdescrseq}) is transformed into the following bag of shingles. 
+\begin{align}\label{E:shinglebag}
+    \begin{split}
+    \{\,&[5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 11], [5, 5, 11, 11], \\
+        & [5, 11, 11, 5], [11, 11, 5, 5], [11, 5, 5, 5], [5, 5, 5, 5], \\
+        & [5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 10], \\
+        & [5, 5, 10, 9] \,\}
+    \end{split}
+\end{align}
+
+Next, each shingle $s$ is hashed to an integer as shown in~(\ref{E:hashdef}). 
+The hash function used is a simplification of the hash function used in the Rabin-Karp algorithm \citep{Karp1987}.
+The prime number $13$ is used as the base since it is large enough to spread the descriptor values out in hash space without collisions. 
+\begin{gather}\label{E:hashdef}
+    s_{hash} = s_1 \times 13^3 + s_2 \times 13^2 + s_3 \times 13 + s_4
+\end{gather}
+Subsequently, the multiset in (\ref{E:shinglebag}) becomes the following bag of integers.
+\begin{align}\label{E:hashbag}
+    \begin{split}
+    \{\,&11900, 11900, 11906, 11984, 12992, \\
+        &26096, 25082, 11900, 11900, 11900, \\
+        &11900, 11905, 11969 \,\}
+    \end{split}
+\end{align}
+
+This final step completes the transformation of an ordered list of descriptors to a multiset of integers that still retains some of the order information present in the original list.
+
+Notice in (\ref{E:hashbag}) the value 11900, corresponding to the shingle $[ 5, 5, 5, 5 ]$, occurs frequently indicating the presence of a $\beta$-strand. 
+Since most proteins are dominated by regular secondary structure, the abundance of shingles for $\beta$-strands as well as the three types of helices, end up dominating comparisons. 
+Moreover, since shingles are limited in length, this situation allows for structures with many short $\beta$-strands to match structures with fewer long $\beta$-strands.
+The same situation applies to helices.
+
+To address this lack of specificity, we introduce a heuristic we call \emph{run position encoding} (RPE). 
+To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run $i$.
+\begin{gather}
+    runfactor(i) = 
+    \begin{cases}
+        i               &\text{if $i < \lfloor l/2 \rfloor$}\\
+        l - i - 1       &\text{otherwise} 
+    \end{cases}
+\end{gather}
+where $i$ is zero-based and $l$ is the length of the run. 
+Multiplying by $10^5$ places the run factor as the left-most digit in the hash to avoid interference with the digits provided by the hash in (\ref{E:hashdef}).
+This placement is also convenient for visual inspection, since the run factor is isolated as the left-most digit.
+
+The run factors for the sequence in (\ref{E:extdescrseq}) are
+\begin{align}
+    [\, 0, 1, 2, 1, 0, 0, 0, 0, 1, 2, 3, 2, 1, 0, 0, 0 \,].
+\end{align}
+Applied to the bag of integers in (\ref{E:hashbag}) gives
+\begin{align}\label{E:rpebag}
+    \begin{split}
+    \{\,&011900, 111900, 211906, 111984, 012992, \\
+        &026096, 025082, 011900, 111900, 211900, \\
+        &311900, 211905, 111969 \,\},
+    \end{split}
+\end{align}
+where the leading zero run factors are shown for clarity.
+
+This pyramidal approach preserves matches at the boundaries between secondary structure runs and loops that would not otherwise be preserved in the presence of differences in run lengths of one or more.
+
+To see why RPE run factors are calculated at the descriptor level and factored in at the shingle level, consider shingling a list of RPE run factors themselves, which mirrors applying them at the descriptor level.
+\begin{align*}
+    &\text{The sequence of RPE factors} \\
+    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
+    &\qquad\{\, [0, 1, 2, 3], [1, 2, 3, 2], [2, 3, 2, 1], [3, 2, 1, 0] \,\} \\
+    &\text{and with one less element} \\
+    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
+    &\qquad\{\, [0, 1, 2, 2], [1, 2, 2, 1], [2, 2, 1, 0] \,\}
+\end{align*}
+Notice above, there is not a single shingle match for this one-off difference in run length.
+Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
+\begin{align*}
+    &\text{The sequence of RPE factors} \\
+    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
+    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2], [3, 3, 3, 3] \,\} \\
+    &\text{and with one less element} \\
+    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
+    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2] \,\}
+\end{align*}
+In this latter case, a one-off difference in run length results in one less shingle match while still serving to increase the specificity of the shingles.
+
+Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \citep{Levan1971} for multisets,
+\begin{align}
+    J(a,b) = \frac{\sum_i min(a_i, b_i)}{\sum_i max(a_i,b_i)}\text{,}
+\end{align}
+where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively.
+
+\subsection{Fast and scalable structure search}
+
+In IR, the bag of shingles representation of documents is used in the near dupe clustering of documents \citep{Broder1997b}.
+One application of near dupe clustering is in the review stage of Electronic-Discovery \citep{Joshi2008}, which is the most expensive stage in a discovery process. 
+Often millions of documents must be examined by a staff of attorneys to make a reasonable effort at providing all documents relevant to the discovery request. 
+Grouping documents into near dupe clusters and assigning all documents within a cluster to a single reviewer reduces duplication of effort.
+
+In the case of near dupe clustering, each document must be compared to every other document in the collection, taking quadratic time.
+For this task, min-hashing \citep{Broder1998} and locality sensitive hashing (LSH) \citep{Indyk1998} can be combined to reduce this to subquadratic time. 
+Although we do not near dupe cluster domains, we can still leverage the techniques of min-hashing and LSH to speed up protein structure search by a large constant factor.
+
+Min-hashing is used to randomly select items from a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum item in each permuted list.
+If the same random permutation of items is performed on each set of items in a collection, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity \citep{Broder1998}.
+In order to approximate the Jaccard similarity for a given pair of sets, a sufficient number of min-hashes must be obtained.
+
+In our case, the items are bags of shingle hashes for protein structures from which we obtain 60 min-hashes as described in \citet{Rajaraman2012}. 
+Given the key result above, the Jaccard similarity can now be approximated by the proportion of matching min-hashes.
+
+Weighted min-hashing \citep{Chum2008} with integral weights is an extension to min-hashing that can be applied to multisets where the frequency of a hash within a multiset is used as its weight.
+
+Next, we use the LSH banding technique as described in \citet{Rajaraman2012}.
+The key result of the banding technique is that if \emph{any} band positions are a match for a given pair of structures, the probability that a specific similarity threshold has been met can be calculated.
+We use 20 bands of 3-min-hashes where the probability of a Jaccard similarity of 60\% or greater is approximately 99\%. 
+Banding allows the problem of finding similar items to be parallelized across bands since all that is needed for a match is a single band match.
+
+Together, min-hashing and LSH allow for a fast and scalable protein structure search using run position encoded shingles of residue descriptors.
 
@@
 
-\begin{table}[b]
-\tableparts{%
-\caption{This is a table caption}
-\label{table:01}%
-}{%
-\begin{tabular*}{\columnwidth}{@{}lllll@{}}
-\toprule
-Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
-\\
-& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
-\\
-\colrule
-Row 1 & Row 1 & Row 1 & -- & --
-\\
-Row 2 & Row 2 & Row 2 & Row 2 & Row 2
-\\
-\botrule
-\end{tabular*}%
-}
-{This is a table footnote}
-\end{table}
-
 \subsection{Results subsection two}
-
-Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text (see Table \ref{table:01}).
-
-Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text (see Figure \ref{NAR-fig2}a).
-
-Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-\begin{figure*}[t]
-\begin{center}
-\includegraphics{NAR-fig2.eps}
-\end{center}
-\caption{Caption for wide figure over two columns.
-\textbf{(a)} Left figure.
-\textbf{(b)} Right figure (see (a)).
-}
-\label{NAR-fig2}
-\end{figure*}
-
-\subsection{Results subsection three}
 
@@
 Text. Text. Text.
-
-\section{DISCUSSION}
-
-\subsection{Discussion subsection one}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text.
-
-\subsection{Discussion subsection two}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-\subsection{Discussion subsection three}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text.
 

### 2018-10-01 docs/rupee.tex
update plots

@@
 
+\usepackage{textcomp}
 \usepackage{lmodern}
+\usepackage{gensymb}
+\usepackage{booktabs}
 
@@
 %\articlesubtype{This is the article type (optional)}
+
+\hbadness=99999
+
+\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
 
@@
 
-\section{Introduction}
+\section{INTRODUCTION}
 
-Proteins represent the functional end-product within the central dogma of molecular biology \citep{Crick1970}.
+Proteins represent the functional end-product within the central dogma of molecular biology \cite{Crick1970}.
 As such, understanding protein structure is a central goal within structural bioinformatics. 
 Protein structure determination, prediction, alignment, and search all serve to advance this understanding. 
-Below, we present our new approach to a fast, scalable, and purely geometric protein structure search we refer to with the cumbersome but catchy acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
+Below, we present our new approach to a fast, scalable, and purely geometric protein structure search we refer to with the acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
 
-For comparisons, we examine results from the CATHEDRAL structural scan \citep{Redfern2007} available at the CATH website \citep{Sillitoe2015}.
-In addition to recognizing domains in multidomain proteins, CATHEDRAL also can be used to find structural neighbors among CATH domains for an uploaded protein data bank (PDB) file, that is, where an identifier is not provided that can be used for retrieval of pre-calculated results.
-CATHEDRAL is effective at this task but can take upwards of 10 minutes to produce results against CATH s35 representatives.
+%For comparisons, we examine results from the mTM-align structure search \cite{Dong2018}, the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website \cite{Sillitoe2015}, and the secondary structure matching (SSM) search \cite{Krissinel2004}.
+%To evaluate RUPEE, we have made comparisons to the output of the above tools along two dimensions, quality of results and response times. 
+%In the case CATHEDRAL and SSM, RUPEE performs better on average for the domains we evaluated.
 
-Restricting our initial approach to protein domains, we have indexed CATH v4.1 domains, consisting of 308,999 structures, and developed a feature similar to CATHEDRAL that performs a protein structure search based on a PDB file, returning results in seconds rather than minutes.
-To evaluate RUPEE, we have made comparisons to the output of CATHEDRAL along two dimensions, quality of results and response times. 
-In both cases, RUPEE performs better on average for the domains we evaluated.
+%Restricting our initial approach to protein domains, we have indexed CATH v4.1 domains, consisting of 308,999 structures, and developed a feature similar to CATHEDRAL that performs a protein structure search based on a PDB file, returning results in seconds rather than minutes.
 
@@
 
-For the remainder of this paper, we first discuss some related work to provide context for our approach followed by a description of our method. 
-We end with the results of evaluation with CATHEDRAL along with an analysis and conclusion.
+We first discuss some related work to provide a context for our approach followed by a description of our method. 
+We end with a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website \cite{Sillitoe2015}.
 
@@
 
+\section{RELATED WORK}
+
+Pairwise alignment involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric. 
+Most commonly, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
+
+The typical use case of aligning one protein structure to another does not impose tight response time requirements. 
+For this reason, pairwise alignments can focus on accuracy. 
+On the other hand, a protein structure search can involve thousands of comparisons and accuracy is often balanced against speed. 
+In this case, pairwise alignment is still useful for evaluating the results of a search, and this is the approach we take.
+
+For pairwise alignment, Combinatorial Extensions (CE) \citep{Shindyalov1998} and FATCAT \citep{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
+CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
+
+Whereas pairwise structure alignments only depend on the sequence of \ca coordinates, protein structure searches often introduce a further dependence on the sequence order of amino acids.
+This approach often takes the form of clustering proteins based on sequences and pre-calculating results for pairwise alignments among cluster representatives. 
+Then, these pre-calculated results are used for filtering the number of structures used for comparisons against a query protein.
+The exact formula for combining the use of representatives and pre-calculated results varies from system to system.
+However, all systems using this approach share the same disadvantage, an indirect dependence on amino acid sequences. 
+In the absence of a reliance on sequence representatives and pre-calculated results, and without sacrificing accuracy, response times suffer greatly, often taking upwards of an hour for queries to complete.
+
+For protein structure searches, VAST \citep{Gilbrat1996} and the FATCAT server \citep{Ye2004} are among the most popular. 
+Nonetheless, these searches are slow in comparison to mTM, SSM, and CATHEDRAL when pre-calculated results are not used. 
+If given a known protein domain, VAST can return structural neighbors in seconds using pre-calculated results. 
+However, if uploading a PDB file where pre-calculated results are not used, response times for VAST can exceed 30 minutes. 
+Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \citep{Prlic2010}.
+
+The PhyreStorm server \citep{Mezulis2016} provides another notable protein structure search.
+Here too, it depends on PDB pre-calculated pairwise comparisons among PDB-40 cluster representatives \citep{Prlic2010}. 
+Notably, PhyreStorm returns good results within minutes based on an uploaded PDB file.
+
+Given the above, there remains a need for a purely geometric protein structure search.
+For the serendipitous exploration of relations between protein structures performed in the trenches, this search should be fast. 
+Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \citep{gkw1000}, this search should be scalable. 
+At a minimum, RUPEE takes a significant step in this direction as will be shown below.
+
 \section{METHODS}
@@
 Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features amenable to big data processing.
-Protein structure searches that use linear encodings are not unique \citep{Carpentier2005,Daniluk2011,Ritchie2012}.
+Protein structure searches that use linear encodings are not unique \cite{Carpentier2005,Daniluk2011,Ritchie2012}.
 The novelty of our approach lies in its remarkable performance given its simplicity. 
@@
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics{ramachandran}
-\end{center}
-\caption{Ramachandran plot of randomly sampled torsion angles}
-\label{fig:ramachandran}
-\end{figure}
-
 Our first step towards a linear encoding of protein structure is to identify separable regions of permissible torsion angles,
@@
 
-Despite their utility and familiarity, Ramachandran plots \citep{Ramachandran1968} represent angular data using a square plot better suited for scalar data.
+\begin{figure*}[tb]
+\centering
+\includegraphics{torsion_plots}
+\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
+\label{fig:torsion_plots}
+\end{figure*}
+
+Despite their utility and familiarity, Ramachandran plots \cite{Ramachandran1968} represent angular data using a square plot better suited for scalar data.
 This leads to the unwieldy arrangement where the top part of the plot is continuous with the bottom and the left is continuous with the right.
@@
 To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution, CATH s35 representatives to account for precision and redundancy, respectively. 
-A Ramachandran plot of the sampled torsions angles is shown in \figurename~\ref{fig:ramachandran}. 
+A Ramachandran plot of the sampled torsions angles is shown to the left in \figurename~\ref{fig:torsion_plots}. 
 As can be seen, a single cluster of residues, consisting primarily of $\beta$-strands, appears at all 4 corners of the Ramachandran plot.
 
-This continuity problem was partially addressed in \citet{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
+This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
 Both wrapped and mirrored plots take advantage of the sparsely populated areas of the Ramachandran plot at $\phi = 0\degree$ and $\psi = -120\degree$.
@@
 
-\figurename~\ref{fig:torsion} plots the same torsion angles appearing in \figurename~\ref{fig:ramachandran} using a polar plot. 
+To the right in \figurename~\ref{fig:torsion_plots}, we plot the same torsion angles appearing in the Ramachandran plot using a polar plot. 
 In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
 Notice the residues appearing at the 4 corners of the Ramachandran plot now appear in one continuous region of the polar plot centered at $\phi = \pm180\degree$ and $\psi = \pm180\degree$.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics{torsion}
-\end{center}
-\caption{Polar plot of randomly sampled torsion angles}
-\label{fig:torsion}
-\end{figure}
 
@@
 The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
-The eight DSSP secondary structure assignment codes defined in \citet{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
+The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
 
@@
 
-%\begin{figure}[t]
-%\begin{center}
-%\includegraphics{torsion_refs}
-%\end{center}
-%\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
-%\label{fig:torsion_refs}
-%\end{figure}
+\begin{figure*}[tb]
+\begin{center}
+\includegraphics{torsion_refs}
+\end{center}
+\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
+\label{fig:torsion_refs}
+\end{figure*}
 
@@
 
-\begin{table}[!t]
+\begin{table}[t]
     \caption{DSSP Code/Descriptor Map}
@@
 Our initial use of Ramachandran plots to identify regions resulted in the frequent case of highly similar domains from the same CATH s95 clusters being considered significantly different. 
-Alignment of these domains in PyMOL \citep{PyMOL} and the development of a script to label residues with their descriptors showed that slight differences in structure often resulted in distinct descriptors being assigned to aligned residues.
+Alignment of these domains in PyMOL \cite{PyMOL} and the development of a script to label residues with their descriptors showed that slight differences in structure often resulted in distinct descriptors being assigned to aligned residues.
 Once we defined regions using the less confusing polar plots, this discrepancy was no longer observed.
@@
 
-Secondary structure assignments for termini are not always consistent among the variety of secondary structure assignment tools \citep{Martin2005}. 
+Secondary structure assignments for termini are not always consistent among the variety of secondary structure assignment tools \cite{Martin2005}. 
 We also observed this to be the case for DSSP assignments across homologous domains. 
@@
 
-Though \citet{Martin2005} lends some support to this heuristic, we use it primarily based on its performance.
+Though \cite{Martin2005} lends some support to this heuristic, we use it primarily based on its performance.
 
@@
 The processing of text documents within Information Retrieval~(IR) has long been used to satisfy these requirements using bag representations.
-There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \citep{Aungand2004,Zhang2010,Budowski2010}.
+There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \cite{Aungand2004,Zhang2010,Budowski2010}.
 
-We have adapted the syntactic approach to document similarity, often referred to as shingling \citep{Broder1997a}, to our linear encoding of protein structure. 
+We have adapted the syntactic approach to document similarity, often referred to as shingling \cite{Broder1997a}, to our linear encoding of protein structure. 
 We transform a linear sequence of descriptors into a multiset of shingles consisting of 4 consecutive descriptors.
@@
 Next, each shingle $s$ is hashed to an integer as shown in~(\ref{E:hashdef}). 
-The hash function used is a simplification of the hash function used in the Rabin-Karp algorithm \citep{Karp1987}.
+The hash function used is a simplification of the hash function used in the Rabin-Karp algorithm \cite{Karp1987}.
 The prime number $13$ is used as the base since it is large enough to spread the descriptor values out in hash space without collisions. 
@@
 
-Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \citep{Levan1971} for multisets,
+Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \cite{Levan1971} for multisets,
 \begin{align}
@@
 
-In IR, the bag of shingles representation of documents is used in the near dupe clustering of documents \citep{Broder1997b}.
-One application of near dupe clustering is in the review stage of Electronic-Discovery \citep{Joshi2008}, which is the most expensive stage in a discovery process. 
+In IR, the bag of shingles representation of documents is used in the near dupe clustering of documents \cite{Broder1997b}.
+One application of near dupe clustering is in the review stage of Electronic-Discovery \cite{Joshi2008}, which is the most expensive stage in a discovery process. 
 Often millions of documents must be examined by a staff of attorneys to make a reasonable effort at providing all documents relevant to the discovery request. 
@@
 In the case of near dupe clustering, each document must be compared to every other document in the collection, taking quadratic time.
-For this task, min-hashing \citep{Broder1998} and locality sensitive hashing (LSH) \citep{Indyk1998} can be combined to reduce this to subquadratic time. 
+For this task, min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} can be combined to reduce this to subquadratic time. 
 Although we do not near dupe cluster domains, we can still leverage the techniques of min-hashing and LSH to speed up protein structure search by a large constant factor.
@@
 Min-hashing is used to randomly select items from a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum item in each permuted list.
-If the same random permutation of items is performed on each set of items in a collection, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity \citep{Broder1998}.
+If the same random permutation of items is performed on each set of items in a collection, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity \cite{Broder1998}.
 In order to approximate the Jaccard similarity for a given pair of sets, a sufficient number of min-hashes must be obtained.
 
-In our case, the items are bags of shingle hashes for protein structures from which we obtain 60 min-hashes as described in \citet{Rajaraman2012}. 
+In our case, the items are bags of shingle hashes for protein structures from which we obtain 60 min-hashes as described in \cite{Rajaraman2012}. 
 Given the key result above, the Jaccard similarity can now be approximated by the proportion of matching min-hashes.
 
-Weighted min-hashing \citep{Chum2008} with integral weights is an extension to min-hashing that can be applied to multisets where the frequency of a hash within a multiset is used as its weight.
+Weighted min-hashing \cite{Chum2008} with integral weights is an extension to min-hashing that can be applied to multisets where the frequency of a hash within a multiset is used as its weight.
 
-Next, we use the LSH banding technique as described in \citet{Rajaraman2012}.
+Next, we use the LSH banding technique as described in \cite{Rajaraman2012}.
 The key result of the banding technique is that if \emph{any} band positions are a match for a given pair of structures, the probability that a specific similarity threshold has been met can be calculated.

### 2018-10-01 figures/ramachandran.R

@@ -11,13 +11,13 @@ rm(list = ls())
 df <- read.csv('torsion.txt')
 
 # map values
-df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend'), to = c('Helix', 'Strand', 'Coil'))
+df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
 
 # reorder factor levels
-df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Coil'))
+df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
 
 # color scale
-color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Coil' = 'black')
+color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
 
 ramachandran_plot <- ggplot(df, aes(phi, psi, color = sse)) +
     

### 2018-10-01 figures/torsion_refs.R

@@ -11,20 +11,20 @@ refs <- read.csv('torsion_refs.txt')
 annotes <- read.csv('torsion_annotes.txt')
 
 # map values
-df$sse <- mapvalues(df$sse, from = c('Bend'), to = c('Coil'))
+df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
 
 # subset data
-df <- subset(df, df$sse == 'Helix' | df$sse == 'Strand' | df$sse == 'Coil')
+df <- subset(df, df$sse == 'Helix' | df$sse == 'Strand' | df$sse == 'Bend/Coil')
 
 # reorder factor levels
-df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Coil'))
+df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
 
 # wrap and translate torsion angles
 df$phi <- ifelse(df$phi < 0, df$phi + 360, df$phi)
 df$phi <- df$phi + 200
 
 # color scale
-color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Coil' = 'black')
+color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
 
 ggplot(df, aes(phi, psi, color = sse)) +
     

### 2018-10-01 docs/rupee.tex
edits

@@
 
-For pairwise alignment, Combinatorial Extensions (CE) \citep{Shindyalov1998} and FATCAT \citep{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
+For pairwise alignment, Combinatorial Extensions (CE) \cite{Shindyalov1998} and FATCAT \cite{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
 CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
@@
 
-For protein structure searches, VAST \citep{Gilbrat1996} and the FATCAT server \citep{Ye2004} are among the most popular. 
+For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
 Nonetheless, these searches are slow in comparison to mTM, SSM, and CATHEDRAL when pre-calculated results are not used. 
@@
 However, if uploading a PDB file where pre-calculated results are not used, response times for VAST can exceed 30 minutes. 
-Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \citep{Prlic2010}.
+Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
 
-The PhyreStorm server \citep{Mezulis2016} provides another notable protein structure search.
-Here too, it depends on PDB pre-calculated pairwise comparisons among PDB-40 cluster representatives \citep{Prlic2010}. 
+The PhyreStorm server \cite{Mezulis2016} provides another notable protein structure search.
+Here too, it depends on PDB pre-calculated pairwise comparisons among PDB-40 cluster representatives \cite{Prlic2010}. 
 Notably, PhyreStorm returns good results within minutes based on an uploaded PDB file.
@@
 For the serendipitous exploration of relations between protein structures performed in the trenches, this search should be fast. 
-Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \citep{gkw1000}, this search should be scalable. 
+Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \cite{gkw1000}, this search should be scalable. 
 At a minimum, RUPEE takes a significant step in this direction as will be shown below.
@@
 
-Secondary structure assignments for termini are not always consistent among the variety of secondary structure assignment tools \cite{Martin2005}. 
-We also observed this to be the case for DSSP assignments across homologous domains. 
-Here, we introduce a heuristic we call \emph{secondary structure extension} (SSE) to address this variance.
-
-SSE iterates a sequence of descriptors once in both the forward and backward directions. 
-Whenever a helix or strand descriptor is encountered, the next descriptor receives the same assignment as the preceding residue if its torsion angles match the region of the preceding residue, regardless of its own secondary structure assignment.
-
-SSE performed on the sequence found in (\ref{E:descrseq}) gives the sequence in (\ref{E:extdescrseq}).
-Notice, the subsequence $[\, 8, 8 \,]$ in (\ref{E:descrseq}), corresponding to bends with torsion angles falling in the densest region of $\beta$-strand residues, becomes $[\, 5, 5 \,]$ in (\ref{E:extdescrseq}).
-\begin{gather}\label{E:extdescrseq} 
-    [\, 5, 5, 5, 5, 5, 11, 11, 5, 5, 5, 5, 5, 5, 5, 10, 9 \,]
-\end{gather}
-
-Though \cite{Martin2005} lends some support to this heuristic, we use it primarily based on its performance.
-
 \subsection{Bag representation of protein structure}
@@
 By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
-As an example, the sequence in (\ref{E:extdescrseq}) is transformed into the following bag of shingles. 
+As an example, the sequence in (\ref{E:descrseq}) is transformed into the following bag of shingles. 
 \begin{align}\label{E:shinglebag}
@@
         & [5, 11, 11, 5], [11, 11, 5, 5], [11, 5, 5, 5], [5, 5, 5, 5], \\
-        & [5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 10], \\
-        & [5, 5, 10, 9] \,\}
+        & [5, 5, 5, 5], [5, 5, 5, 8], [5, 5, 8, 8], [5, 8, 8, 10], \\
+        & [8, 8, 10, 9] \,\}
     \end{split}
@@
     \{\,&11900, 11900, 11906, 11984, 12992, \\
-        &26096, 25082, 11900, 11900, 11900, \\
-        &11900, 11905, 11969 \,\}
+        &26096, 25082, 11900, 11900, 11903, \\
+        &11942, 12451, 19067 \,\}
     \end{split}
@@
 
-Notice in (\ref{E:hashbag}) the value 11900, corresponding to the shingle $[ 5, 5, 5, 5 ]$, occurs frequently indicating the presence of a $\beta$-strand. 
+Notice in (\ref{E:hashbag}) the value 11900, corresponding to the shingle $[ 5, 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
 Since most proteins are dominated by regular secondary structure, the abundance of shingles for $\beta$-strands as well as the three types of helices, end up dominating comparisons. 
@@
 
-The run factors for the sequence in (\ref{E:extdescrseq}) are
+The run factors for the sequence in (\ref{E:descrseq}) are
 \begin{align}
-    [\, 0, 1, 2, 1, 0, 0, 0, 0, 1, 2, 3, 2, 1, 0, 0, 0 \,].
+    [\, 0, 1, 2, 1, 0, 0, 0, 0, 1, 2, 1, 0, 0, 0, 0, 0 \,].
 \end{align}
@@
     \{\,&011900, 111900, 211906, 111984, 012992, \\
-        &026096, 025082, 011900, 111900, 211900, \\
-        &311900, 211905, 111969 \,\},
+        &026096, 025082, 011900, 111900, 211903, \\
+        &111942, 012451, 019067 \,\}
     \end{split}
@@
 \end{align*}
-Notice above, there is not a single shingle match for this one-off difference in run length.
+Notice above, there is not a single match for this one-off difference in run length.
 Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
@@
 
-In our case, the items are bags of shingle hashes for protein structures from which we obtain 60 min-hashes as described in \cite{Rajaraman2012}. 
+In our case, the items are bags of shingle hashes for protein structures from which we obtain 99 min-hashes as described in \cite{Rajaraman2012}. 
 Given the key result above, the Jaccard similarity can now be approximated by the proportion of matching min-hashes.
-
-Weighted min-hashing \cite{Chum2008} with integral weights is an extension to min-hashing that can be applied to multisets where the frequency of a hash within a multiset is used as its weight.
 
@@
 The key result of the banding technique is that if \emph{any} band positions are a match for a given pair of structures, the probability that a specific similarity threshold has been met can be calculated.
-We use 20 bands of 3-min-hashes where the probability of a Jaccard similarity of 60\% or greater is approximately 99\%. 
+We use 33 bands of 3-min-hashes where the probability of a Jaccard similarity of 60\% or greater is approximately 99\%. 
 Banding allows the problem of finding similar items to be parallelized across bands since all that is needed for a match is a single band match.

### 2018-10-02 docs/rupee.tex
introduce fast and regular modes

@@
 \documentclass[a4,center,fleqn]{NAR}
+
+%TODO
+% 1. Subsection 'fast and scalable structure search' is not the final section. 
+% 2. In the intro to methods we should indicate the general outline better.
 
@@
 
-%For comparisons, we examine results from the mTM-align structure search \cite{Dong2018}, the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website \cite{Sillitoe2015}, and the secondary structure matching (SSM) search \cite{Krissinel2004}.
-%To evaluate RUPEE, we have made comparisons to the output of the above tools along two dimensions, quality of results and response times. 
-%In the case CATHEDRAL and SSM, RUPEE performs better on average for the domains we evaluated.
-
-%Restricting our initial approach to protein domains, we have indexed CATH v4.1 domains, consisting of 308,999 structures, and developed a feature similar to CATHEDRAL that performs a protein structure search based on a PDB file, returning results in seconds rather than minutes.
+RUPEE has two modes of operation, fast and regular. 
+Fast mode is significantly faster than all other protein structure searches discussed below but at the expensive of accuracy.
+Despite this, we will show that the accuracy of RUPEE in fast mode is not far below that of the best available structure searches. 
+On the other hand, the accuracy and response times of RUPEE in regular mode are comparable to currently available protein structure searches that are commonly considered fast.
 
@@
 
+\tablename~\ref{tab:codes} summarizes the mapping between region and secondary structure assignment combinations and ranges of integer valued descriptors.  
+The specific mapping was arrived at primarily based on an evaluation of results.
+
 \begin{figure*}[tb]
@@
 \end{figure*}
-
-\tablename~\ref{tab:codes} summarizes the mapping between region and secondary structure assignment combinations and ranges of integer valued descriptors.  
-The specific mapping was arrived at primarily based on quality of results.
 

### 2018-10-02 docs/rupee.tex
remove table

@@
 
-Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features amenable to big data processing.
+Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features. 
+Min-hashing and locality sensitive hashing (LSH), techniques drawn from big-data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and slow.
+
 Protein structure searches that use linear encodings are not unique \cite{Carpentier2005,Daniluk2011,Ritchie2012}.
@@
 
-\tablename~\ref{tab:codes} summarizes the mapping between region and secondary structure assignment combinations and ranges of integer valued descriptors.  
-The specific mapping was arrived at primarily based on an evaluation of results.
-
 \begin{figure*}[tb]
@@
 \end{figure*}
-
-\begin{table}[t]
-    \caption{DSSP Code/Descriptor Map}
-    \label{tab:codes}
-\centering
-\begin{tabular}{lll}
-\toprule
-    \head{DSSP Codes} & \head{SS} & \head{Descriptors}\\
-\midrule
-    G, H, I & helix & 1-4\\
-    E & strand & 5-7\\
-    S, C & bend, coil & 8-10\\
-    T & turn & 11\\
-    B & bridge & 12\\
-\bottomrule
-\end{tabular}
-\end{table}
 

### 2018-10-03 docs/rupee.tex
authors

@@
 \documentclass[a4,center,fleqn]{NAR}
-
-%TODO
-% 1. Subsection 'fast and scalable structure search' is not the final section. 
-% 2. In the intro to methods we should indicate the general outline better.
 
@@
 \author{%
-Corresponding Author\,$^{1,*}$,
-First Co-Author\,$^{2}$
-and Second Co-Author\,$^2$%
+Ronald Ayoub\,$^{1,}$%
 \footnote{To whom correspondence should be addressed.
-Tel: +44 000 0000000; Fax: +44 000 0000000; Email: xxx@yyyy.ac.zz}}
+Email: ronaldayoub@mail.umkc.edu},
+Yugyung Lee\,$^{1}$}
 
 \address{%
-$^{1}$Affiliation of Corresponding Author
-and
-$^{2}$Affiliation of Both Co-Authors}
+$^{1}$
+School of Computing and Engineering, 
+University of Missouri at Kansas City,
+5110 Rockhill Road,
+Kansas City, MO 64110, USA}
+
 % Affiliation must include:
@@
 
-\subsection{Fast and scalable structure search}
+\subsection{Min-hashing and LSH}
 
@@
 
-Together, min-hashing and LSH allow for a fast and scalable protein structure search using run position encoded shingles of residue descriptors.
+Together, min-hashing and LSH provide the foundation for both operating modes of RUPEE, fast and regular.
+
+\subsection{Operating modes}
+
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text. Text. Text. Text. Text. Text. Text.
 

### 2018-10-03 docs/rupee.tex
intro

@@
 Protein structure determination, prediction, alignment, and search all serve to advance this understanding. 
-Below, we present our new approach to a fast, scalable, and purely geometric protein structure search we refer to with the acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
+Below, we present our approach to a fast, scalable, and purely geometric protein structure search we refer to with the acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
+
+Given a protein domain identifier, whole chain identifier or an uploaded file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or else among whole chains defined in the PDB.
+In contrast to currently available protein structure searches, RUPEE is able to search either of these databases using any identifier. 
+For instance, you can search SCOPe using a CATH domain identifier.
 
@@
 We first discuss some related work to provide a context for our approach followed by a description of our method. 
-We end with a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website \cite{Sillitoe2015}.
+We end with a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website.
 

### 2018-11-02 rupee-srv/src/main/java/edu/umkc/rupee/srv/Main.java
error reporting

@@ -58,6 +58,8 @@ public class Main {
 
                 exp.execute();
 
+                exp.close();
+
                 // service queue
 
                 PreparedStatement stmt = conn.prepareCall("SELECT * from search_queue WHERE status = 'pending' ORDER BY inserted_on DESC;");
@@ -71,6 +73,11 @@ public class Main {
 
                     SearchStatus.updateStatus(item.getSearchId(), "queued");
                 }
+
+                rs.close();
+                stmt.close();
+
+                conn.close();
       
                 Thread.sleep(SLEEP_TIME);
             }

### 2018-11-02 rupee-srv/src/main/java/edu/umkc/rupee/srv/SearchTask.java

@@ -26,12 +26,19 @@ public class SearchTask implements Runnable {
                 QueueItem item = requestQueue.take();
             
                 SearchStatus.updateStatus(item.getSearchId(), "processing");
+                try {
 
-                SearchQueue.search(item);    
+                    SearchQueue.search(item);    
+                    SearchStatus.updateStatus(item.getSearchId(), "complete");
 
-                SearchStatus.updateStatus(item.getSearchId(), "complete");
+                } catch (Exception e) {
 
-            } catch (Exception e) {
+                    Logger.getLogger(SearchTask.class.getName()).log(Level.SEVERE, null, e);
+                    SearchStatus.updateStatus(item.getSearchId(), "error");
+
+                }
+            
+            } catch (InterruptedException e) {
                 Logger.getLogger(SearchTask.class.getName()).log(Level.SEVERE, null, e);
             }
         }           

### 2018-11-05 figures/combined_response.R
plots

@@ -1,0 +1,64 @@
+
+library(grid)
+library(gridExtra)
+
+source('response.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = length(list(...)),
+           nrow = 1,
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(list(plots[[2]], plots[[3]]), function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol - 1, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+dummy_plot <- get_timing_plot(
+        'dummy timing',
+        'response_dummy.txt',
+        c('RUPEE', 'RUPEE Fast', 'mTM', 'SSM','CATHEDRAL'), 
+        c('#e41a1c', '#377eb8', '#4daf4a', '#984ea3','#ff7f00'),
+        TRUE
+)
+scop_plot <- get_timing_plot(
+        'scop_d62 timing',
+        'response_scop_d62.txt',
+        c('RUPEE', 'RUPEE Fast', 'mTM', 'SSM'), 
+        c('#e41a1c', '#377eb8', '#4daf4a', '#984ea3'),
+        TRUE
+)
+cath_plot <- get_timing_plot(
+        'cath_d99 timing',
+        'response_cath_d99.txt',
+        c('RUPEE', 'RUPEE Fast', 'CATHEDRAL'), 
+        c('#e41a1c', '#377eb8', '#ff7f00'),
+        FALSE
+)
+
+combined <- grid_arrange_shared_legend(dummy_plot, scop_plot, cath_plot)
+
+ggsave('combined_response.eps', plot = combined, width = 7, height = 2.5)
+

### 2018-11-05 figures/response.R

@@ -5,62 +5,74 @@ library(plyr)
 # clear environment
 rm(list = ls())
 
-# read in data file
-df <- read.csv('response.txt')
+get_timing_plot <- function(p_title, p_file, p_levels, p_colors, p_y_axis) {
 
-# reorder factor levels
-df$app <- factor(df$app, levels = c('RUPEE', 'CATHEDRAL'))
+    # read in data file
+    df <- read.csv(p_file)
 
-ggplot(df, aes(residue_count, response_time, group = app, color = app)) +
-    
-    # geoms
-    geom_line(
-        size = rel(0.5)
-    ) + 
-    geom_point(
-        size = rel(0.75)
-    ) + 
-    geom_vline(
-        xintercept = 162,
-        colour = 'grey50', 
-        size = rel(0.2)
-    ) +
+    # reorder factor levels
+    df$app <- factor(df$app, levels = p_levels)
 
-    # scales
-    scale_color_grey(
-        start = 0,
-        end = 0.6
-    ) + 
-    
-    # guides
-    guides(color = guide_legend(override.aes = list(size = rel(0.5)))) + 
+    # *** plot
 
-    # axis labels
-    labs(
-         x = '# of residues', 
-         y = 'response time'
-    ) + 
-    
-    # default theme 
-    theme_bw() +
+    plot <- 
 
-    # default override
-    theme(
-        plot.title = element_blank(), 
-        plot.margin = margin(0,15,0,0), 
+        ggplot(df, aes(gram_count, timing, group = app, color = app)) +
+            
+        # geoms
+        geom_point(
+            size = rel(0.75)
+        ) + 
 
-        panel.grid = element_blank(),
+        # scales
+        scale_color_manual(
+            values = p_colors,
+            labels = p_levels
+        ) + 
+
+        # guides
+        guides(color = guide_legend(override.aes = list(size = rel(0.5)))) + 
+
+        # axis labels
+        labs(
+             x = 'residue count', 
+             y = 'response time (seconds)'
+        ) + 
         
-        axis.text = element_text(size = 7), 
-        axis.title = element_text(size = 8), 
-        
-        legend.text = element_text(size = 7),
-        legend.title = element_blank(), 
-        legend.position = 'bottom',
-        legend.margin = unit(0,'mm'),
-        legend.direction = 'horizontal'
-    ) 
+        # title
+        ggtitle(p_title)
 
-ggsave('response.eps', width = 3, height = 2.0)
+    # *** theme
+    
+    theme <-  
 
[…]

### 2018-11-05 figures/response.R
plots

@@ -23,15 +23,20 @@ get_timing_plot <- function(p_title, p_file, p_levels, p_colors, p_y_axis) {
         geom_point(
             size = rel(0.75)
         ) + 
+        geom_smooth(     
+            size = rel(0.5),
+            show.legend = FALSE
+        ) + 
 
         # scales
         scale_color_manual(
             values = p_colors,
             labels = p_levels
         ) + 
-
-        # guides
-        guides(color = guide_legend(override.aes = list(size = rel(0.5)))) + 
+        scale_y_continuous(
+            trans = "log10",
+            limits = c(1,10000)
+        ) + 
 
         # axis labels
         labs(

### 2018-11-07 docs/rupee.tex
error reporting
paper

@@
 
-RUPEE has two modes of operation, fast and regular. 
+RUPEE has two modes of operation, fast and top-aligned. 
 Fast mode is significantly faster than all other protein structure searches discussed below but at the expensive of accuracy.
 Despite this, we will show that the accuracy of RUPEE in fast mode is not far below that of the best available structure searches. 
-On the other hand, the accuracy and response times of RUPEE in regular mode are comparable to currently available protein structure searches that are commonly considered fast.
+On the other hand, the accuracy and response times of RUPEE in top-aligned mode are comparable to currently available protein structure searches that are commonly considered fast.
 
@@
 Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features. 
-Min-hashing and locality sensitive hashing (LSH), techniques drawn from big-data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and slow.
+Min-hashing and locality sensitive hashing (LSH), techniques drawn from big-data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and top-aligned.
 
@@
 
-\begin{figure*}[tb]
+\begin{figure*}[t]
 \centering
-\includegraphics{torsion_plots}
+\includegraphics{combined_torsion}
 \caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
-\label{fig:torsion_plots}
+\label{fig:combined_torsion}
 \end{figure*}
@@
 
-To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution, CATH s35 representatives to account for precision and redundancy, respectively. 
-A Ramachandran plot of the sampled torsions angles is shown to the left in \figurename~\ref{fig:torsion_plots}. 
+To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution CATH s35 representatives to account for precision and redundancy, respectively. 
+A Ramachandran plot of the sampled torsions angles is shown to the left in \figurename~\ref{fig:combined_torsion}. 
 As can be seen, a single cluster of residues, consisting primarily of $\beta$-strands, appears at all 4 corners of the Ramachandran plot.
@@
 
-To the right in \figurename~\ref{fig:torsion_plots}, we plot the same torsion angles appearing in the Ramachandran plot using a polar plot. 
+To the right in \figurename~\ref{fig:combined_torsion}, we plot the same torsion angles appearing in the Ramachandran plot using a polar plot. 
 In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
@@
 
-Polar plots for each group of DSSP assignment codes along with defined regions and descriptor designations are shown in \figurename~\ref{fig:torsion_refs}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
+\begin{figure*}[tb]
+\begin{center}
+\includegraphics{regions}
+\end{center}
+\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
+\label{fig:regions}
+\end{figure*}
+
+Polar plots for each group of DSSP assignment codes along with defined regions and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
 For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
@@
 
-\begin{figure*}[tb]
+\begin{figure}[tb]
 \begin{center}
-\includegraphics{torsion_refs}
+\includegraphics[width=3in,keepaspectratio]{1nycA00}
 \end{center}
-\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
-\label{fig:torsion_refs}
-\end{figure*}
+\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
+\label{fig:beta_turn}
+\end{figure}
 
-Our initial use of Ramachandran plots to identify regions resulted in the frequent case of highly similar domains from the same CATH s95 clusters being considered significantly different. 
-Alignment of these domains in PyMOL \cite{PyMOL} and the development of a script to label residues with their descriptors showed that slight differences in structure often resulted in distinct descriptors being assigned to aligned residues.
-Once we defined regions using the less confusing polar plots, this discrepancy was no longer observed.
-
-As an example of our linear encoding, the following sequence of descriptors represents a $\beta$-turn-$\beta$ motif followed by bends and coil.
+As an example of our linear encoding, we apply our method to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
+The corresponding sequence of residue descriptors is shown below.
 \begin{gather}\label{E:descrseq} 
-    [\, 5, 5, 5, 5, 5, 11, 11, 5, 5, 5, 5, 5, 8, 8, 10, 9 \,]
+    [\, 5, 5, 5, 5, 5, 5, 7, 5, 11, 11, 5, 5, 5, 5, 5, 5 \,]
 \end{gather}
@@
     \begin{split}
-    \{\,&[5, 5, 5, 5], [5, 5, 5, 5], [5, 5, 5, 11], [5, 5, 11, 11], \\
-        & [5, 11, 11, 5], [11, 11, 5, 5], [11, 5, 5, 5], [5, 5, 5, 5], \\
-        & [5, 5, 5, 5], [5, 5, 5, 8], [5, 5, 8, 8], [5, 8, 8, 10], \\
-        & [8, 8, 10, 9] \,\}
+        \{\,&[5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 7] \\
+            & [5, 7, 5], [7, 5, 11], [5, 11, 11], [11, 11, 5], [11, 5, 5] \\
+            & [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5] \,\}
     \end{split}
@@
 \begin{gather}\label{E:hashdef}
-    s_{hash} = s_1 \times 13^3 + s_2 \times 13^2 + s_3 \times 13 + s_4
+    s_{hash} = s_1 \times 13^2 + s_2 \times 13 + s_3
 \end{gather}
@@
     \begin{split}
-    \{\,&11900, 11900, 11906, 11984, 12992, \\
-        &26096, 25082, 11900, 11900, 11903, \\
-        &11942, 12451, 19067 \,\}
+    \{\,&915, 915, 915, 915, 917, 941, 1259 \\
+        &999, 2007, 1929, 915, 915, 915, 915 \,\}
     \end{split}
@@
 
-Notice in (\ref{E:hashbag}) the value 11900, corresponding to the shingle $[ 5, 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
+Notice in (\ref{E:hashbag}) the value 915, corresponding to the shingle $[ 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
 Since most proteins are dominated by regular secondary structure, the abundance of shingles for $\beta$-strands as well as the three types of helices, end up dominating comparisons. 
@@
 \begin{align}
-    [\, 0, 1, 2, 1, 0, 0, 0, 0, 1, 2, 1, 0, 0, 0, 0, 0 \,].
+    [\, 0, 1, 2, 2, 1, 0, 0, 0, 0, 0, 0, 1, 2, 2, 1, 0 \,].
 \end{align}
@@
     \begin{split}
-    \{\,&011900, 111900, 211906, 111984, 012992, \\
-        &026096, 025082, 011900, 111900, 211903, \\
-        &111942, 012451, 019067 \,\}
+    \{\,&00915, 10915, 20915, 20915, 10917, 00941, 01259 \\
+        &00999, 02007, 01929, 00915, 10915, 20915, 20915 \,\}
     \end{split}
@@
 
-Together, min-hashing and LSH provide the foundation for both operating modes of RUPEE, fast and regular.
+Together, min-hashing and LSH provide the foundation for both operating modes of RUPEE, fast and top-aligned.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
+RUPEE provides 2 operating modes, fast and top-aligned. 
+Each operating mode builds on the results provided by the min-hashing and LSH system described above. 
+When a structure search is executed in either mode, a number of concurrent tasks are executed corresponding to the number of bands used for LSH. 
+These concurrent tasks identify candidate matches based on a single band match and then validate the matches based on a comparison of min-hashes.
+
+In fast mode, the top 8,000 matches are obtained along with the original gram sequences defined for the structures.
+A further validation is done by performing a longest common subsequence (LCS) analysis of the matched gram sequences and adjusting the Jaccard similarity scores accordingly.
+This step accounts for possible gram matches among pairs of structures that are out of order since the min-hashing and LSH techniques themselves do not consider the order of the gram matches.
+The final step of fast mode is to sort the matches based on the adjusted scores and return the results.
+
+Top-aligned is an additional step following fast mode. 
+First, unoptimized CE alignments are performed on the top 2,000 matches obtained from fast mode. 
+Then optimized CE alignments are performed on the top 400 matches and these are finally returned sorted either by RMSD or TM-Score. 
+Currently, top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.
 

### 2018-11-07 docs/rupee.tex
paper

@@
 
-\subsection{Results subsection one}
+Protein structure searches can be evaluated using pairwise alignment scores or by comparison of results against the hierarchy of a protein structure classification database.
+The RMSD of aligned residues is widely used in evaluations but is not perfectly suited to full-length comparisons between structures since distances between unaligned residues are not factored into the score.
+On the other hand, the TM-score \cite{Zhang2004} takes all residues into account. 
+Among protein structure classification databases for which corresponding structure searches exist, SCOPe \citep{Fox2013} and CATH \citep{Orengo1997} are the most popular.
+
+For our results, we have created 3 benchmarks (scop\_d360, scop\_d62, and cath\_d99) for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
+scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains for which mTM returns 100 or more results defined in SCOPe 2.07. 
+Similarly, scop\_d62 is derived from the d500 benchmark filtered for domains defined in SCOP 1.73 for which SSM returns 50 or more results.  
+In keeping with our description of RUPEE in \cite{Ayoub2017}, the cath\_d99 benchmark contains 99 superfamily representatives from the top 100 most diverse superfamilies defined in CATH v4.2 for which CATHEDRAL returns results in less than 12 hours.
+
+We perform pairwise evaluations to ensure the fairness of our comparisons. 
+First, For domain searches, SSM is working with the SCOP 1.73 database, so accordingly we operate RUPEE on SCOP 1.73 domains to ensure RUPEE does not have more domains to work with for scoring and precision evaluations.
+Second, mTM is updated to work with SCOP 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
+On the other hand, CATHEDRAL presents no such challenges but still requires a separate benchmark since it is working with a distinct hierarchy, CATH v4.2.
+
+All benchmark definitions can be found in the supplementary material.
+
+\subsection{Scoring}
+
+\figurename~\ref{fig:combined_scoring_ce} shows average cumulative values for each ranked result averaged over all searches.
+Both RMSD and TM-score values are shown, provided as outputs from CE pairwise alignments. 
+References lines are drawn in the TM-score plot in \figurename~\ref{fig:combined_scoring_ce} at TM-scores of 0.5 and 0.17. 
+A TM-score above 0.5 is a good predictor for whether or not two domains are in the same fold \cite{Xu2010}.
+TM-scores greater than 0.17 are considered potentially meaningful whereas TM-scores less than 0.17 are considered to be due to random alignment \cite{Zhang2004}.
+
+\begin{figure*}[tb]
+\begin{center}
+\includegraphics{combined_scoring_ce}
+\end{center}
+\caption{Evaluation of scoring from CE pairwise alignments}
+\label{fig:combined_scoring_ce}
+\end{figure*}
+
+A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in the supplementary material. 
+The same relative relationships hold with only small variations.
+
+All of RUPEE fast and top-aligned, sorted by RMSD and TM-Score, perform better than SSM and CATHEDRAL.
+The scoring in the cath\_d99 benchmark comparisons are notably lower than for the other two benchmarks. 
+This is expected since CATHEDRAL only returns CATH s35 representatives and for this comparison RUPEE is filtered for s35 representatives to match. 
+Given that the cath\_d99 benchmark is evaluated against representatives, there are fewer highly similar structures returned in the results.
+
+In our evaluation, mTM faired better than SSM and CATHEDRAL. 
+For TM-Score, RUPEE and mTM are nearly identical. 
+For RMSD, RUPEE does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
+If mTM sorted by RMSD then we feel the results again would be nearly identical.
+Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
+
+\subsection{Precision}
+
+\figurename~\ref{fig:combined_precision} shows precision (i.e.
+positive predictive value or PPV) averaged over all searches, where positive results are defined as domains with the same classification for the indicated hierarchy level as the query domain.
+Here is where things get interesting. 
+We should expect a structure search of a given database to have reasonable precision with respect to the hierarchy levels of the structure database it is searching against. 
+However, it is not clear how to define reasonable. 
+In addition, high precision beyond a certain level to some degree is a measure of the usefulness of the results. 
+If precision is too high then a search ends up not providing results more interesting than the what the hierarchicy already defined, in which case it would be sufficient for a search to return the best match and from their refer to the hierarchy.
+
+\begin{figure*}[tb]
+\begin{center}
+\includegraphics{combined_precision}
+\end{center}
+\caption{Something Something}
+\label{fig:combined_precision}
+\end{figure*}
+
+\subsection{Response Times}
 
@@
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+
+\begin{figure*}[tb]
+\begin{center}
+\includegraphics{combined_response}
+\end{center}
+\caption{Something Something}
+\label{fig:combined_response}
+\end{figure*}
+
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
@@
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Text. Text. Text.
 
-\subsection{Results subsection two}
+\section{DISCUSSION}
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

### 2018-11-07 docs/rupee.tex
plots

@@
 positive predictive value or PPV) averaged over all searches, where positive results are defined as domains with the same classification for the indicated hierarchy level as the query domain.
-Here is where things get interesting. 
-We should expect a structure search of a given database to have reasonable precision with respect to the hierarchy levels of the structure database it is searching against. 
+Here, RUPEE is 
+A plot of recall is unnecessary since \figurename~\ref{fig:combined_precision} provides precision at specific ranks for identical sets of searches.
+Hence, recall curves have the same relative relationships as those shown for precision.
+
+We should expect a structure search to have reasonable precision with respect to the hierarchy levels of the structure classification it is searching. 
 However, it is not clear how to define reasonable. 
-In addition, high precision beyond a certain level to some degree is a measure of the usefulness of the results. 
-If precision is too high then a search ends up not providing results more interesting than the what the hierarchicy already defined, in which case it would be sufficient for a search to return the best match and from their refer to the hierarchy.
+On the other hand, if precision is too high, the search provides little value beyond that provided by the structure classification hierarchy it is searching. 
+That is, it would be sufficient for a search to return the best match and from their refer to the hierarchy.
 
@@
 \end{figure*}
+
+Similar to scoring evaluations above, all of RUPEE fast and top-aligned, sorted by RMSD and TM-Score, perform better than SSM and CATHEDRAL.
 

### 2018-11-07 figures/combined_response.R

@@ -39,22 +39,22 @@ grid_arrange_shared_legend <-
 dummy_plot <- get_timing_plot(
         'dummy timing',
         'response_dummy.txt',
-        c('RUPEE', 'RUPEE Fast', 'mTM', 'SSM','CATHEDRAL'), 
-        c('#e41a1c', '#377eb8', '#4daf4a', '#984ea3','#ff7f00'),
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'mTM', 'SSM','CATHEDRAL'), 
+        c('#e41a1c', '#4daf4a', '#984ea3', '#ff7f00', '#a65628'),
         TRUE
 )
 scop_plot <- get_timing_plot(
         'scop_d62 timing',
         'response_scop_d62.txt',
-        c('RUPEE', 'RUPEE Fast', 'mTM', 'SSM'), 
-        c('#e41a1c', '#377eb8', '#4daf4a', '#984ea3'),
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'mTM', 'SSM'), 
+        c('#e41a1c', '#4daf4a', '#984ea3', '#ff7f00'),
         TRUE
 )
 cath_plot <- get_timing_plot(
         'cath_d99 timing',
         'response_cath_d99.txt',
-        c('RUPEE', 'RUPEE Fast', 'CATHEDRAL'), 
-        c('#e41a1c', '#377eb8', '#ff7f00'),
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'CATHEDRAL'), 
+        c('#e41a1c', '#4daf4a', '#a65628'),
         FALSE
 )
 

### 2018-11-07 docs/rupee.tex
paper

@@
 
-\begin{figure*}[t]
+\begin{figure*}[tb]
 \centering
@@
 For our results, we have created 3 benchmarks (scop\_d360, scop\_d62, and cath\_d99) for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
-scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains for which mTM returns 100 or more results defined in SCOPe 2.07. 
+scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains in SCOPe 2.07 for which mTM returns 100 or more results.
 Similarly, scop\_d62 is derived from the d500 benchmark filtered for domains defined in SCOP 1.73 for which SSM returns 50 or more results.  
@@
 Both RMSD and TM-score values are shown, provided as outputs from CE pairwise alignments. 
-References lines are drawn in the TM-score plot in \figurename~\ref{fig:combined_scoring_ce} at TM-scores of 0.5 and 0.17. 
 A TM-score above 0.5 is a good predictor for whether or not two domains are in the same fold \cite{Xu2010}.
@@
 
-All of RUPEE fast and top-aligned, sorted by RMSD and TM-Score, perform better than SSM and CATHEDRAL.
+RUPEE fast and top-aligned, sorted by both RMSD and TM-Score, perform better than SSM and CATHEDRAL.
 The scoring in the cath\_d99 benchmark comparisons are notably lower than for the other two benchmarks. 
-This is expected since CATHEDRAL only returns CATH s35 representatives and for this comparison RUPEE is filtered for s35 representatives to match. 
+This is expected since CATHEDRAL only returns CATH s35 representatives.
+Likewise, for this comparison RUPEE is filtered for s35 representatives to match. 
 Given that the cath\_d99 benchmark is evaluated against representatives, there are fewer highly similar structures returned in the results.
@@
 In our evaluation, mTM faired better than SSM and CATHEDRAL. 
-For TM-Score, RUPEE and mTM are nearly identical. 
+For TM-Score, RUPEE and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
 For RMSD, RUPEE does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
-If mTM sorted by RMSD then we feel the results again would be nearly identical.
+If mTM sorted by RMSD we feel the results again would be nearly identical.
 Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
@@
 positive predictive value or PPV) averaged over all searches, where positive results are defined as domains with the same classification for the indicated hierarchy level as the query domain.
-Here, RUPEE is 
 A plot of recall is unnecessary since \figurename~\ref{fig:combined_precision} provides precision at specific ranks for identical sets of searches. 
@@
 On the other hand, if precision is too high, the search provides little value beyond that provided by the structure classification hierarchy it is searching. 
-That is, it would be sufficient for a search to return the best match and from their refer to the hierarchy.
+Towards the extreme end of high precision, it would be sufficient for a search to return the best match and from there refer to the hierarchy for additional results.
 
@@
 
-Similar to scoring evaluations above, all of RUPEE fast and top-aligned, sorted by RMSD and TM-Score, perform better than SSM and CATHEDRAL.
+Similar to the scoring evaluations above, RUPEE fast and top-aligned, sorted by both RMSD and TM-Score, show higher precision than SSM and CATHEDRAL with the exception of RUPEE top-aligned sorted by RMSD for ranks lower than 10 compared against SSM.
+
+Again, mTM faired better than SSM and CATHEDRAL. 
+Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-Score. 
+In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be lead to regard this as a negative result. 
+However, to the contrary, in the presence of \figurename~\ref{fig:combined_scoring_ce}, where it is shown that RUPEE and mTM have almost identical scoring, this result is remarkable. 
+This disparity suggest that RUPEE is better able to find significantly similar matches not necessarily aligned with the SCOP hierarchy. 
+In fact, since the initial min-hashing and LSH technique used by RUPEE check for similarity to all available structures, no structure is able to hide behind a sequence based cluster representative. 
+So this result is in keeping with how RUPEE is intended to work and how it is described above.
 

### 2018-11-08 docs/rupee.tex
paper

@@
 \end{center}
-\caption{Something Something}
+\caption{Precision plots for scop\_d360, scop\_d62, and cath\_d99 benchmarks}
 \label{fig:combined_precision}
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+\figurename~\ref{fig:combined_response} shows response times in seconds for the scop\_d62 and cath\_d99 benchmarks. 
+Here, we are able to show RUPEE, mTM and SSM on the same plot because scop\_d62 is a subset of the scop\_d360 benchmark. 
+Both plots are shown with a logarithmic scale in order to include all outliers while still being able to view the overall trends in response times.
 
@@
 \end{center}
-\caption{Something Something}
+\caption{Response time plots for scop\_d62 and cath\_d99 benchmarks}
 \label{fig:combined_response}
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+In all cases, RUPEE in fast mode is considerably faster than all other searches. 
+It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to CATHEDRAL and RUPEE in top-aligned mode.
+Response times for SSM are not affected by residue counts at all and always returns results in less than 100 seconds but this is at the expense of performance as shown in \figurename~\ref{fig:combined_scoring_ce}.
+
+In the left plot of \figurename~\ref{fig:combined_response}, it is shown that RUPEE in top-aligned mode is faster than mTM for residue counts below 200, but then response times for RUPEE increase beyond that of mTM.
+Down the stretch mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times.
+
+The trend of increasing response times for RUPEE in top-aligned mode is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.
+
+Response times to a large degree are a measure of the amount of resources available to an application. 
+In the case of RUPEE, our response times were gathered from RUPEE running on a fairly old laptop with a 2nd generation Intel\textregistered{} Core\texttrademark{} i7-2720QM Quad-Core CPU and 8 GB of memory.
+With more resources the response times of RUPEE can be further improved since pairwise alignments can be run in parallel. 
+For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
 

### 2018-11-08 docs/rupee.tex
paper

@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+Not to understate the significance of what has been shown, that a purely geometric sequence alignment-free big data approach to protein structure search can compete with the current state of the art protein structure searches available, there remains challenges for RUPEE to address in addition to avenues for further investigation.
+
+While our min-hashing and LSH scheme does allow for some flexibility in the size of matched protein structures, it is not specifically designed for containment searches. 
+However, the initial min-hashing and LSH search does operate fast enough, within seconds, that it does present the possibility of executing multiple searches. 
+With more resources, we can distribute min-hash and band data across multiple compute units, with each data set representing a subset of chopped domain representations. 
+With a 75\% overlap of these subsets, RUPEE searches effectively become containment searches.
+
+We have tried the overlapping subset idea and have found it to be effective. 
+However, on a single compute unit, the time required is more than we are willing to accept for this first iteration of RUPEE.
+
+One possible drawback of RUPEE is that in both fast and top-aligned modes, it only returns the top 400 results. 
+Again, with more resources, this number can be increased, but there still remains a need for a cut-off.
+
+In most search domains, having to looking past the first few hundred results usually indicates an ineffective search strategy.
+For instance, RUPEE provides filters that can be used for traversing structure space more efficiently. 
+For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query domain at a chosen hierarchy level classification. 
+Additionally, for CATH you can filter results based on hierarchy level representatives. 
+Since RUPEE does not rely on sequence clusters, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.
+
+One area that stands out for possible improvement is our longest common subsequence (LCS) scoring adjustment to the results initially returned by RUPEE. 
+While the LCS step has been shown to be effective, it is notable for its simplicity. 
+A more complex step of validating the sequence of gram matches can take a form similar to the path extension algorithm used by CE. 
+In this case, sequences of matches would only be extended when the difference of interresidue distances between gram pairs already in the sequence and a candidate pair to be added to the sequence fall below some threshold.
+
+On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the grams themselves could lead.
+Sin
+
+As can be observed from Figure 4 and Figure 5, there are good domain matches with the SCOP hierarchy that mTM is able to find that RUPEE does not. 
+Conversely, there are good domain matches outside not aligned with the SCOP hierarchy that RUPEE finds and mTM is not. 
+A comprehensive listing of these difference may find interesting similarities not previously known.
 

### 2018-11-08 docs/rupee.tex
paper

@@
-\documentclass[a4,center,fleqn]{NAR}
+\documentclass[letter,center,fleqn]{NAR}
 
@@
 
-To see why RPE run factors are calculated at the descriptor level and factored in at the shingle level, consider shingling a list of RPE run factors themselves, which mirrors applying them at the descriptor level.
-\begin{align*}
-    &\text{The sequence of RPE factors} \\
-    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 1, 2, 3], [1, 2, 3, 2], [2, 3, 2, 1], [3, 2, 1, 0] \,\} \\
-    &\text{and with one less element} \\
-    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 1, 2, 2], [1, 2, 2, 1], [2, 2, 1, 0] \,\}
-\end{align*}
-Notice above, there is not a single match for this one-off difference in run length.
-Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
-\begin{align*}
-    &\text{The sequence of RPE factors} \\
-    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2], [3, 3, 3, 3] \,\} \\
-    &\text{and with one less element} \\
-    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2] \,\}
-\end{align*}
-In this latter case, a one-off difference in run length results in one less shingle match while still serving to increase the specificity of the shingles.
-
 Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \cite{Levan1971} for multisets,

### 2018-11-08 docs/rupee.tex
paper

@@
 
-Polar plots for each group of DSSP assignment codes along with defined regions and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
+Polar plots for each group of DSSP assignment codes along with defined region and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
 For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
@@
 We have adapted the syntactic approach to document similarity, often referred to as shingling \cite{Broder1997a}, to our linear encoding of protein structure. 
-We transform a linear sequence of descriptors into a multiset of shingles consisting of 4 consecutive descriptors.
+We transform a linear sequence of descriptors into a multiset of shingles consisting of 3 consecutive descriptors.
 The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
@@
 
-For our results, we have created 3 benchmarks (scop\_d360, scop\_d62, and cath\_d99) for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
+For our results, we have created 3 benchmarks, scop\_d360, scop\_d62, and cath\_d99, for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
 scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains in SCOPe 2.07 for which mTM returns 100 or more results.
@@
 First, For domain searches, SSM is working with the SCOP 1.73 database, so accordingly we operate RUPEE on SCOP 1.73 domains to ensure RUPEE does not have more domains to work with for scoring and precision evaluations.
-Second, mTM is updated to work with SCOP 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
+Second, mTM is updated to work with SCOPe 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
 On the other hand, CATHEDRAL presents no such challenges but still requires a separate benchmark since it is working with a distinct hierarchy, CATH v4.2.
@@
 \figurename~\ref{fig:combined_scoring_ce} shows average cumulative values for each ranked result averaged over all searches.
-Both RMSD and TM-score values are shown, provided as outputs from CE pairwise alignments. 
+Both RMSD and TM-score values are shown, provided as outputs from optimized CE pairwise alignments. 
 A TM-score above 0.5 is a good predictor for whether or not two domains are in the same fold \cite{Xu2010}.
@@
 Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-Score. 
-In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be lead to regard this as a negative result. 
+In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be led to regard this as a negative result. 
 However, to the contrary, in the presence of \figurename~\ref{fig:combined_scoring_ce}, where it is shown that RUPEE and mTM have almost identical scoring, this result is remarkable. 
-This disparity suggest that RUPEE is better able to find significantly similar matches not necessarily aligned with the SCOP hierarchy. 
+This disparity suggest that RUPEE is better able to find significantly similar matches not necessarily aligned with the SCOPe hierarchy. 
 In fact, since the initial min-hashing and LSH technique used by RUPEE check for similarity to all available structures, no structure is able to hide behind a sequence based cluster representative. 
@@
 Both plots are shown with a logarithmic scale in order to include all outliers while still being able to view the overall trends in response times. 
+Loess regression curves are also provided to further highlight the overall trends.
 
@@
 
-In all cases, RUPEE in fast mode is considerably faster than all other searches. 
-It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to CATHEDRAL and RUPEE in top-aligned mode.
+In all cases, RUPEE fast is considerably faster than all other searches. 
+It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to CATHEDRAL and RUPEE top-aligned.
 Response times for SSM are not affected by residue counts at all and always returns results in less than 100 seconds but this is at the expense of performance as shown in \figurename~\ref{fig:combined_scoring_ce}.
 
-In the left plot of \figurename~\ref{fig:combined_response}, it is shown that RUPEE in top-aligned mode is faster than mTM for residue counts below 200, but then response times for RUPEE increase beyond that of mTM.
-Down the stretch mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times.
+In the left plot of \figurename~\ref{fig:combined_response}, it is shown that RUPEE top-aligned is faster than mTM for residue counts below 200, but then response times for RUPEE increase beyond that of mTM.
+Down the stretch, mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times.
 
-The trend of increasing response times for RUPEE in top-aligned mode is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.
+The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.
 
@@
 
-Not to understate the significance of what has been shown, that a purely geometric sequence alignment-free big data approach to protein structure search can compete with the current state of the art protein structure searches available, there remains challenges for RUPEE to address in addition to avenues for further investigation.
+Not to understate the significance of what has been shown, that a purely geometric alignment-free big data approach to protein structure search can compete with the current state of the art protein structure searches available, there remains challenges for RUPEE to address in addition to avenues for further investigation.
 
 While our min-hashing and LSH scheme does allow for some flexibility in the size of matched protein structures, it is not specifically designed for containment searches. 
-However, the initial min-hashing and LSH search does operate fast enough, within seconds, that it does present the possibility of executing multiple searches. 
-With more resources, we can distribute min-hash and band data across multiple compute units, with each data set representing a subset of chopped domain representations. 
+However, the initial min-hashing and LSH search does operate fast enough, within seconds, that it does present the possibility of executing multiple searches within the context of a single query. 
+With more resources, we can distribute min-hash and band data across multiple compute units, with each data set representing a subset of chopped structure representations. 
 With a 75\% overlap of these subsets, RUPEE searches effectively become containment searches.
@@
 One possible drawback of RUPEE is that in both fast and top-aligned modes, it only returns the top 400 results. 
-Again, with more resources, this number can be increased, but there still remains a need for a cut-off.
+Again, with more resources, this number can be increased, but there still remains a need for some kind of cut-off.
 
-In most search domains, having to looking past the first few hundred results usually indicates an ineffective search strategy.
-For instance, RUPEE provides filters that can be used for traversing structure space more efficiently. 
-For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query domain at a chosen hierarchy level classification. 
+In most search tools, having to looking past the first few hundred results usually indicates an ineffective search strategy.
+To this end, RUPEE provides filters that can be used for traversing structure space more efficiently. 
+For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query structure at a chosen hierarchy level classification. 
 Additionally, for CATH you can filter results based on hierarchy level representatives. 
@@
 On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the grams themselves could lead.
-Sin
+For instance, topological permutations such as circular permutations, segment-swapping and changing secondary structures within homologous proteins are not uncommon \cite{Andreeva2007}. 
+The initial RUPEE min-hashing and LSH algorithm provides candidate matches along with matched grams. 
+With some thought, an algorithm similar to FATCAT can be developed allowing for permutations in addition to twists.
 
-As can be observed from Figure 4 and Figure 5, there are good domain matches with the SCOP hierarchy that mTM is able to find that RUPEE does not. 
-Conversely, there are good domain matches outside not aligned with the SCOP hierarchy that RUPEE finds and mTM is not. 
+As can be observed from considering \figurename~\ref{fig:combined_scoring_ce} and \figurename~\ref{fig:combined_precision} together, there are good domain matches aligned with the SCOPe hierarchy that mTM is able to find that RUPEE does not.
+Conversely, there are good domain matches not aligned with the SCOPe hierarchy that RUPEE finds and mTM does not. 
 A comprehensive listing of these difference may find interesting similarities not previously known.

### 2018-11-08 docs/rupee.tex
paper

@@
 \begin{abstract}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text.
+Given the close relationship between protein structure and function, protein structure searches have long played an established role in bioinformatics. 
+Despite their maturity, existing protein structure searches either compromise between fast response times and quality of results or use simplifying assumptions. 
+These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.\\
+We have developed a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles. 
+Along the way, we introduce a new torsion angle plot to assist in identifying separable regions of torsion angles. 
+Subsequently, we introduce a new heuristic we call \emph{run position encoding}, for handling the lack of specificity of items within character sequences containing runs of repeats. 
+Comparing our results to the output of the CATH structural scan, response times are measured in seconds as opposed to minutes and average RMSDs and TM-scores are better. 
+Our approach is a step towards a comprehensive indexing of protein structures scalable to millions of entries.\\
+The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. 
+Code and data are available at \url{https://github.com/rayoub/rupee}.\\
 \end{abstract}
@@
 On the other hand, the accuracy and response times of RUPEE in top-aligned mode are comparable to currently available protein structure searches that are commonly considered fast.
+
+RUPEE stands out as not just another protein structure search, of which there are many. 
+RUPEE is the first, to our knowledge, purely geometric protein structure search to achieve results as good as the current state of the art protein structure searches. 
+Additionally, it can be argued that the kinds of matches RUPEE returns have more added value than the current state of the art in that with equal scores it is able to return results not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as PDB-90.
+In this regard, RUPEE makes a fundamental contribution to protein structure research that lends itself to being leveraged in existing systems. 
+It also provided a path for further research activity in the direction of big data represenations of protein structures.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+With the growth rate of solved structures deposited in the PDB, the need for a fast and scalable structure search is growing. 
+Using run position encoded shingles of residue descriptors combined with min-hashing and LSH, we have shown that RUPEE is able to provide good results in seconds running on an 8-core laptop against the RUPEE index in a PostgreSQL database, serviced by a single thread.
+RUPEE response times may be further improved by the structural near dupe clustering of domains for use in a filtering step not dependent on clusters derived from sequence data.
+
+Aside from response times and scalability, there is room for improvement in RUPEE, especially with respect to encoding the unstructured regions of proteins.
+For short loops containing simple motifs such as the $\beta$-turn-$\beta$ motif, shingle matches correctly factor into RUPEE similarity comparisons. 
+However, with the longer and more complex loop and tail regions, random matching and mismatching takes a toll further down in the list of ranked results.
+
+In addition to RUPEE, we have introduced two items that may find wider applicability. 
+The first item is the introduction of a new polar torsion angle plot that maintains the continuity of permissible torsion angle regions while maintaining the familiar torsion angle ranges used in Ramachandran plots.
+The next item is the \emph{run position encoding} heuristic, which may find wider applicability due to it simplicity and generality.
 

### 2018-11-08 docs/rupee.tex
abstract

@@
 Despite their maturity, existing protein structure searches either compromise between fast response times and quality of results or use simplifying assumptions. 
-These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.\\
+These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.
 We have developed a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles. 
-Along the way, we introduce a new torsion angle plot to assist in identifying separable regions of torsion angles. 
-Subsequently, we introduce a new heuristic we call \emph{run position encoding}, for handling the lack of specificity of items within character sequences containing runs of repeats. 
-Comparing our results to the output of the CATH structural scan, response times are measured in seconds as opposed to minutes and average RMSDs and TM-scores are better. 
-Our approach is a step towards a comprehensive indexing of protein structures scalable to millions of entries.\\
-The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. 
-Code and data are available at \url{https://github.com/rayoub/rupee}.\\
+Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for alignment-free big data approaches to protein structure searches, producing equal or better results than the current state of the art in protein search.
+
+The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. Code and data are available at \url{https://github.com/rayoub/rupee}.
 \end{abstract}

### 2018-11-12 docs/rupee.tex
paper

--- 2018-11-08 docs/rupee.tex
@@
 \usepackage{booktabs}
+\usepackage{placeins}
 
@@
 
-\title{Article title}
+\title{RUPEE: A fast and accurate purely geometric protein structure search}
 
@@
 \begin{abstract}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text.
+Given the close relationship between protein structure and function, protein structure searches have long played an established role in bioinformatics. 
+Despite their maturity, existing protein structure searches either use simplifying assumptions or compromise between fast response times and quality of results. 
+These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.
+We have developed RUPEE, a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
+Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for purely geometric big data approaches to protein structure searches, producing equal or better results than the current state of the art in protein structure search.
+
+The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. Code and data are available at \url{https://github.com/rayoub/rupee}.
 \end{abstract}
@@
 
-Given a protein domain identifier, whole chain identifier or an uploaded file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or else among whole chains defined in the PDB.
+Given a protein domain identifier, whole chain identifier or an uploaded PDB file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or among whole chains defined in the PDB.
 In contrast to currently available protein structure searches, RUPEE is able to search either of these databases using any identifier. 
@@
 
+\begin{figure*}[b]
+\centering
+\includegraphics{combined_torsion}
+\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
+\label{fig:combined_torsion}
+\end{figure*}
+
 For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
@@
 
-\begin{figure*}[tb]
-\centering
-\includegraphics{combined_torsion}
-\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
-\label{fig:combined_torsion}
-\end{figure*}
-
 Despite their utility and familiarity, Ramachandran plots \cite{Ramachandran1968} represent angular data using a square plot better suited for scalar data.
@@
 To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution CATH s35 representatives to account for precision and redundancy, respectively. 
-A Ramachandran plot of the sampled torsions angles is shown to the left in \figurename~\ref{fig:combined_torsion}. 
+A Ramachandran plot of the sampled torsions angles is shown in the left plot of \figurename~\ref{fig:combined_torsion}. 
 As can be seen, a single cluster of residues, consisting primarily of $\beta$-strands, appears at all 4 corners of the Ramachandran plot.
-
-This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
-Both wrapped and mirrored plots take advantage of the sparsely populated areas of the Ramachandran plot at $\phi = 0\degree$ and $\psi = -120\degree$.
-However, with larger samples of torsion angles, the area at $\psi = -120\degree$ becomes less sparse. 
-The use of a polar plot resolves this elegantly by only requiring one break in continuity at $\phi = 0\degree$.
-
-To the right in \figurename~\ref{fig:combined_torsion}, we plot the same torsion angles appearing in the Ramachandran plot using a polar plot. 
-In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
-Notice the residues appearing at the 4 corners of the Ramachandran plot now appear in one continuous region of the polar plot centered at $\phi = \pm180\degree$ and $\psi = \pm180\degree$.
-
-\subsection{Linear Encoding of Protein Structure}
-
-The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
-The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
 
@@
 
+This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
+Both wrapped and mirrored plots take advantage of the sparsely populated areas of the Ramachandran plot at $\phi = 0\degree$ and $\psi = -120\degree$.
+However, with larger samples of torsion angles, the area at $\psi = -120\degree$ becomes less sparse. 
+The use of a polar plot resolves this elegantly by only requiring one break in continuity at $\phi = 0\degree$.
+
+In the right plot of \figurename~\ref{fig:combined_torsion}, we show the same torsion angles appearing in the Ramachandran plot using a polar plot. 
+In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
+Notice the residues appearing at the 4 corners of the Ramachandran plot now appear in one continuous region of the polar plot centered at $\phi = \pm180\degree$ and $\psi = \pm180\degree$.
+
+\subsection{Linear Encoding of Protein Structure}
+
+The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
+The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
+
 Polar plots for each group of DSSP assignment codes along with defined region and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
@@
 
-\begin{figure}[tb]
+\begin{figure}[b]
 \begin{center}
@@
 
-RUPEE provides 2 operating modes, fast and top-aligned. 
+RUPEE provides two modes, fast and top-aligned. 
 Each operating mode builds on the results provided by the min-hashing and LSH system described above. 
@@
 Then optimized CE alignments are performed on the top 400 matches and these are finally returned sorted either by RMSD or TM-Score. 
-Currently, top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.
+Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.
 
@@
 We perform pairwise evaluations to ensure the fairness of our comparisons. 
-First, For domain searches, SSM is working with the SCOP 1.73 database, so accordingly we operate RUPEE on SCOP 1.73 domains to ensure RUPEE does not have more domains to work with for scoring and precision evaluations.
+First, for domain searches, SSM is working with the SCOP 1.73 database, so accordingly we operate RUPEE on SCOP 1.73 domains to ensure RUPEE does not have more domains to work with for scoring and precision evaluations.
 Second, mTM is updated to work with SCOPe 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
@@
 \end{center}
-\caption{Evaluation of scoring from CE pairwise alignments}
+\caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
 \label{fig:combined_scoring_ce}
@@
 
-RUPEE fast and top-aligned, sorted by both RMSD and TM-Score, perform better than SSM and CATHEDRAL.
+RUPEE fast, top-aligned sorted by RMSD, and top-aligned sorted by TM-Score, perform better than SSM and CATHEDRAL.
 The scoring in the cath\_d99 benchmark comparisons are notably lower than for the other two benchmarks. 
@@
 In our evaluation, mTM faired better than SSM and CATHEDRAL. 
-For TM-Score, RUPEE and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
-For RMSD, RUPEE does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
-If mTM sorted by RMSD we feel the results again would be nearly identical.
+mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-Score points of mTM at the 100$^{th}$ result, which is notable considering its speed.
+
+For TM-Score, RUPEE top-aligned and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
+For RMSD, RUPEE top-aligned does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
+If mTM sorted by RMSD we suspect the results again would be nearly identical.
 Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
@@
 \end{center}
-\caption{Precision plots for scop\_d360, scop\_d62, and cath\_d99 benchmarks}
+\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
 \label{fig:combined_precision}
@@
 \figurename~\ref{fig:combined_response} shows response times in seconds for the scop\_d62 and cath\_d99 benchmarks. 
-Here, we are able to show RUPEE, mTM and SSM on the same plot because scop\_d62 is a subset of the scop\_d360 benchmark. 
+Here, we are able to show RUPEE fast and top-aligned, mTM and SSM on the same plot because scop\_d62 is a subset of the scop\_d360 benchmark. 
 Both plots are shown with a logarithmic scale in order to include all outliers while still being able to view the overall trends in response times. 
@@
 \end{center}
-\caption{Response time plots for scop\_d62 and cath\_d99 benchmarks}
+\caption{Response times for RUPEE fast and RUPEE top-aligned. The response times for RUPEE top-aligned are dominated by pairwise structure alignments and do not depend on the sort order.}
 \label{fig:combined_response}
@@
 Down the stretch, mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times. 
+The right plot of \figurename~\ref{fig:combined_response} shows RUPEE top-aligned is significantly faster than CATHEDRAL for all residue counts.
 
@@
 
-Not to understate the significance of what has been shown, that a purely geometric alignment-free big data approach to protein structure search can compete with the current state of the art protein structure searches available, there remains challenges for RUPEE to address in addition to avenues for further investigation.
+As shown above, a purely geometric big data approach to protein structure search can compete with the current state of the art protein structure searches available.
+Nonetheless, there remain avenues for further improvement and investigation.
 
@@
 Again, with more resources, this number can be increased, but there still remains a need for some kind of cut-off. 
-
-In most search tools, having to looking past the first few hundred results usually indicates an ineffective search strategy.
+Nonetheless, in most search tools, having to looking past the first few hundred results usually indicates an ineffective search strategy.
 To this end, RUPEE provides filters that can be used for traversing structure space more efficiently. 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+With the growth rate of solved structures deposited in the PDB, the need for a fast and scalable structure search is growing. 
+Using run position encoded shingles of residue descriptors combined with min-hashing and LSH, we have shown that RUPEE fast is able to provide good results in seconds running on an Quad-Core laptop.
+Currently, RUPEE fast is the fastest available protein structure search providing the demonstrated level of accuracy. 
+For RUPEE top-aligned, we have shown that a purely geometric big data approach to protein structure search is able to produce results equal to or better than the current state of the art protein structure searches that variously depend on clustered sequences or protein structure classification hierarchies.
+Moreover, we have shown evidence that suggests the results from RUPEE top-aligned provide more added value by discovering high scoring protein structure matches not necessarily aligned with a particular protein structure classification hierarchy or hiding behind a cluster representative.
+The ability for RUPEE to quickly examine all structures among hundreds of thousands sets it apart as a tool that can be used for discovering previously undetected structural similarity relations between proteins rather than just aligning with an already known fold hierarchy.
 

### 2018-11-12 docs/suppl.tex

\documentclass[letter,center,fleqn]{NAR}

\usepackage{textcomp}
\usepackage{lmodern}
\usepackage{gensymb}
\usepackage{booktabs}

\hbadness=99999

\begin{document}

\onecolumn
\section{FIGURES}

\begin{figure*}[h!]
\begin{center}
\includegraphics{combined_scoring_fatcat}
\end{center}
\caption{Evaluation of scoring from FATCAT pairwise alignments}
\label{fig:combined_scoring_fatcat}
\end{figure*}

\newpage

\section{METHODS ADDENDUM}

To see why RPE run factors are calculated at the descriptor level and factored in at the shingle level, consider shingling a list of RPE run factors themselves, which mirrors applying them at the descriptor level. 
\begin{align*}
    &\text{The sequence of RPE factors} \\
    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 1, 2, 3], [1, 2, 3, 2], [2, 3, 2, 1], [3, 2, 1, 0] \,\} \\
    &\text{and with one less element} \\
    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 1, 2, 2], [1, 2, 2, 1], [2, 2, 1, 0] \,\}
\end{align*}
Notice above, there is not a single match for this one-off difference in run length.
Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
\begin{align*}
    &\text{The sequence of RPE factors} \\
    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2], [3, 3, 3, 3] \,\} \\
    &\text{and with one less element} \\
    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2] \,\}
\end{align*}
In this latter case, a one-off difference in run length results in one less shingle match while still serving to increase the specificity of the shingles.

\newpage

\section{BENCHMARKS}

\end{document}

### 2018-11-13 docs/suppl.tex
suppl

@@
 \end{center}
-\caption{Evaluation of scoring from FATCAT pairwise alignments}
+\caption{Scoring from FATCAT pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
 \label{fig:combined_scoring_fatcat}
@@
 \newpage
-
 \section{BENCHMARKS}
 
+\subsection{scop\_d360}
+
+\begin{verbatim}
+d1a1ca_,d1a92b_,d1ao6b1,d1b0ea_,d1bhaa_,d1bspa_,d1bwza1,d1bzqd_,d1c1ba2,d1c3pa_,
+d1c81a_,d1cklf1,d1d5nc1,d1d6ha1,d1d8la1,d1de0a_,d1di0c_,d1djwb2,d1e0ca1,d1e9ha_,
+d1egya_,d1ek1a2,d1f9qa_,d1ffxa_,d1fh9a_,d1fmta2,d1fyfa1,d1fyfa2,d1g3it_,d1g63i_,
+d1gg3b2,d1gk8k_,d1gqme_,d1gtea4,d1gvra_,d1gztd_,d1hnvb_,d1hzyb_,d1i7pa2,d1ia2a_,
+d1ii2a2,d1ik4f_,d1isba2,d1iwao1,d1j6va_,d1jdya3,d1jeqa1,d1jh2a_,d1jjid_,d1jrqb2,
+d1jxja2,d1jyzm3,d1k9jb_,d1kkmb_,d1kkmj_,d1kooc1,d1kpsc_,d1kq4a1,d1krbc2,d1ksda1,
+d1l6kj_,d1lcpa1,d1liwa6,d1lvha_,d1m80a3,d1mokc1,d1mpsh1,d1mwia_,d1ndqa_,d1ni6c_,
+d1nkza_,d1nzwb_,d1o1cv_,d1odsf_,d1ogcd_,d1oh9a_,d1ojna2,d1p9ka1,d1perl_,d1pf9i3,
+d1px3b4,d1q4qf_,d1q6za1,d1q86d_,d1qb8a_,d1qj3b_,d1qrqa_,d1qs7c_,d1qvrc3,d1r67a1,
+d1roma_,d1s5ma_,d1sbka1,d1sg9a_,d1smyk2,d1srgb_,d1sw6b_,d1sxua_,d1szsa1,d1th8a1,
+d1tjta2,d1tkab1,d1tkba3,d1tr9a1,d1ttob_,d1tyzd_,d1tzyd_,d1u9ma_,d1uc8a1,d1uf5a_,
+d1uj1b_,d1uj4a1,d1upla_,d1v1tb1,d1v54u_,d1vq5d1,d1w7ab2,d1w7vd2,d1wpua_,d1x0sa_,
+d1x1yd1,d1x92b1,d1xckd1,d1xmzb1,d1xn2c_,d1xnwe2,d1xuoa_,d1xvaa_,d1xyla_,d1y3be2,
+d1y69k1,d1yf1c_,d1ygcl_,d1yhut_,d1yima_,d1yl4w1,d1yo6c_,d1yq2a4,d1ywhm3,d1z25a3,
+d1z3qa_,d1zcfg_,d1zdja_,d1zqqa4,d220la_,d2avyh1,d2b66k2,d2b7aa_,d2b9nf1,d2b9no1,
+d2bb3a1,d2bfea1,d2bm4a1,d2bq8x_,d2bsqc1,d2c64a2,d2c9lz1,d2ds0a_,d2dtyd_,d2dxia2,
+d2e1va2,d2f3fa_,d2fdsa1,d2fk3c1,d2fugu1,d2g7ga1,d2gdub2,d2gjwd2,d2gmqa1,d2hbxb_,
+d2hd1a_,d2hh2a_,d2hhhc2,d2idrb_,d2igad1,d2itjb_,d2iw6b1,d2j31a1,d2j62b2,d2juaa1,
+d2lq7a1,d2noea1,d2nuwa_,d2o1ba_,d2ofea_,d2oqef1,d2pf2a2,d2plsf2,d2puga2,d2q7qh_,
+d2qbij1,d2qbra_,d2qexc1,d2qp1s1,d2quea_,d2ripa1,d2rmaq_,d2uxcg1,d2uynb_,d2v4eg_,
+d2v6ma2,d2v7xa2,d2vggb2,d2vv6d_,d2vy0b_,d2wipa1,d2wipc1,d2wogb_,d2x7yb_,d2yzdg1,
+d2z0ac1,d2z27b_,d2z4ng1,d2zfzd_,d2zwib_,d3a5cc3,d3abmi_,d3aend_,d3ah3b_,d3anzi1,
+d3aofb_,d3ayzb_,d3b6oa_,d3bc5a1,d3bp9f_,d3bwia_,d3bzub2,d3c6qb_,d3cjbg1,d3cojc2,
+d3d5dp1,d3dh1b1,d3dllw1,d3dugf2,d3dyab_,d3e6kb_,d3ej8a_,d3f1sa_,d3f3yb_,d3flqa_,
+d3foub_,d3fvlc_,d3g3cb1,d3guag1,d3gw1a_,d3gw9b_,d3h66b_,d3h90c2,d3hjjc_,d3hlib_,
+d3hqpf2,d3ikab_,d3is3a_,d3k3ai_,d3k8ca_,d3kfab1,d3kpbd_,d3l7uc_,d3l7zd2,d3m5ka_,
+d3mg8r_,d3n6fb_,d3ne4a_,d3nfdf_,d3nvya2,d3nyxa1,d3o92b_,d3ohuf_,d3om5a_,d3ozqa1,
+d3pwsb2,d3q6ja3,d3q7jb1,d3qpkb3,d3qu1b_,d3r83a_,d3resb_,d3so1c_,d3tbla1,d3tcrb_,
+d3ubnc_,d3ujeb1,d3umld_,d3uwlb_,d3uyta_,d3vdba5,d3w7ob_,d3wefb_,d3wrta_,d3wyla_,
+d3ximd_,d3ziaf3,d4a1ua_,d4a75g1,d4au0a_,d4b1tb_,d4b7ba_,d4b7qd_,d4bpzb1,d4cqli_,
+d4d2oa_,d4d8gb1,d4db5a_,d4e4nb_,d4f5lb1,d4fkwa_,d4frtb_,d4h0ta2,d4hhyd1,d4hx6a1,
+d4i5bb1,d4ii4b1,d4isob_,d4iuaa1,d4ixzc_,d4j7xa_,d4jarc1,d4jcfa_,d4jhxc2,d4jyka2,
+d4jyox_,d4k1wc2,d4k64c1,d4kv5a_,d4ltco_,d4lzwb_,d4mq6b_,d4mswc_,d4mv6a2,d4mw5b1,
+d4napb_,d4nbjh_,d4nhzc2,d4otaa_,d4p3ya3,d4pd4f_,d4pitb1,d4pvma_,d4q1la_,d4q1sy_,
+d4q2va_,d4qseb_,d4qv0c_,d4qv4o_,d4qv5e_,d4qv8l_,d4qzwy_,d4r17d_,d4ryva_,d4tvab4,
+d4u39g1,d4unwa_,d4xheh1,d4xkdf_,d4yuya_,d4zgla_,d5acra_,d5cpya_,d5rlaa_,d7ccpa_
+\end{verbatim}
+
+\subsection{scop\_d62}
+
+\begin{verbatim}
+d1ao6b1,d1b0ea_,d1brwa1,d1bspa_,d1bzqd_,d1c1ba2,d1cklf1,d1d8la1,d1di0c_,d1dm5c_,
+d1e9ha_,d1egya_,d1f9qa_,d1fyfa1,d1g3it_,d1gg3b2,d1gqme_,d1hc7c3,d1hnvb_,d1i6hf_,
+d1ia2a_,d1isba2,d1iwao1,d1j6va_,d1jrqb2,d1jxja2,d1kkmj_,d1kpsc_,d1ndqa_,d1nzwb_,
+d1o1cv_,d1ogbb1,d1pf9i3,d1px3b4,d1qj3b_,d1qrqa_,d1rhgc_,d1roma_,d1s5ma_,d1srgb_,
+d1szsa1,d1tyzd_,d1tzyd_,d1v1tb1,d1v54u_,d1xyla_,d1zdja_,d1zqqa4,d1zr4e2,d220la_,
+d2c64a2,d2f4vp1,d2igad1,d2iw6b1,d2nvqi2,d2oqef1,d2puga2,d2rmaq_,d3ximd_,d4otaa_,
+d5rlaa_,d7ccpa_
+\end{verbatim}
+
+\subsection{cath\_d99}
+
+\begin{verbatim}
+1bxoA02,1byiA00,1hdoA00,1jfbA00,1k5nA01,1l3kA01,1lqtB02,1n3lA01,1n5uA03,1nkiA00,
+1nwwA00,1nz0D00,1psrA00,1r0mA01,1rl6A02,1rtqA00,1swyA00,1unqA00,1vimC00,1wmwB00,
+1xmkA00,2bw4A01,2dkjA02,2fvyA01,2nrlA00,2o9sA00,2ob3A00,2oizA01,2osxA01,2rbkA01,
+2vb1A00,2vxnA00,2w8tA01,2wn9D00,2wurA00,2ylbC00,2zcmA00,3a02A00,3dlcA00,3e2oA01,
+3go9A02,3goeA00,3h7iA02,3hj4A02,3iohA00,3kffA00,3ks3A00,3ku3A02,3ku3B00,3lqbA00,
+3nbcA00,3sovA02,3t5tB01,3u7qA02,3uljB00,3w5hA01,3wh2A00,3ziyA03,4bj0A00,4cayB00,
+4cbuA01,4cvrA00,4d3tA02,4d3tA03,4dd5A01,4ep4A00,4f1vA02,4fvyA01,4g1qA04,4k8gA02,
+4l8aA00,4mf5A02,4mtuA00,4oh7A02,4pf3A00,4r2xD00,4ua6A00,4unuA00,4xemA01,4yapA01,
+4z8jA00,4zflD00,5a71A00,5avdA02,5cgqB01,5cphA00,5dp2A01,5dzeA00,5hyvA02,5ibnA00,
+5jbxB01,5jryA01,5jryA02,5k8sB00,5kvsA02,5lvoA01,5lvoA02,5m17A00,5sy4A00
+\end{verbatim}
+
 \end{document}

### 2018-11-13 rupee-mgr/src/main/java/edu/umkc/rupee/mgr/Main.java

@@ -55,7 +55,6 @@ import edu.umkc.rupee.lib.Db;
 import edu.umkc.rupee.lib.DbId;
 import edu.umkc.rupee.lib.Hashes;
 import edu.umkc.rupee.lib.LCS;
-import edu.umkc.rupee.lib.Labels;
 import edu.umkc.rupee.lib.Similarity;
 import edu.umkc.rupee.lib.Uploading;
 import edu.umkc.rupee.scop.ScopHash;
@@ -716,10 +715,25 @@ public class Main {
 
     private static void option_d(CommandLine line) throws Exception {
 
+        
+        List<String> dbIds = Db.getBenchmark("cath_d99");
+        for (int i = 0; i < dbIds.size(); i++) {
+
+            if (i % 10 == 0) {
+                System.out.print("\n" + dbIds.get(i) + ",");
+            }
+            else {
+                System.out.print(dbIds.get(i) + ",");
+            }
+        }
+        System.out.println("");
+
+        /*
         List<Labels.Label> labels = Labels.getLabels("1nycA00", DbTypeCriteria.CATH);
         for (Labels.Label label : labels) {
             System.out.println(label.getResidueNumber() + "," + label.getLabel());
         }
+        */
 
         /*
         AlignResults.alignRupeeResults("scop_d360", "scop_v2_07", "tm_score", DbTypeCriteria.SCOP, 100);

### 2018-11-13 docs/rupee.tex
minor edits

@@
 Given a protein domain identifier, whole chain identifier or an uploaded PDB file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or among whole chains defined in the PDB.
-In contrast to currently available protein structure searches, RUPEE is able to search either of these databases using any identifier. 
+RUPEE is able to search either of these databases using any identifier. 
 For instance, you can search SCOPe using a CATH domain identifier.
@@
 RUPEE stands out as not just another protein structure search, of which there are many. 
-RUPEE is the first, to our knowledge, purely geometric protein structure search to achieve results as good as the current state of the art protein structure searches. 
-Additionally, it can be argued that the kinds of matches RUPEE returns have more added value than the current state of the art in that with equal scores it is able to return results not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as PDB-90.
+RUPEE is the first, to our knowledge, purely geometric protein structure search to achieve results as good as the best available protein structure searches. 
+Additionally, it can be argued that the kinds of matches that RUPEE does return have more added value than the current state of the art in that with equal scores it is able to return results not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as the PDB-90.
 In this regard, RUPEE makes a fundamental contribution to protein structure research that lends itself to being leveraged in existing systems. 
@@
 Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features. 
-Min-hashing and locality sensitive hashing (LSH), techniques drawn from big-data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and top-aligned.
+Min-hashing and locality sensitive hashing (LSH), techniques drawn from big data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and top-aligned.
 
@@
 
-As shown above, a purely geometric big data approach to protein structure search can compete with the current state of the art protein structure searches available.
+As shown above, a purely geometric big data approach to protein structure search can compete with the best available protein structure searches.
 Nonetheless, there remain avenues for further improvement and investigation.
@@
 For RUPEE top-aligned, we have shown that a purely geometric big data approach to protein structure search is able to produce results equal to or better than the current state of the art protein structure searches that variously depend on clustered sequences or protein structure classification hierarchies.
-Moreover, we have shown evidence that suggests the results from RUPEE top-aligned provide more added value by discovering high scoring protein structure matches not necessarily aligned with a particular protein structure classification hierarchy or hiding behind a cluster representative.
-The ability for RUPEE to quickly examine all structures among hundreds of thousands sets it apart as a tool that can be used for discovering previously undetected structural similarity relations between proteins rather than just aligning with an already known fold hierarchy.
+Moreover, we have shown evidence that suggests the results from RUPEE top-aligned provide more added value by discovering high scoring protein structure matches not necessarily aligned with a particular protein structure classification hierarchy or hiding behind cluster representatives.
+The ability for RUPEE to quickly examine all structures among hundreds of thousands sets it apart as a tool that can be used for discovering previously undetected structural similarities.
 

### 2018-11-13 docs/rupee.tex
spelling
abstract

@@
 We have developed RUPEE, a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
-Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for purely geometric big data approaches to protein structure searches, producing equal or better results than the current state of the art in protein structure search.
+
+Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for purely geometric big data approaches to protein structure searches.
+RUPEE in top-aligned mode produces equal or better results than the best available protein structure searches, and RUPEE in fast mode demonstrates the fastest response times coupled with high quality results.
 
@@
 In this regard, RUPEE makes a fundamental contribution to protein structure research that lends itself to being leveraged in existing systems. 
-It also provided a path for further research activity in the direction of big data represenations of protein structures.
+It also provided a path for further research activity in the direction of big data representations of protein structures.
 

### 2018-11-13 docs/rupee.tex
edits

@@
 The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
+
+The length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles. 
+In \cite{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
+With the additions discussed in the \emph{Operating modes} section below, we have found RUPEE is more tolerant of false positives and so accordingly we have cast a wider net by decreasing the shingle length to 3.
 

### 2018-11-15 docs/rupee.tex
image

@@
 
-\begin{figure*}[b]
+\begin{figure*}[t]
 \centering
@@
 Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
-
-The PhyreStorm server \cite{Mezulis2016} provides another notable protein structure search.
-Here too, it depends on PDB pre-calculated pairwise comparisons among PDB-40 cluster representatives \cite{Prlic2010}. 
-Notably, PhyreStorm returns good results within minutes based on an uploaded PDB file.
 
@@
 
-\begin{figure*}[tb]
-\begin{center}
-\includegraphics{regions}
-\end{center}
-\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
-\label{fig:regions}
-\end{figure*}
-
 This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
@@
 
-\begin{figure}[b]
-\begin{center}
-\includegraphics[width=3in,keepaspectratio]{1nycA00}
-\end{center}
-\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
-\label{fig:beta_turn}
-\end{figure}
-
 As an example of our linear encoding, we apply our method to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
@@
 There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \cite{Aungand2004,Zhang2010,Budowski2010}.
+
+\begin{figure*}[t]
+\begin{center}
+\includegraphics{regions}
+\end{center}
+\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
+\label{fig:regions}
+\end{figure*}
+
+\begin{figure}[b]
+\begin{center}
+\includegraphics[width=3in,keepaspectratio]{1nycA00}
+\end{center}
+\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
+\label{fig:beta_turn}
+\end{figure}
 
@@
 \end{align}
-
 This final step completes the transformation of an ordered list of descriptors to a multiset of integers that still retains some of the order information present in the original list.

### 2018-11-16 docs/plos_latex_template.tex
plos template

--- 2018-11-15 docs/rupee.tex
@@
-\documentclass[letter,center,fleqn]{NAR}
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
-\usepackage{textcomp}
-\usepackage{lmodern}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
+
+% -- my additions --
+
 \usepackage{gensymb}
-\usepackage{booktabs}
-\usepackage{placeins}
-
-% Enter dates of publication
-\copyrightyear{2018}
-\pubdate{?? ?????? ????}
-\pubyear{????}
-\jvolume{??}
-\jissue{??}
-
-%\articlesubtype{This is the article type (optional)}
-
-\hbadness=99999
-
-\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
+\usepackage{xspace}
 
@@
 \begin{document}
+\vspace*{0.2in}
 
-\title{RUPEE: A fast and accurate purely geometric protein structure search}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{RUPEE: A fast and accurate purely geometric protein structure search} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Ronald Ayoub\textsuperscript{1*},
+Yugyung Lee\textsuperscript{1}
+\\
+\bigskip
+\textbf{1} School of Computing and Engineering, University of Missouri at Kansas City, USA
+\\
+\bigskip
 
-\author{%
-Ronald Ayoub\,$^{1,}$%
-\footnote{To whom correspondence should be addressed.
-Email: ronaldayoub@mail.umkc.edu},
-Yugyung Lee\,$^{1}$}
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+%\Yinyang These authors contributed equally to this work.
 
-\address{%
-$^{1}$
-School of Computing and Engineering, 
-University of Missouri at Kansas City,
-5110 Rockhill Road,
-Kansas City, MO 64110, USA}
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
 
-% Affiliation must include:
-% Department name, institution name, full road and district address,
-% state, Zip or postal code, country
+% Current address notes
+%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+% \textcurrency b Insert second current address 
+% \textcurrency c Insert third current address
 
-\history{%
-Received ?????? ??, ????;
-Revised ?????? ??, ????;
-Accepted ?????? ??, ????}
+% Deceased author note
+%\dag Deceased
 
-\maketitle
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
 
-\begin{abstract}
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* ronaldayoub@mail.umkc.edu
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
 Given the close relationship between protein structure and function, protein structure searches have long played an established role in bioinformatics. 
@@
 
-The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. Code and data are available at \url{https://github.com/rayoub/rupee}.
-\end{abstract}
+The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. 
+Code and data are available at \url{https://github.com/rayoub/rupee}.
 
-\section{INTRODUCTION}
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
 
@@
 
-% **************************************************************
-% Keep this command to avoid text of first page running into the
-% first page footnotes
-\enlargethispage{-65.1pt}
-% **************************************************************
-
-\section{RELATED WORK}
+\section*{Related work}
 
@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics{combined_torsion}
-\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
-\label{fig:combined_torsion}
-\end{figure*}
-
 For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
@@
 
-\section{METHODS}
+\section*{Methods}
 
@@
 
-\subsection{Regions of Torsion Angles}
+\subsection*{Regions of Torsion Angles}
 
@@
 
+\begin{figure*}[!h]
+\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
+\label{fig:combined_torsion}
+\end{figure*}
+
 This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
@@
 
-\subsection{Linear Encoding of Protein Structure}
+\subsection*{Linear Encoding of Protein Structure}
 
@@
 
+\begin{figure*}[!h]
+\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
+\label{fig:regions}
+\end{figure*}
+
 As an example of our linear encoding, we apply our method to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
@@
 
-\subsection{Bag representation of protein structure}
+\begin{figure}[!h]
+\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
+\label{fig:beta_turn}
+\end{figure}
+
+\subsection*{Bag representation of protein structure}
 
@@
 There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \cite{Aungand2004,Zhang2010,Budowski2010}.
-
-\begin{figure*}[t]
-\begin{center}
-\includegraphics{regions}
-\end{center}
-\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
-\label{fig:regions}
-\end{figure*}
-
-\begin{figure}[b]
-\begin{center}
-\includegraphics[width=3in,keepaspectratio]{1nycA00}
-\end{center}
-\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
-\label{fig:beta_turn}
-\end{figure}
 
@@
 
-\subsection{Min-hashing and LSH}
+\subsection*{Min-hashing and LSH}
 
@@
 
-\subsection{Operating modes}
+\subsection*{Operating modes}
 
@@
 
-\section{RESULTS}
+\section*{Results}
 
@@
 On the other hand, the TM-score \cite{Zhang2004} takes all residues into account. 
-Among protein structure classification databases for which corresponding structure searches exist, SCOPe \citep{Fox2013} and CATH \citep{Orengo1997} are the most popular.
+Among protein structure classification databases for which corresponding structure searches exist, SCOPe \cite{Fox2013} and CATH \cite{Orengo1997} are the most popular.
 
@@
 
-\subsection{Scoring}
+\subsection*{Scoring}
 
@@
 
-\begin{figure*}[tb]
-\begin{center}
-\includegraphics{combined_scoring_ce}
-\end{center}
+\begin{figure*}[!h]
 \caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
@@
 In our evaluation, mTM faired better than SSM and CATHEDRAL. 
-mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-Score points of mTM at the 100$^{th}$ result, which is notable considering its speed.
+mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-Score points of mTM at the 100\textsuperscript{th} result, which is notable considering its speed.
 
@@
 
-\subsection{Precision}
+\subsection*{Precision}
 
@@
 
+\begin{figure*}[!h]
+\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
+\label{fig:combined_precision}
+\end{figure*}
+
 We should expect a structure search to have reasonable precision with respect to the hierarchy levels of the structure classification it is searching. 
@@
 Towards the extreme end of high precision, it would be sufficient for a search to return the best match and from there refer to the hierarchy for additional results.
-
-\begin{figure*}[tb]
-\begin{center}
-\includegraphics{combined_precision}
-\end{center}
-\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
-\label{fig:combined_precision}
-\end{figure*}
 
@@
 
-\subsection{Response Times}
+\subsection*{Response Times}
 
@@
 
-\begin{figure*}[tb]
-\begin{center}
-\includegraphics{combined_response}
-\end{center}
+\begin{figure*}[h!]
 \caption{Response times for RUPEE fast and RUPEE top-aligned. The response times for RUPEE top-aligned are dominated by pairwise structure alignments and do not depend on the sort order.}
@@
 
-\section{DISCUSSION}
+\section*{Discussion}
 
@@
 
-\section{CONCLUSION}
+\section*{Conclusion}
 
@@
 
-\subsubsection{Conflict of interest statement.} None declared.
-\newpage
+\nolinenumbers
 
-\nocite{Ayoub2017}
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
 \nocite{BioJava2012}
 \bibliography{rupee}
-\bibliographystyle{NAR-natbib}
 

### 2018-11-16 docs/plos_latex_template.tex
supporting information

@@
 
-All benchmark definitions can be found in the supplementary material.
+All benchmark definitions can be found in \nameref{S3_Benchmarks}.
 
@@
 
-A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in the supplementary material. 
+A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S1_Fig}. 
 The same relative relationships hold with only small variations.
@@
 
+\section*{Supporting information}
+
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Scoring from FATCAT pairwise alignments.}
+
+\paragraph*{S2 Methods.}
+\label{S2_Methods}
+{\bf Run factors for shingles instead of descriptors.}
+
+\paragraph*{S3 Benchmarks.}
+\label{S3_Benchmarks}
+{\bf Domains included in benchmarks used for evaluation.}
+
 \nolinenumbers

### 2018-11-16 docs/rupee.tex
bbl file

@@
 
-All benchmark definitions can be found in the supplementary material.
+All benchmark definitions can be found in \nameref{S3_Benchmarks}.
 
-\subsection{Scoring}
+\subsection*{Scoring}
 
@@
 
-\subsubsection{Conflict of interest statement.} None declared.
-\newpage
+\section*{Supporting information}
 
-\nocite{Ayoub2017}
-\nocite{BioJava2012}
-\bibliography{rupee}
-\bibliographystyle{NAR-natbib}
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Scoring from FATCAT pairwise alignments.}
+
+\paragraph*{S2 Methods.}
+\label{S2_Methods}
+{\bf Run factors for shingles instead of descriptors.}
+
+\paragraph*{S3 Benchmarks.}
+\label{S3_Benchmarks}
+{\bf Domains included in benchmarks used for evaluation.}
+
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+\begin{thebibliography}{10}
+
+\bibitem{Crick1970}
+Crick F.
+\newblock Central dogma of molecular biology.
+\newblock Nature. 1970;227(5258):561--563.
+
+\bibitem{Fox2013}
+Fox NK, Brenner SE, Chandonia JM.
+\newblock {SCOP}e: Structural Classification of Proteins - extended,
+  integrating {SCOP} and {ASTRAL} data and classification of new structures.
+\newblock Nucleic Acids Res. 2014;42(1):304--309.
+
+\bibitem{Orengo1997}
+Orengo C, Mitchie A, Jones S, Jones DT, Swindells M, Thornton JM.
+\newblock {CATH} - A hierarchic classification of protein domain structures.
+\newblock Structure. 1997;5(8):1093--1109.
+
+\bibitem{Cheng2014}
+Cheng H, Schaeffer RD, Liao Y, Kinch LN, Pei J, Shi S, et~al.
+\newblock {ECOD: An Evolutionary Classification of Protein Domains}.
+\newblock PLoS Computational Biology. 2014;10(12).
+
+\bibitem{Dong2018}
+Dong R, Pan S, Peng Z, Zhang Y, Yang J.
+\newblock {mTM-align: a server for fast protein structure database search and
+  multiple protein structure alignment}.
+\newblock Nucleic Acids Research. 2018;46(July):380--386.
+
+\bibitem{Krissinel2004}
+Krissinel E, Henrick K.
+\newblock {Secondary-structure matching (SSM), a new tool for fast protein
+  structure alignment in three dimensions}.
+\newblock Acta Crystallographica Section D: Biological Crystallography.
+  2004;60(12 I):2256--2268.
+
+\bibitem{Redfern2007}
+Redfern OC, Harrison A, Dallman T, Pearl FMG, Orengo CA.
+\newblock {CATHEDRAL}: A Fast and Effective Algorithm to Predict Folds and
+  Domain Boundaries from Multidomain Protein Structures.
+\newblock {PL}o{S} Comput Biol. 2007;3(11):e232.
+
+\bibitem{Shindyalov1998}
+Shindyalov IN, Bourne PE.
+\newblock Protein structure alignment by incremental combinatorial extension
+  ({CE}) of the optimal path.
+\newblock Protein Eng Des Sel. 1998;11(9):739--747.
+
+\bibitem{Ye2003}
+Yuzhen~Ye AG.
+\newblock Flexible structure alignment by chaining aligned fragment pairs
+  allowing twists.
+\newblock Bioinformatics. 2003;19(2):246--255.
+
+\bibitem{Gilbrat1996}
+Gilbrat JF, Madej T, Bryant SH.
+\newblock Surprising similarities in structure comparison.
+\newblock Curr Opin Struct Biol. 1996;6(3):377--385.
+
+\bibitem{Ye2004}
+Yuzhen~Ye AG.
+\newblock {FATCAT}: a web server for flexible structure comparison and
+  structure similarity searching.
+\newblock Nucleic Acids Res. 2004;32(2):582--585.
+
+\bibitem{Prlic2010}
+Prli{\'c} A, Bliven S, Rose PW, Bluhm WF, Bizon C, Godzik A, et~al.
+\newblock Pre-calculated protein structure alignments at the {RCSB} {PDB}
+  website.
+\newblock Bioinformatics. 2010;26(23):2983--2985.
+
+\bibitem{gkw1000}
+Rose PW, Prli{\'c} A, Altunkaya A, Bi C, Bradley AR, Christie CH, et~al.
+\newblock The {RCSB} protein data bank: integrative view of protein, gene and
+  {3D} structural information.
+\newblock Nucleic Acids Res. 2017;45(D1):D271--D281.
+
+\bibitem{Carpentier2005}
+Carpentier M, Brouillet S, Pothier J.
+\newblock {YAKUSA}: A fast structural database scanning method.
+\newblock Proteins. 2005;61(1):137--151.
+
+\bibitem{Daniluk2011}
+Daniluk P, Lesyng B.
+\newblock A novel method to compare protein structures using local descriptors.
+\newblock BMC Bioinformatics. 2011;12(1):344.
+
+\bibitem{Ritchie2012}
+Mavridis L, Ritchie DW.
+\newblock In: {3D-Blast}: {3D} protein structure alignment, comparison, and
+  classification using spherical polar fourier correlations. World Scientific;
+  2012. p. 281--292.
+
+\bibitem{Ramachandran1968}
+Ramachandran GN, Sasisekharan V.
+\newblock Conformation of polypeptides and proteins.
+\newblock Adv Protein Chem. 1968;23:283--438.
+
+\bibitem{Karplus2010}
+Hollingsworth SA, Karplus PA.
+\newblock A fresh look at the {R}amachandran plot and the occurrence of
+  standard structures in proteins.
+\newblock Biomol Concepts. 2010;1:271--283.
+
+\bibitem{Kabsch1983}
+Kabsch W, Sander C.
+\newblock Dictionary of protein secondary structure: Pattern recognition of
+  hydrogen-bonded and geometrical features.
+\newblock Biopolymers. 1983;22(12):2577--2637.
+
+\bibitem{Aungand2004}
+Aungand Z, Tan KL.
+\newblock Rapid 3D protein structure database searching using information
+  retrieval techniques.
+\newblock Bioinformatics. 2004;20(7):1045--1052.
+
+\bibitem{Zhang2010}
+Zhang L, Bailey J, Konagurthu AS, Ramamohanarao K.
+\newblock A fast indexing approach for protein structure comparison.
+\newblock {BMC} Bioinformatics. 2010;11(Suppl 1):S46.
+
+\bibitem{Budowski2010}
+Budowski-Tal I, Nov Y, Kolodny R.
+\newblock {FragBag}, an accurate representation of protein structure, retrieves
+  structural neighbors from the entire {PDB} quickly and accurately.
+\newblock Proceedings of the National Academy of Sciences.
+  2010;107(8):3481--3486.
+
+\bibitem{Broder1997a}
+Broder AZ.
+\newblock On the resemblance and containment of documents.
+\newblock In: Proc. Compression and Complexity of Sequences. Positano, Italy;
+  1997. p. 21--29.
+
+\bibitem{Ayoub2017}
+Ayoub R, Lee Y.
+\newblock RUPEE: Scalable protein structure search using run position encoded
+  residue descriptors.
+\newblock In: 2017 IEEE International Conference on Bioinformatics and
+  Biomedicine (BIBM); 2017. p. 74--78.
+
+\bibitem{Karp1987}
+Karp RM, Rabin MO.
+\newblock Efficient randomized pattern-matching algorithms.
+\newblock {IBM} Journal of Research and Development. 1987;31(2):249--260.
+
+\bibitem{Levan1971}
+Levandowsky M, Winter D.
+\newblock Distance between Sets.
+\newblock Nature. 1971;234(5323):34--35.
+
+\bibitem{Broder1997b}
+Broder AZ, Glassman SC, Manasse MS, Zweig G.
+\newblock Syntactic clustering of the Web.
+\newblock Computer Networks and ISDN Systems. 1997;29(8-13):1157--1166.
+
+\bibitem{Joshi2008}
+Joshi S, Contractor D, Ng K, Deshpande PM, Hampp T.
+\newblock Auto-grouping emails for faster e-discovery.
+\newblock In: Proceedings of Very Large Databases Endowment 2011. vol.~4; 2011.
+  p. 1284--1294.
+
+\bibitem{Broder1998}
+Broder AZ, Charikar M, Frieze AM, Mitzenmacher M.
+\newblock Min-wise independent permutations.
+\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
+  327--336.
+
+\bibitem{Indyk1998}
+Indyk P, Motwani R.
+\newblock Approximate nearest neighbors: towards removing the curse of
+  dimensionality.
+\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
+  604--613.
+
+\bibitem{Rajaraman2012}
+Rajaraman A, Ullman JD.
+\newblock 3.
+\newblock In: Mining of Massive Datasets. Cambridge University Press; 2012. p.
+  53--70.
+
+\bibitem{Zhang2004}
+Zhang Y, Skolnick J.
+\newblock Scoring function for automated assessment of protein structure
+  template quality.
+\newblock Proteins. 2004;57(4):702--710.
+
+\bibitem{Xu2010}
+J~Xu YZ.
+\newblock How significant is a protein structure similarity with {TM}-score =
+  0.5?
+\newblock Bioinformatics. 2010;26(7):889--895.
+
+\bibitem{Andreeva2007}
+Andreeva A, Prli{\'c} A, Hubbard TJP, Murzin AG.
+\newblock {SISYPHUS}: structural alignments for proteins with non-trivial
+  relationships.
+\newblock Nucleic Acids Res. 2007;35(1):253--259.
+
+\bibitem{BioJava2012}
+Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
+\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
+\newblock Bioinformatics. 2012;28(20):2693--2695.
+
+\end{thebibliography}
 

### 2018-11-16 docs/S1_benchmarks.tex
supporting info

--- 2018-11-13 docs/suppl.tex
@@
-\documentclass[letter,center,fleqn]{NAR}
+\documentclass[letter]{article}
 
-\usepackage{textcomp}
 \usepackage{lmodern}
-\usepackage{gensymb}
-\usepackage{booktabs}
 
@@
 
-\onecolumn
-\section{FIGURES}
-
-\begin{figure*}[h!]
-\begin{center}
-\includegraphics{combined_scoring_fatcat}
-\end{center}
-\caption{Scoring from FATCAT pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
-\label{fig:combined_scoring_fatcat}
-\end{figure*}
-
-\newpage
-
-\section{METHODS ADDENDUM}
-
-To see why RPE run factors are calculated at the descriptor level and factored in at the shingle level, consider shingling a list of RPE run factors themselves, which mirrors applying them at the descriptor level.
-\begin{align*}
-    &\text{The sequence of RPE factors} \\
-    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 1, 2, 3], [1, 2, 3, 2], [2, 3, 2, 1], [3, 2, 1, 0] \,\} \\
-    &\text{and with one less element} \\
-    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 1, 2, 2], [1, 2, 2, 1], [2, 2, 1, 0] \,\}
-\end{align*}
-Notice above, there is not a single match for this one-off difference in run length.
-Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
-\begin{align*}
-    &\text{The sequence of RPE factors} \\
-    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2], [3, 3, 3, 3] \,\} \\
-    &\text{and with one less element} \\
-    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
-    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2] \,\}
-\end{align*}
-In this latter case, a one-off difference in run length results in one less shingle match while still serving to increase the specificity of the shingles.
-
-\newpage
-\section{BENCHMARKS}
+\section{Benchmarks}
 

### 2018-11-16 docs/rupee.tex
supporting info

@@
 
-All benchmark definitions can be found in \nameref{S3_Benchmarks}.
+All benchmark definitions can be found in \nameref{S1_Benchmarks}.
 
@@
 
-A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S1_Fig}. 
+A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S2_Fig}. 
 The same relative relationships hold with only small variations.
@@
 
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
+\paragraph*{S1 Benchmarks.}
+\label{S1_Benchmarks}
+{\bf Domains included in benchmarks used for evaluation.}
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
 {\bf Scoring from FATCAT pairwise alignments.}
 
-\paragraph*{S2 Methods.}
-\label{S2_Methods}
+\paragraph*{S3 Methods Addendum.}
+\label{S3_Methods}
 {\bf Run factors for shingles instead of descriptors.}
-
-\paragraph*{S3 Benchmarks.}
-\label{S3_Benchmarks}
-{\bf Domains included in benchmarks used for evaluation.}
 

### 2019-01-06 docs/rupee_2.tex
baseline

--- 2018-11-16 docs/rupee.tex
@@
 
-The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. 
+The RUPEE protein structure search is available at \url{https://ayoubresearch.com}. 
 Code and data are available at \url{https://github.com/rayoub/rupee}.
@@
 %
-\begin{thebibliography}{10}
 
-\bibitem{Crick1970}
-Crick F.
-\newblock Central dogma of molecular biology.
-\newblock Nature. 1970;227(5258):561--563.
-
-\bibitem{Fox2013}
-Fox NK, Brenner SE, Chandonia JM.
-\newblock {SCOP}e: Structural Classification of Proteins - extended,
-  integrating {SCOP} and {ASTRAL} data and classification of new structures.
-\newblock Nucleic Acids Res. 2014;42(1):304--309.
-
-\bibitem{Orengo1997}
-Orengo C, Mitchie A, Jones S, Jones DT, Swindells M, Thornton JM.
-\newblock {CATH} - A hierarchic classification of protein domain structures.
-\newblock Structure. 1997;5(8):1093--1109.
-
-\bibitem{Cheng2014}
-Cheng H, Schaeffer RD, Liao Y, Kinch LN, Pei J, Shi S, et~al.
-\newblock {ECOD: An Evolutionary Classification of Protein Domains}.
-\newblock PLoS Computational Biology. 2014;10(12).
-
-\bibitem{Dong2018}
-Dong R, Pan S, Peng Z, Zhang Y, Yang J.
-\newblock {mTM-align: a server for fast protein structure database search and
-  multiple protein structure alignment}.
-\newblock Nucleic Acids Research. 2018;46(July):380--386.
-
-\bibitem{Krissinel2004}
-Krissinel E, Henrick K.
-\newblock {Secondary-structure matching (SSM), a new tool for fast protein
-  structure alignment in three dimensions}.
-\newblock Acta Crystallographica Section D: Biological Crystallography.
-  2004;60(12 I):2256--2268.
-
-\bibitem{Redfern2007}
-Redfern OC, Harrison A, Dallman T, Pearl FMG, Orengo CA.
-\newblock {CATHEDRAL}: A Fast and Effective Algorithm to Predict Folds and
-  Domain Boundaries from Multidomain Protein Structures.
-\newblock {PL}o{S} Comput Biol. 2007;3(11):e232.
-
-\bibitem{Shindyalov1998}
-Shindyalov IN, Bourne PE.
-\newblock Protein structure alignment by incremental combinatorial extension
-  ({CE}) of the optimal path.
-\newblock Protein Eng Des Sel. 1998;11(9):739--747.
-
-\bibitem{Ye2003}
-Yuzhen~Ye AG.
-\newblock Flexible structure alignment by chaining aligned fragment pairs
-  allowing twists.
-\newblock Bioinformatics. 2003;19(2):246--255.
-
-\bibitem{Gilbrat1996}
-Gilbrat JF, Madej T, Bryant SH.
-\newblock Surprising similarities in structure comparison.
-\newblock Curr Opin Struct Biol. 1996;6(3):377--385.
-
-\bibitem{Ye2004}
-Yuzhen~Ye AG.
-\newblock {FATCAT}: a web server for flexible structure comparison and
-  structure similarity searching.
-\newblock Nucleic Acids Res. 2004;32(2):582--585.
-
-\bibitem{Prlic2010}
-Prli{\'c} A, Bliven S, Rose PW, Bluhm WF, Bizon C, Godzik A, et~al.
-\newblock Pre-calculated protein structure alignments at the {RCSB} {PDB}
-  website.
-\newblock Bioinformatics. 2010;26(23):2983--2985.
-
-\bibitem{gkw1000}
-Rose PW, Prli{\'c} A, Altunkaya A, Bi C, Bradley AR, Christie CH, et~al.
-\newblock The {RCSB} protein data bank: integrative view of protein, gene and
-  {3D} structural information.
-\newblock Nucleic Acids Res. 2017;45(D1):D271--D281.
-
-\bibitem{Carpentier2005}
-Carpentier M, Brouillet S, Pothier J.
-\newblock {YAKUSA}: A fast structural database scanning method.
-\newblock Proteins. 2005;61(1):137--151.
-
-\bibitem{Daniluk2011}
-Daniluk P, Lesyng B.
-\newblock A novel method to compare protein structures using local descriptors.
-\newblock BMC Bioinformatics. 2011;12(1):344.
-
-\bibitem{Ritchie2012}
-Mavridis L, Ritchie DW.
-\newblock In: {3D-Blast}: {3D} protein structure alignment, comparison, and
-  classification using spherical polar fourier correlations. World Scientific;
-  2012. p. 281--292.
-
-\bibitem{Ramachandran1968}
-Ramachandran GN, Sasisekharan V.
-\newblock Conformation of polypeptides and proteins.
-\newblock Adv Protein Chem. 1968;23:283--438.
-
-\bibitem{Karplus2010}
-Hollingsworth SA, Karplus PA.
-\newblock A fresh look at the {R}amachandran plot and the occurrence of
-  standard structures in proteins.
-\newblock Biomol Concepts. 2010;1:271--283.
-
-\bibitem{Kabsch1983}
-Kabsch W, Sander C.
-\newblock Dictionary of protein secondary structure: Pattern recognition of
-  hydrogen-bonded and geometrical features.
-\newblock Biopolymers. 1983;22(12):2577--2637.
-
-\bibitem{Aungand2004}
-Aungand Z, Tan KL.
-\newblock Rapid 3D protein structure database searching using information
-  retrieval techniques.
-\newblock Bioinformatics. 2004;20(7):1045--1052.
-
-\bibitem{Zhang2010}
-Zhang L, Bailey J, Konagurthu AS, Ramamohanarao K.
-\newblock A fast indexing approach for protein structure comparison.
-\newblock {BMC} Bioinformatics. 2010;11(Suppl 1):S46.
-
-\bibitem{Budowski2010}
-Budowski-Tal I, Nov Y, Kolodny R.
-\newblock {FragBag}, an accurate representation of protein structure, retrieves
-  structural neighbors from the entire {PDB} quickly and accurately.
-\newblock Proceedings of the National Academy of Sciences.
-  2010;107(8):3481--3486.
-
-\bibitem{Broder1997a}
-Broder AZ.
-\newblock On the resemblance and containment of documents.
-\newblock In: Proc. Compression and Complexity of Sequences. Positano, Italy;
-  1997. p. 21--29.
-
-\bibitem{Ayoub2017}
-Ayoub R, Lee Y.
-\newblock RUPEE: Scalable protein structure search using run position encoded
-  residue descriptors.
-\newblock In: 2017 IEEE International Conference on Bioinformatics and
-  Biomedicine (BIBM); 2017. p. 74--78.
-
-\bibitem{Karp1987}
-Karp RM, Rabin MO.
-\newblock Efficient randomized pattern-matching algorithms.
-\newblock {IBM} Journal of Research and Development. 1987;31(2):249--260.
-
-\bibitem{Levan1971}
-Levandowsky M, Winter D.
-\newblock Distance between Sets.
-\newblock Nature. 1971;234(5323):34--35.
-
-\bibitem{Broder1997b}
-Broder AZ, Glassman SC, Manasse MS, Zweig G.
-\newblock Syntactic clustering of the Web.
-\newblock Computer Networks and ISDN Systems. 1997;29(8-13):1157--1166.
-
-\bibitem{Joshi2008}
-Joshi S, Contractor D, Ng K, Deshpande PM, Hampp T.
-\newblock Auto-grouping emails for faster e-discovery.
-\newblock In: Proceedings of Very Large Databases Endowment 2011. vol.~4; 2011.
-  p. 1284--1294.
-
-\bibitem{Broder1998}
-Broder AZ, Charikar M, Frieze AM, Mitzenmacher M.
-\newblock Min-wise independent permutations.
-\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
-  327--336.
-
-\bibitem{Indyk1998}
-Indyk P, Motwani R.
-\newblock Approximate nearest neighbors: towards removing the curse of
-  dimensionality.
-\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
-  604--613.
-
-\bibitem{Rajaraman2012}
-Rajaraman A, Ullman JD.
-\newblock 3.
-\newblock In: Mining of Massive Datasets. Cambridge University Press; 2012. p.
-  53--70.
-
-\bibitem{Zhang2004}
-Zhang Y, Skolnick J.
-\newblock Scoring function for automated assessment of protein structure
-  template quality.
-\newblock Proteins. 2004;57(4):702--710.
-
-\bibitem{Xu2010}
-J~Xu YZ.
-\newblock How significant is a protein structure similarity with {TM}-score =
-  0.5?
-\newblock Bioinformatics. 2010;26(7):889--895.
-
-\bibitem{Andreeva2007}
-Andreeva A, Prli{\'c} A, Hubbard TJP, Murzin AG.
-\newblock {SISYPHUS}: structural alignments for proteins with non-trivial
-  relationships.
-\newblock Nucleic Acids Res. 2007;35(1):253--259.
-
-\bibitem{BioJava2012}
-Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
-\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
-\newblock Bioinformatics. 2012;28(20):2693--2695.
-
-\end{thebibliography}
+\nocite{Ayoub2017}
+\nocite{BioJava2012}
+\bibliography{rupee_2}
 

### 2019-01-06 docs/rupee_2.tex
false positives

@@
 
-The length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles. 
-In \cite{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
-With the additions discussed in the \emph{Operating modes} section below, we have found RUPEE is more tolerant of false positives and so accordingly we have cast a wider net by decreasing the shingle length to 3.
-
 By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
@@
 
-Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \cite{Levan1971} for multisets,
+Now that we have a representation of a protein structure as a bag of integers, similarity for a candidate pair of structures $a$ and $b$ is defined as the Jaccard similarity \cite{Levan1971} for multisets,
 \begin{align}
@@
 where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively.
+
+In applying the Jaccard similarity to sets of shingles, the length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles.
+In \cite{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
+The additional requirements for structural similarity we introduce in the \emph{Operating modes} section below has the ultimate effect of reducing false positives, so this allowed us to decrease the shingle length to 3 to control better for false negatives.
 

### 2019-01-06 docs/rupee_2.tex
region plots

@@
 
-The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
-The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
-
-Polar plots for each group of DSSP assignment codes along with defined region and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
+The polar plot described above is used to define torsion angle regions for DSSP secondary structure assignments.
+We divide six of the eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} into three groups: helices (`G',`H',`I'), strands (`E'), and bends and coils (`S',`C').
+For each of the three groups, we plotted the torsion angles and identified regions into which they clustered as shown in \figurename~\ref{fig:regions}.
+The regions for helices are assigned descriptors 1 to 4, for strands 5 to 7, and for bends and coils 8 to 10. 
+The other two DSSP secondary structure assignments codes for turns (`T') and bridges~(`B'), are assigned descriptors 11 and 12, respectively.
 For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
-The only exception is found in the bends and coil plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.
+The only exception is found in the bends and coils plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.
 

### 2019-01-06 docs/rupee_2.tex
connect some more dots

@@
 
-As an example of our linear encoding, we apply our method to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
+We use the above numeric descriptors to create a linear encoding of protein structures. 
+For example, we apply our linear encoding to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
 The corresponding sequence of residue descriptors is shown below.

### 2019-01-09 docs/rupee_2.tex
run length

@@
 
-To address this lack of specificity, we introduce a heuristic we call \emph{run position encoding} (RPE). 
+To address this lack of specificity, we introduce a heuristic we call \emph{run position encoding} (RPE), where a run is a consecutive sequence of identical descriptors. 
 To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run $i$.
@@
 These concurrent tasks identify candidate matches based on a single band match and then validate the matches based on a comparison of min-hashes. 
+In this way, RUPEE quickly compares the query structure to every structure in the database.
 
-In fast mode, the top 8,000 matches are obtained along with the original gram sequences defined for the structures.
+In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained along with the original gram sequences defined for the structures.
 A further validation is done by performing a longest common subsequence (LCS) analysis of the matched gram sequences and adjusting the Jaccard similarity scores accordingly.

### 2019-01-10 docs/rupee_2.tex
lsh and min-hashing

@@
 
-Min-hashing is used to randomly select items from a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum item in each permuted list.
-If the same random permutation of items is performed on each set of items in a collection, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity \cite{Broder1998}.
+Min-hashing generally is used to create a fixed-length signature for a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum hash in each permuted list.
+If the same process is performed on a pair of sets, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity of the two sets \cite{Broder1998}.
 In order to approximate the Jaccard similarity for a given pair of sets, a sufficient number of min-hashes must be obtained.
 
-In our case, the items are bags of shingle hashes for protein structures from which we obtain 99 min-hashes as described in \cite{Rajaraman2012}. 
-Given the key result above, the Jaccard similarity can now be approximated by the proportion of matching min-hashes.
+In our case, the sets contain shingle hashes for a protein structure from which we obtain 99 min-hashes for each set as described in \cite{Rajaraman2012}. 
+At this stage, we have reduced our representation of protein structures from variable-sized sets of shingles to fixed-length signatures.
+Given the key result above, the Jaccard similarity for any pair of protein structures can now be approximated by the proportion of matching min-hashes.
 
-Next, we use the LSH banding technique as described in \cite{Rajaraman2012}.
-The key result of the banding technique is that if \emph{any} band positions are a match for a given pair of structures, the probability that a specific similarity threshold has been met can be calculated.
-We use 33 bands of 3-min-hashes where the probability of a Jaccard similarity of 60\% or greater is approximately 99\%. 
-Banding allows the problem of finding similar items to be parallelized across bands since all that is needed for a match is a single band match.
+We use the LSH banding technique as described in \cite{Rajaraman2012} to first identify candidate matches without having to compare min-hashes for every protein structure. 
+We divide the 99 min-hashes in the signatures into contiguous subsequences (i.e. bands) of 3 min-hashes each, giving a total of 33 bands. 
+For each band, the min-hashes it contains are combined into yet another hash. 
+The key result of the banding technique is that if \emph{any} band hashes are a match for a given pair of structures, we can calculate the probability that a specific Jaccard similarity threshold has been met.
+For 33 bands of 3 min-hashes, the probability of a band match occurring for a pair of structures having a Jaccard similarity of 60\% or greater is approximately 99\%. 
+Banding allows the problem of finding similar structures to be parallelized across bands since all that is needed for a candidate match is a single band match.
 
@@
 Each operating mode builds on the results provided by the min-hashing and LSH system described above. 
-When a structure search is executed in either mode, a number of concurrent tasks are executed corresponding to the number of bands used for LSH. 
-These concurrent tasks identify candidate matches based on a single band match and then validate the matches based on a comparison of min-hashes. 
-In this way, RUPEE quickly compares the query structure to every structure in the database.
+When a structure search is executed in either mode, a number of concurrent tasks are executed corresponding to the 33 bands used for LSH. 
+These concurrent tasks identify candidate matches based on a single band match; for each candidate match, we estimate the Jaccard similarity using the min-hashes. 
+In this way, RUPEE quickly compares the query structure to every structure in the database, which in the case of ECOD is greater than 600,000 protein domains.
 

### 2019-01-10 docs/rupee_2.tex
lcs explanation

@@
 
-In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained along with the original gram sequences defined for the structures.
-A further validation is done by performing a longest common subsequence (LCS) analysis of the matched gram sequences and adjusting the Jaccard similarity scores accordingly.
-This step accounts for possible gram matches among pairs of structures that are out of order since the min-hashing and LSH techniques themselves do not consider the order of the gram matches.
+In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained.
+For each match, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
+As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
+This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
 The final step of fast mode is to sort the matches based on the adjusted scores and return the results.

### 2019-01-10 docs/rupee_2.tex
ce alignments and filter sizes

@@
 
-In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained.
-For each match, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
+In fast mode, the top 8000 matches from the min-hashing and LSH initial filtering are obtained.
+For each match, we adjust the Jaccard similarity to account for matched shingles that are out of sequence order. 
+For this adjustment, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
 As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
 This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
-The final step of fast mode is to sort the matches based on the adjusted scores and return the results.
+The final step of fast mode is to sort the matches based on the adjusted Jaccard similarity scores and return the results.
 
-Top-aligned is an additional step following fast mode. 
-First, unoptimized CE alignments are performed on the top 2,000 matches obtained from fast mode. 
-Then optimized CE alignments are performed on the top 400 matches and these are finally returned sorted either by RMSD or TM-Score. 
-Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.
+Top-aligned is an additional step following fast mode that uses CE to identify the best pairwise alignments among the top 2000 alignments from fast mode.
+First, we perform unoptimized CE alignments on the top 2000 matches obtained from fast mode. 
+Then, we perform optimized CE alignments on the top 400 matches based on the unoptimized alignments and these results are finally returned sorted either by RMSD or TM-Score. 
+We limit the optimized CE alignments to the top 400 matches because for CE pairwise alignments, finding an optimized alignment through the use of dynamic programming is an additional time-intensive step.
+The details of the difference between unoptimized and optimized CE alignments can be found in \cite{Shindyalov1998}.
+
+Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2000 results enough good matches to compete with the best available structure searches.
+The filter sizes of 8000, 2000, and 400 for fast mode, unoptimized CE alignments, and optimized CE alignments, respectively, have been chosen based on quality of results and speed. 
+We have found that increasing the size of each of these filters results in only marginal improvements in the quality of results. 
+Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.
 
@@
 
-The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.
+The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2000 results provided by RUPEE fast mode.
 

### 2019-01-11 docs/rupee_2.tex
methods

@@
 Min-hashing generally is used to create a fixed-length signature for a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum hash in each permuted list.
-If the same process is performed on a pair of sets, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity of the two sets \cite{Broder1998}.
+If the same process is performed on a pair of sets, the key result is that the probability of matching min-hashes at the same position is equal to the Jaccard similarity of the two sets \cite{Broder1998}.
 In order to approximate the Jaccard similarity for a given pair of sets, a sufficient number of min-hashes must be obtained.
 
-In our case, the sets contain shingle hashes for a protein structure from which we obtain 99 min-hashes for each set as described in \cite{Rajaraman2012}. 
+In our case, the sets contain shingles for a protein structure from which we obtain 99 min-hashes for each set as described in \cite{Rajaraman2012}. 
 At this stage, we have reduced our representation of protein structures from variable-sized sets of shingles to fixed-length signatures.
@@
 
-Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2000 results enough good matches to compete with the best available structure searches.
 The filter sizes of 8000, 2000, and 400 for fast mode, unoptimized CE alignments, and optimized CE alignments, respectively, have been chosen based on quality of results and speed. 
@@
 Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.
+
+Top-aligned is a simple step following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2000 results enough good matches to compete with the best available structure searches.
 

### 2019-01-11 docs/rupee_2.tex
tm-score

@@
 Pairwise alignment involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric. 
-Most commonly, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
+Traditionally, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
+However, the RMSD score does not factor in the distance between unaligned residues nor does it consider the percentage of aligned residues, that is, alignment \emph{coverage}. 
+RMSD scores also have some dependence on the length of the aligned proteins. 
+On the other hand, the TM-score \cite{Zhang2004} takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
+For this reason, TM-score is frequently used in the assessment of protein structure alignments.
 
@@
 First, we perform unoptimized CE alignments on the top 2000 matches obtained from fast mode. 
-Then, we perform optimized CE alignments on the top 400 matches based on the unoptimized alignments and these results are finally returned sorted either by RMSD or TM-Score. 
+Then, we perform optimized CE alignments on the top 400 matches based on the unoptimized alignments and these results are finally returned sorted either by RMSD or TM-score. 
 We limit the optimized CE alignments to the top 400 matches because for CE pairwise alignments, finding an optimized alignment through the use of dynamic programming is an additional time-intensive step.
@@
 
-Protein structure searches can be evaluated using pairwise alignment scores or by comparison of results against the hierarchy of a protein structure classification database.
-The RMSD of aligned residues is widely used in evaluations but is not perfectly suited to full-length comparisons between structures since distances between unaligned residues are not factored into the score.
-On the other hand, the TM-score \cite{Zhang2004} takes all residues into account. 
+Protein structure searches can be evaluated using pairwise alignment scores (e.g.
+RMSD and TM-score as described above) or by comparison of results against the hierarchy of a protein structure classification database.
 Among protein structure classification databases for which corresponding structure searches exist, SCOPe \cite{Fox2013} and CATH \cite{Orengo1997} are the most popular.
@@
 \begin{figure*}[!h]
-\caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
+\caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-score, and RUPEE top-aligned sorted by RMSD}
 \label{fig:combined_scoring_ce}
@@
 
-RUPEE fast, top-aligned sorted by RMSD, and top-aligned sorted by TM-Score, perform better than SSM and CATHEDRAL.
+RUPEE fast, top-aligned sorted by RMSD, and top-aligned sorted by TM-score, perform better than SSM and CATHEDRAL.
 The scoring in the cath\_d99 benchmark comparisons are notably lower than for the other two benchmarks. 
@@
 In our evaluation, mTM faired better than SSM and CATHEDRAL. 
-mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-Score points of mTM at the 100\textsuperscript{th} result, which is notable considering its speed.
+mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-score points of mTM at the 100\textsuperscript{th} result, which is notable considering its speed.
 
-For TM-Score, RUPEE top-aligned and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
-For RMSD, RUPEE top-aligned does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
+For TM-score, RUPEE top-aligned and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
+For RMSD, RUPEE top-aligned does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-score. 
 If mTM sorted by RMSD we suspect the results again would be nearly identical.
@@
 \begin{figure*}[!h]
-\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
+\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-score, and RUPEE top-aligned sorted by RMSD}
 \label{fig:combined_precision}
@@
 
-Similar to the scoring evaluations above, RUPEE fast and top-aligned, sorted by both RMSD and TM-Score, show higher precision than SSM and CATHEDRAL with the exception of RUPEE top-aligned sorted by RMSD for ranks lower than 10 compared against SSM.
+Similar to the scoring evaluations above, RUPEE fast and top-aligned, sorted by both RMSD and TM-score, show higher precision than SSM and CATHEDRAL with the exception of RUPEE top-aligned sorted by RMSD for ranks lower than 10 compared against SSM.
 
 Again, mTM faired better than SSM and CATHEDRAL. 
-Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-Score. 
+Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-score. 
 In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be led to regard this as a negative result. 

### 2019-01-13 docs/rupee.tex
related work

@@
 Code and data are available at \url{https://github.com/rayoub/rupee}.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 

### 2019-01-13 docs/rupee_2.tex
related work

@@
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-
 \linenumbers
@@
 
-The typical use case of aligning one protein structure to another does not impose tight response time requirements. 
-For this reason, pairwise alignments can focus on accuracy. 
+Pairwise alignments often favor accuracy over speed because the typical use case of aligning one protein structure to another does not impose tight response time requirements. 
 On the other hand, a protein structure search can involve thousands of comparisons and accuracy is often balanced against speed. 
@@
 CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
+
+Besides CE and FATCAT, TM-align \cite{Zhang2005} and DALI \cite{Sander1995} are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
+TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
+DALI compares distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
 
@@
 For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
-Nonetheless, these searches are slow in comparison to mTM, SSM, and CATHEDRAL when pre-calculated results are not used. 
+Nonetheless, these searches are slow in comparison to the structure searches we compare to in this paper, mTM, SSM, and CATHEDRAL, when pre-calculated results are not used. 
 If given a known protein domain, VAST can return structural neighbors in seconds using pre-calculated results. 
@@
 Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
+
+DALI also provides a heuristic structure search \cite{Holm2010} of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
+In the case of searching, DALI first identifies matched PDB-90 representatives and then walks a pre-calculated graph of structural similarities to identify further matches in the PDB to gradually build up the set of structures similar to the query structure.
+DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI \cite{Dong2018}.
 
@@
 While the LCS step has been shown to be effective, it is notable for its simplicity. 
-A more complex step of validating the sequence of gram matches can take a form similar to the path extension algorithm used by CE. 
-In this case, sequences of matches would only be extended when the difference of interresidue distances between gram pairs already in the sequence and a candidate pair to be added to the sequence fall below some threshold.
+A more complex step of validating the sequence of shingle matches can take a form similar to the path extension algorithm used by CE. 
+In this case, sequences of matches would only be extended when the difference of interresidue distances between shingle pairs already in the sequence and a candidate pair to be added to the sequence fall below some threshold.
 
-On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the grams themselves could lead.
+On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the shingles themselves could lead.
 For instance, topological permutations such as circular permutations, segment-swapping and changing secondary structures within homologous proteins are not uncommon \cite{Andreeva2007}. 
-The initial RUPEE min-hashing and LSH algorithm provides candidate matches along with matched grams. 
+The initial RUPEE min-hashing and LSH algorithm provides candidate matches along with matched shingles. 
 With some thought, an algorithm similar to FATCAT can be developed allowing for permutations in addition to twists.

### 2019-01-14 docs/rupee_2.tex
results

@@
 TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
-DALI compares distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
+DALI compares intramolecular distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
 
@@
 
-For our results, we have created 3 benchmarks, scop\_d360, scop\_d62, and cath\_d99, for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
+For our results, we have derived 3 benchmarks, scop\_d360, scop\_d62, and cath\_d99, for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
+To avoid introducing our own bias, we were careful to derive each benchmark from an existing benchmark used in a previously published work or an existing list of protein domains provided by an independent third party.
 scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains in SCOPe 2.07 for which mTM returns 100 or more results.
@@
 In keeping with our description of RUPEE in \cite{Ayoub2017}, the cath\_d99 benchmark contains 99 superfamily representatives from the top 100 most diverse superfamilies defined in CATH v4.2 for which CATHEDRAL returns results in less than 12 hours.
+
+At each point in our comparison to mTM, SSM, and CATHEDRAL, where a decision had to be made that may favor one tool over another, we were careful to make sure RUPEE is not favored. 
+For instance, while filtering the benchmarks based on the number of results returned may eliminate some hard targets, we note that in all cases RUPEE returns more than 100 results.
 

### 2019-01-14 docs/rupee_2.tex
response times

@@
 
+Response times to a large degree are a measure of the amount of resources available to an application. 
+Response times for RUPEE were gathered from RUPEE running on a fairly old laptop with a 2nd generation Intel\textregistered{} Core\texttrademark{} i7-2720QM Quad-Core CPU and 8 GB of memory. 
+With more resources the response times of RUPEE can be further improved since pairwise alignments can be run in parallel. 
+For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
+
+Given that our response time comparisons are made against the respective tools running in different environments, we cannot derive solid conclusions about the efficiency of the methods themselves. 
+Nevertheless, these response times do fairly compare the user experience of the respective tools. 
+Moreover, in some cases the response times differ dramatically, by an order of magnitude in the case of RUPEE fast.
+
 \figurename~\ref{fig:combined_response} shows response times in seconds for the scop\_d62 and cath\_d99 benchmarks. 
@@
 The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2000 results provided by RUPEE fast mode.
-
-Response times to a large degree are a measure of the amount of resources available to an application. 
-In the case of RUPEE, our response times were gathered from RUPEE running on a fairly old laptop with a 2nd generation Intel\textregistered{} Core\texttrademark{} i7-2720QM Quad-Core CPU and 8 GB of memory.
-With more resources the response times of RUPEE can be further improved since pairwise alignments can be run in parallel. 
-For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
 

### 2019-01-28 docs/rupee_2.tex
standard
revisions

@@
 RUPEE has two modes of operation, fast and top-aligned. 
-Fast mode is significantly faster than all other protein structure searches discussed below but at the expensive of accuracy.
+Fast mode is significantly faster than all other protein structure searches discussed below but at the expense of accuracy.
 Despite this, we will show that the accuracy of RUPEE in fast mode is not far below that of the best available structure searches. 
@@
 RUPEE is the first, to our knowledge, purely geometric protein structure search to achieve results as good as the best available protein structure searches. 
-Additionally, it can be argued that the kinds of matches that RUPEE does return have more added value than the current state of the art in that with equal scores it is able to return results not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as the PDB-90.
-In this regard, RUPEE makes a fundamental contribution to protein structure research that lends itself to being leveraged in existing systems. 
-It also provided a path for further research activity in the direction of big data representations of protein structures.
+Being purely geometric, the kinds of matches that RUPEE returns are not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as the PDB-90.
+Moreover, without a dependence on pre-calculated results, it is easy to apply a number of filters to the protein structures RUPEE searches in order to better focus on structures of interest.
+As one example, domains not having the same fold classification as the query structure can be searched exclusively to investigate unexpected structural relationships across folds. 
+In this regard, RUPEE makes a fundamental contribution to protein structure research that also provides a path for further research in the direction of big data representations of protein structures.
 
@@
 
-\section*{Related work}
+\section*{Related Work}
 
@@
 DALI compares intramolecular distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
+
+Of the pairwise alignment tools, CE, FATCAT, TM-align and DALI, we have found TM-align is the fastest while also providing high-quality pairwise structure alignments. 
+It is for this reason that we use TM-align for RUPEE in top-aligned mode.
 
@@
 
-\subsection*{Regions of Torsion Angles}
+\subsection*{Regions of torsion angles}
 
@@
 
-\subsection*{Linear Encoding of Protein Structure}
+\subsection*{Linear encoding of protein structure}
 
@@
 
-\subsection*{Response Times}
+\subsection*{Response times}
 
 Response times to a large degree are a measure of the amount of resources available to an application. 
-Response times for RUPEE were gathered from RUPEE running on a fairly old laptop with a 2nd generation Intel\textregistered{} Core\texttrademark{} i7-2720QM Quad-Core CPU and 8 GB of memory. 
-With more resources the response times of RUPEE can be further improved since pairwise alignments can be run in parallel. 
+Response times for RUPEE were gathered from the RUPEE web site running on a single Amazon Web Services (AWS) c5.2xlarge elastic compute (EC2) unit. 
+With more resources, RUPEE response times can be further improved since pairwise alignments can be run in parallel. 
 For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
@@
 
-The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2000 results provided by RUPEE fast mode.
+The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 8000 results provided by RUPEE fast mode.
 
@@
 Additionally, for CATH you can filter results based on hierarchy level representatives. 
-Since RUPEE does not rely on sequence clusters, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.
+Since RUPEE does not rely on sequence clusters or pre-calculated results, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.
 
@@
 
-As can be observed from considering \figurename~\ref{fig:combined_scoring_ce} and \figurename~\ref{fig:combined_precision} together, there are good domain matches aligned with the SCOPe hierarchy that mTM is able to find that RUPEE does not.
-Conversely, there are good domain matches not aligned with the SCOPe hierarchy that RUPEE finds and mTM does not. 
-A comprehensive listing of these difference may find interesting similarities not previously known.
-
 \section*{Conclusion}
@@
 With the growth rate of solved structures deposited in the PDB, the need for a fast and scalable structure search is growing. 
-Using run position encoded shingles of residue descriptors combined with min-hashing and LSH, we have shown that RUPEE fast is able to provide good results in seconds running on an Quad-Core laptop.
+Using run position encoded shingles of residue descriptors combined with min-hashing and LSH, we have shown that RUPEE fast is able to provide good results in seconds running on a single AWS elastic compute unit.
 Currently, RUPEE fast is the fastest available protein structure search providing the demonstrated level of accuracy. 
-For RUPEE top-aligned, we have shown that a purely geometric big data approach to protein structure search is able to produce results equal to or better than the current state of the art protein structure searches that variously depend on clustered sequences or protein structure classification hierarchies.
-Moreover, we have shown evidence that suggests the results from RUPEE top-aligned provide more added value by discovering high scoring protein structure matches not necessarily aligned with a particular protein structure classification hierarchy or hiding behind cluster representatives.
+For RUPEE top-aligned, we have shown that a purely geometric big data approach to protein structure search is able to produce results equal to or better than the current state of the art protein structure searches that variously depend on clustered sequences or pre-calculated results.
 The ability for RUPEE to quickly examine all structures among hundreds of thousands sets it apart as a tool that can be used for discovering previously undetected structural similarities.
 
-\section*{Supporting information}
+\section*{Supporting Information}
 

### 2019-01-28 docs/rupee_2.tex
revisions

@@
 
-Top-aligned is an additional step following fast mode that uses CE to identify the best pairwise alignments among the top 2000 alignments from fast mode.
-First, we perform unoptimized CE alignments on the top 2000 matches obtained from fast mode. 
-Then, we perform optimized CE alignments on the top 400 matches based on the unoptimized alignments and these results are finally returned sorted either by RMSD or TM-score. 
-We limit the optimized CE alignments to the top 400 matches because for CE pairwise alignments, finding an optimized alignment through the use of dynamic programming is an additional time-intensive step.
-The details of the difference between unoptimized and optimized CE alignments can be found in \cite{Shindyalov1998}.
+Top-aligned is an additional step following fast mode that uses TM-align to identify the best pairwise alignments among the 8000 matches returned from fast mode.
+First, we execute TM-align on the 8000 matches obtained from fast mode using a reduced number of dynamic programming iterations in the TM-align algorithm. 
+We sort these initial alignments by the sort criterion entered by the user, either RMSD or TM-score, and obtain the top 400 matches.
+Finally, we execute TM-align using the default number of dynamic programming iterations on the top 400 matches and return the sorted results based on the sort criterion.
 
-The filter sizes of 8000, 2000, and 400 for fast mode, unoptimized CE alignments, and optimized CE alignments, respectively, have been chosen based on quality of results and speed. 
-We have found that increasing the size of each of these filters results in only marginal improvements in the quality of results. 
+The filter sizes of 8000 and 400 have been chosen based on quality of results and speed. 
+We have found that increasing the size of either of these filters results in only marginal improvements in the quality of results. 
 Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.
 
-Top-aligned is a simple step following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2000 results enough good matches to compete with the best available structure searches.
+Top-aligned is a simple step following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 8000 results enough good matches to compete with the best available structure searches.
 

### 2019-01-29 docs/rupee_2.tex
revisions

@@
 Being purely geometric, the kinds of matches that RUPEE returns are not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as the PDB-90.
-Moreover, without a dependence on pre-calculated results, it is easy to apply a number of filters to the protein structures RUPEE searches in order to better focus on structures of interest.
+Moreover, without a dependence on pre-calculated results, it is easy to apply filters at any level of granularity to the protein structures RUPEE searches in order to better focus on structures of interest.
 As one example, domains not having the same fold classification as the query structure can be searched exclusively to investigate unexpected structural relationships across folds. 
@@
 Second, mTM is updated to work with SCOPe 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
-On the other hand, CATHEDRAL presents no such challenges but still requires a separate benchmark since it is working with a distinct hierarchy, CATH v4.2.
+On the other hand, CATHEDRAL presents no such challenges but still requires a separate benchmark since it is working with a distinct set of domains, CATH v4.2.
 
@@
 
+\subsection*{Alignment normalization}
+
+The differences in approach among pairwise structure alignment tools can complicate efforts to achieve a fair comparison of protein structure searches that depend on them.
+Specifically, while RUPEE top-aligned and mTM both use TM-align for pairwise structure alignments, RUPEE normalizes by the average length of the aligned structures whereas mTM normalizes by the length of the query structure.
+Given how close the RUPEE top-aligned and mTM results shown below are with respect to scoring and precision, it is important to first examine the impact of each kind of normalization on the comparisons and also explain why we have chosen to normalize by the average length of the aligned structures for RUPEE top-aligned.
+
+By default, TM-align normalizes by the length of the query structure, that is, the first structure passed to it. 
+This normalization is asymmetric since higher TM-scores result when the query structure is smaller than the target structure and conversely, lower TM-scores result when the query structure is larger than the target structure.
+In extreme cases, high TM-scores can be achieved even when the target structure is 10 times larger than the query structure so long as the query structure can be aligned somewhere within the target structure.
+Since mTM uses the default asymmetric normalization provided by TM-align, this asymmetry becomes apparent in a detailed examination of mTM results.
+
+RUPEE top-aligned uses the TM-align option of normalizing by the average length. 
+This results in symmetric scoring where the order of the structures in the alignment has no effect on the TM-score.
+The first reason we use symmetric scoring in top-aligned is to synergistically match the min-hashing and LSH layer, which filters results based on the Jaccard similarity, a symmetric similarity measure.
+If, on the other hand, RUPEE top-aligned normalizes by the query structure, scoring and precision are negatively effected. 
+The second reason is that we plan to extend RUPEE to include both \emph{contained by} and \emph{contains} searches and do not want to favor one at the expense of the other by using asymmetric scoring.
+
+To examine how these difference effect RUPEE top-aligned and mTM results, we gathered the maximum percentage differences in length among the results for each structure search for domains in scop\_d360.
+We averaged these maximum percentage differences and found the average for RUPEE is 19.4\% and for mTM it is 90.8\%. 
+Whereas for RUPEE, these difference reflect larger and smaller query structures equally, for mTM, the larger difference always reflect a query structure smaller than the target structure. 
+Most of the extreme cases of mTM matching a small structure to a larger structure several times its size is matching small helical fragments to larger transmembrane proteins or other proteins with helical bundles.
+
+Given the difference in normalization between RUPEE and mTM, to be fair, we compare RUPEE scoring with mTM scoring below using TM-align normalized by the length of the query structure in addition to the average length of aligned structures.
+
 \subsection*{Scoring}
 
-\figurename~\ref{fig:combined_scoring_ce} shows average cumulative values for each ranked result averaged over all searches.
-Both RMSD and TM-score values are shown, provided as outputs from optimized CE pairwise alignments. 
+\figurename~\ref{fig:combined_scoring_tm_avg} shows average cumulative values for each ranked result averaged over all searches.
+Both RMSD and TM-score values are shown, provided as outputs from TM-align pairwise alignments normalized by the average length of aligned structures.
 A TM-score above 0.5 is a good predictor for whether or not two domains are in the same fold \cite{Xu2010}.
@@
 \begin{figure*}[!h]
-\caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-score, and RUPEE top-aligned sorted by RMSD}
-\label{fig:combined_scoring_ce}
+\caption{Scoring from TM-align pairwise alignments normalized by the average length of aligned structures for RUPEE fast, RUPEE top-aligned sorted by TM-score, and RUPEE top-aligned sorted by RMSD}
+\label{fig:combined_scoring_tm_avg}
 \end{figure*}
-
-A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S2_Fig}. 
-The same relative relationships hold with only small variations.
 
@@
 
-For TM-score, RUPEE top-aligned and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
+For both TM-score and RMSD, RUPEE top-aligned performed better than mTM. 
 For RMSD, RUPEE top-aligned does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-score. 
-If mTM sorted by RMSD we suspect the results again would be nearly identical.
+If mTM sorted by RMSD, their results likely will be improved. 
 Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
+
+\figurename~\ref{fig:combined_scoring_tm_q} again shows average cumulative values for each ranked result averaged over all searches but only for RUPEE and mTM. 
+The difference here is that instead of normalizing by the average length of the protein structures we show results for TM-align normalized by the length of the query structure. 
+This time, mTM  performs better than RUPEE top-aligned sorted by TM-score.
+
+\begin{figure*}[!h]
+\caption{Scoring from TM-align pairwise alignments normalized by the length of the query structure for RUPEE fast, RUPEE top-aligned sorted by TM-score, and RUPEE top-aligned sorted by RMSD}
+\label{fig:combined_scoring_tm_q}
+\end{figure*}
+
+Taken together, \figurename~\ref{fig:combined_scoring_tm_avg} and \figurename~\ref{fig:combined_scoring_tm_q} show that the results of RUPEE and mTM are roughly equal and where they do differ is a result of the differences in normalization.
+
+Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} \nameref{S3_Fig}, respectively. 
+These additional figures lend further support to what has already been show above.
 

### 2019-01-29 docs/rupee_2.tex
fix reference

@@
 
-Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} \nameref{S3_Fig}, respectively. 
+Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} and \nameref{S3_Fig}, respectively. 
 These additional figures lend further support to what has already been show above.
@@
 \label{S2_Fig}
+{\bf Scoring from CE pairwise alignments.}
+
+\paragraph*{S3 Fig.}
+\label{S3_Fig}
 {\bf Scoring from FATCAT pairwise alignments.}

### 2019-01-29 docs/rupee_2.tex
revisions

@@
 
-Similar to the scoring evaluations above, RUPEE fast and top-aligned, sorted by both RMSD and TM-score, show higher precision than SSM and CATHEDRAL with the exception of RUPEE top-aligned sorted by RMSD for ranks lower than 10 compared against SSM.
+RUPEE fast and top-aligned sorted by TM-score show higher precision than SSM and CATHEDRAL.
+mTM shows higher precision than RUPEE fast. 
+However, RUPEE top-aligned sorted by TM-score shows equal or higher precision than mTM up to the 50\textsuperscript{th} result and then drops below that of mTM. 
+The lower precision after the 50\textsuperscript{th} result can be attributed, in large part, to the differences in normalization. 
+A good example of this is for the search on domain d1j6va\_ from scop\_d360 having 148 residues.
+After the initial block of closely matched structures, mTM begins returning structures within the same fold with more than 200 residues like d1q2la2 and d1q2la3.
+On the other hand, RUPEE begins to look outside the fold to structures like d2fyxb2 and d2fyxa1 that provide better full-length alignments with respect to both the query and the target protein.
 
-Again, mTM faired better than SSM and CATHEDRAL. 
-Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-score. 
-In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be led to regard this as a negative result. 
-However, to the contrary, in the presence of \figurename~\ref{fig:combined_scoring_ce}, where it is shown that RUPEE and mTM have almost identical scoring, this result is remarkable. 
-This disparity suggest that RUPEE is better able to find significantly similar matches not necessarily aligned with the SCOPe hierarchy. 
-In fact, since the initial min-hashing and LSH technique used by RUPEE check for similarity to all available structures, no structure is able to hide behind a sequence based cluster representative. 
-So this result is in keeping with how RUPEE is intended to work and how it is described above.
+RUPEE top-aligned sorted by RMSD shows higher precision than for CATHEDRAL but lower precision than mTM and SSM. 
+Also, RUPEE top-aligned sorted by RMSD shows lower precision than both RUPEE fast and RUPEE top-aligned sorted by TM-score.
+The lower precision for RUPEE top-aligned sorted by RMSD is a direct consequence of RMSD not being suitable for full-length alignments as discussed above in \emph{Related work}.
+For this reason, it is advised to sort RUPEE top-aligned results by TM-score. 
+RUPEE top-align provides a sort by RMSD only for the sake of completeness.
 
@@
 In all cases, RUPEE fast is considerably faster than all other searches. 
-It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to CATHEDRAL and RUPEE top-aligned.
-Response times for SSM are not affected by residue counts at all and always returns results in less than 100 seconds but this is at the expense of performance as shown in \figurename~\ref{fig:combined_scoring_ce}.
+It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to RUPEE top-aligned, mTM and CATHEDRAL.
+Response times for SSM are not affected by residue counts at all and always returns results in less than 100 seconds but this is at the expense of performance as shown in \figurename~\ref{fig:combined_scoring_tm_avg}.
 
-In the left plot of \figurename~\ref{fig:combined_response}, it is shown that RUPEE top-aligned is faster than mTM for residue counts below 200, but then response times for RUPEE increase beyond that of mTM.
-Down the stretch, mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times. 
-The right plot of \figurename~\ref{fig:combined_response} shows RUPEE top-aligned is significantly faster than CATHEDRAL for all residue counts.
+The left plot of \figurename~\ref{fig:combined_response} shows that RUPEE top-aligned is faster than mTM for all residue counts. 
+Likewise, the right plot of \figurename~\ref{fig:combined_response} shows that RUPEE top-aligned is significantly faster than CATHEDRAL for all residue counts.
 
@@
 
-\paragraph*{S3 Methods Addendum.}
-\label{S3_Methods}
+\paragraph*{S4 Methods Addendum.}
+\label{S4_Methods}
 {\bf Run factors for shingles instead of descriptors.}

### 2019-01-29 docs/rupee_2.tex
revisions

@@
 These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.
-We have developed RUPEE, a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
+To address these limitations we have developed RUPEE, a fast and accurate purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
 
@@
 Given a protein domain identifier, whole chain identifier or an uploaded PDB file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or among whole chains defined in the PDB.
-RUPEE is able to search either of these databases using any identifier. 
+RUPEE is able to search these databases using any identifier. 
 For instance, you can search SCOPe using a CATH domain identifier.
@@
 This results in symmetric scoring where the order of the structures in the alignment has no effect on the TM-score.
-The first reason we use symmetric scoring in top-aligned is to synergistically match the min-hashing and LSH layer, which filters results based on the Jaccard similarity, a symmetric similarity measure.
+The first reason we use symmetric scoring in RUPEE top-aligned is to synergistically match the min-hashing and LSH layer, which filters results based on the Jaccard similarity, a symmetric similarity measure.
 If, on the other hand, RUPEE top-aligned normalizes by the query structure, scoring and precision are negatively effected. 
@@
 To examine how these difference effect RUPEE top-aligned and mTM results, we gathered the maximum percentage differences in length among the results for each structure search for domains in scop\_d360.
-We averaged these maximum percentage differences and found the average for RUPEE is 19.4\% and for mTM it is 90.8\%. 
+We averaged these maximum percentage differences and found the average for RUPEE is 19.4\% and for mTM is 90.8\%. 
 Whereas for RUPEE, these difference reflect larger and smaller query structures equally, for mTM, the larger difference always reflect a query structure smaller than the target structure. 
@@
 If mTM sorted by RMSD, their results likely will be improved. 
-Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
+Nevertheless, it is worth noting that the initial min-hashing and LSH technique used by RUPEE does not explicitly bias results towards one particular measure.
 
@@
 Again, with more resources, this number can be increased, but there still remains a need for some kind of cut-off. 
-Nonetheless, in most search tools, having to looking past the first few hundred results usually indicates an ineffective search strategy.
+Nonetheless, in most search tools, having to look past the first few hundred results usually indicates an ineffective search strategy.
 To this end, RUPEE provides filters that can be used for traversing structure space more efficiently. 
-For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query structure at a chosen hierarchy level classification. 
-Additionally, for CATH you can filter results based on hierarchy level representatives. 
+For SCOPe, CATH, and ECOD the user can instruct the search to only return domains that differ from the query structure at a chosen hierarchy level classification. 
+Additionally, for CATH the user can filter results based on hierarchy level representatives. 
 Since RUPEE does not rely on sequence clusters or pre-calculated results, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.

### 2019-01-29 docs/rupee_2.tex
bib

@@
 
-\section*{Related Work}
+\section*{Related work}
 
@@
 
-Taken together, \figurename~\ref{fig:combined_scoring_tm_avg} and \figurename~\ref{fig:combined_scoring_tm_q} show that the results of RUPEE and mTM are roughly equal and where they do differ is a result of the differences in normalization.
+Taken together, Figs~\ref{fig:combined_scoring_tm_avg}~and~\ref{fig:combined_scoring_tm_q} show that the results of RUPEE and mTM are roughly equal and where they do differ is a result of the differences in normalization.
 
@@
 
-\section*{Supporting Information}
+\section*{Supporting information}
 
@@
 % 
+\begin{thebibliography}{10}
 
-\nocite{Ayoub2017}
-\nocite{BioJava2012}
-\bibliography{rupee_2}
+\bibitem{Crick1970}
+Crick F.
+\newblock Central dogma of molecular biology.
+\newblock Nature. 1970;227(5258):561--563.
+
+\bibitem{Fox2013}
+Fox NK, Brenner SE, Chandonia JM.
+\newblock {SCOP}e: Structural Classification of Proteins - extended,
+  integrating {SCOP} and {ASTRAL} data and classification of new structures.
+\newblock Nucleic Acids Res. 2014;42(1):304--309.
+
+\bibitem{Orengo1997}
+Orengo C, Mitchie A, Jones S, Jones DT, Swindells M, Thornton JM.
+\newblock {CATH} - A hierarchic classification of protein domain structures.
+\newblock Structure. 1997;5(8):1093--1109.
+
+\bibitem{Cheng2014}
+Cheng H, Schaeffer RD, Liao Y, Kinch LN, Pei J, Shi S, et~al.
+\newblock {ECOD: An Evolutionary Classification of Protein Domains}.
+\newblock PLoS Computational Biology. 2014;10(12).
+
+\bibitem{Dong2018}
+Dong R, Pan S, Peng Z, Zhang Y, Yang J.
+\newblock {mTM-align: a server for fast protein structure database search and
+  multiple protein structure alignment}.
+\newblock Nucleic Acids Research. 2018;46(July):380--386.
+
+\bibitem{Krissinel2004}
+Krissinel E, Henrick K.
+\newblock {Secondary-structure matching (SSM), a new tool for fast protein
+  structure alignment in three dimensions}.
+\newblock Acta Crystallographica Section D: Biological Crystallography.
+  2004;60(12 I):2256--2268.
+
+\bibitem{Redfern2007}
+Redfern OC, Harrison A, Dallman T, Pearl FMG, Orengo CA.
+\newblock {CATHEDRAL}: A Fast and Effective Algorithm to Predict Folds and
+  Domain Boundaries from Multidomain Protein Structures.
+\newblock {PL}o{S} Comput Biol. 2007;3(11):e232.
+
+\bibitem{Zhang2004}
+Zhang Y, Skolnick J.
+\newblock Scoring function for automated assessment of protein structure
+  template quality.
+\newblock Proteins. 2004;57(4):702--710.
+
+\bibitem{Shindyalov1998}
+Shindyalov IN, Bourne PE.
+\newblock Protein structure alignment by incremental combinatorial extension
+  ({CE}) of the optimal path.
+\newblock Protein Eng Des Sel. 1998;11(9):739--747.
+
+\bibitem{Ye2003}
+Yuzhen~Ye AG.
+\newblock Flexible structure alignment by chaining aligned fragment pairs
+  allowing twists.
+\newblock Bioinformatics. 2003;19(2):246--255.
+
+\bibitem{Zhang2005}
+Zhang Y, Skolnick J.
+\newblock {TM-align: A protein structure alignment algorithm based on the
+  TM-score}.
+\newblock Nucleic Acids Research. 2005;33(7):2302--2309.
+
+\bibitem{Sander1995}
+Holm L, Sander C.
+\newblock Dali: a network tool for protein structure comparison.
+\newblock Trends in Biochemical Sciences. 1995;20(11):478 -- 480.
+
+\bibitem{Gilbrat1996}
+Gilbrat JF, Madej T, Bryant SH.
+\newblock Surprising similarities in structure comparison.
+\newblock Curr Opin Struct Biol. 1996;6(3):377--385.
+
+\bibitem{Ye2004}
+Yuzhen~Ye AG.
+\newblock {FATCAT}: a web server for flexible structure comparison and
+  structure similarity searching.
+\newblock Nucleic Acids Res. 2004;32(2):582--585.
+
+\bibitem{Prlic2010}
+Prli{\'c} A, Bliven S, Rose PW, Bluhm WF, Bizon C, Godzik A, et~al.
+\newblock Pre-calculated protein structure alignments at the {RCSB} {PDB}
+  website.
+\newblock Bioinformatics. 2010;26(23):2983--2985.
+
+\bibitem{Holm2010}
+Holm L, Rosenstr{\"{o}}m P.
+\newblock {Dali server: Conservation mapping in 3D}.
+\newblock Nucleic Acids Research. 2010;38(SUPPL. 2):1--5.
+
+\bibitem{gkw1000}
+Rose PW, Prli{\'c} A, Altunkaya A, Bi C, Bradley AR, Christie CH, et~al.
+\newblock The {RCSB} protein data bank: integrative view of protein, gene and
+  {3D} structural information.
+\newblock Nucleic Acids Res. 2017;45(D1):D271--D281.
+
+\bibitem{Carpentier2005}
+Carpentier M, Brouillet S, Pothier J.
+\newblock {YAKUSA}: A fast structural database scanning method.
+\newblock Proteins. 2005;61(1):137--151.
+
+\bibitem{Daniluk2011}
+Daniluk P, Lesyng B.
+\newblock A novel method to compare protein structures using local descriptors.
+\newblock BMC Bioinformatics. 2011;12(1):344.
+
+\bibitem{Ritchie2012}
+Mavridis L, Ritchie DW.
+\newblock In: {3D-Blast}: {3D} protein structure alignment, comparison, and
+  classification using spherical polar fourier correlations. World Scientific;
+  2012. p. 281--292.
+
+\bibitem{Ramachandran1968}
+Ramachandran GN, Sasisekharan V.
+\newblock Conformation of polypeptides and proteins.
+\newblock Adv Protein Chem. 1968;23:283--438.
+
+\bibitem{Karplus2010}
+Hollingsworth SA, Karplus PA.
+\newblock A fresh look at the {R}amachandran plot and the occurrence of
+  standard structures in proteins.
+\newblock Biomol Concepts. 2010;1:271--283.
+
+\bibitem{Kabsch1983}
+Kabsch W, Sander C.
+\newblock Dictionary of protein secondary structure: Pattern recognition of
+  hydrogen-bonded and geometrical features.
+\newblock Biopolymers. 1983;22(12):2577--2637.
+
+\bibitem{Aungand2004}
+Aungand Z, Tan KL.
+\newblock Rapid 3D protein structure database searching using information
+  retrieval techniques.
+\newblock Bioinformatics. 2004;20(7):1045--1052.
+
+\bibitem{Zhang2010}
+Zhang L, Bailey J, Konagurthu AS, Ramamohanarao K.
+\newblock A fast indexing approach for protein structure comparison.
+\newblock {BMC} Bioinformatics. 2010;11(Suppl 1):S46.
+
+\bibitem{Budowski2010}
+Budowski-Tal I, Nov Y, Kolodny R.
+\newblock {FragBag}, an accurate representation of protein structure, retrieves
+  structural neighbors from the entire {PDB} quickly and accurately.
+\newblock Proceedings of the National Academy of Sciences.
+  2010;107(8):3481--3486.
+
+\bibitem{Broder1997a}
+Broder AZ.
+\newblock On the resemblance and containment of documents.
+\newblock In: Proc. Compression and Complexity of Sequences. Positano, Italy;
+  1997. p. 21--29.
+
+\bibitem{Karp1987}
+Karp RM, Rabin MO.
+\newblock Efficient randomized pattern-matching algorithms.
+\newblock {IBM} Journal of Research and Development. 1987;31(2):249--260.
+
+\bibitem{Levan1971}
+Levandowsky M, Winter D.
+\newblock Distance between Sets.
+\newblock Nature. 1971;234(5323):34--35.
+
+\bibitem{Ayoub2017}
+Ayoub R, Lee Y.
+\newblock RUPEE: Scalable protein structure search using run position encoded
+  residue descriptors.
+\newblock In: 2017 IEEE International Conference on Bioinformatics and
+  Biomedicine (BIBM); 2017. p. 74--78.
+
+\bibitem{Broder1997b}
+Broder AZ, Glassman SC, Manasse MS, Zweig G.
+\newblock Syntactic clustering of the Web.
+\newblock Computer Networks and ISDN Systems. 1997;29(8-13):1157--1166.
+
+\bibitem{Joshi2008}
+Joshi S, Contractor D, Ng K, Deshpande PM, Hampp T.
+\newblock Auto-grouping emails for faster e-discovery.
+\newblock In: Proceedings of Very Large Databases Endowment 2011. vol.~4; 2011.
+  p. 1284--1294.
+
+\bibitem{Broder1998}
+Broder AZ, Charikar M, Frieze AM, Mitzenmacher M.
+\newblock Min-wise independent permutations.
+\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
+  327--336.
+
+\bibitem{Indyk1998}
+Indyk P, Motwani R.
+\newblock Approximate nearest neighbors: towards removing the curse of
+  dimensionality.
+\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
+  604--613.
+
+\bibitem{Rajaraman2012}
+Rajaraman A, Ullman JD.
+\newblock 3.
+\newblock In: Mining of Massive Datasets. Cambridge University Press; 2012. p.
+  53--70.
+
+\bibitem{Xu2010}
+J~Xu YZ.
+\newblock How significant is a protein structure similarity with {TM}-score =
+  0.5?
+\newblock Bioinformatics. 2010;26(7):889--895.
+
+\bibitem{Andreeva2007}
+Andreeva A, Prli{\'c} A, Hubbard TJP, Murzin AG.
+\newblock {SISYPHUS}: structural alignments for proteins with non-trivial
+  relationships.
+\newblock Nucleic Acids Res. 2007;35(1):253--259.
+
+\bibitem{BioJava2012}
+Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
+\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
+\newblock Bioinformatics. 2012;28(20):2693--2695.
+
+\end{thebibliography}
 

### 2019-01-30 docs/rebuttal.tex
rebuttal.tex

% LaTeX rebuttal letter example.
% 2018 fzenke.net
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}

% import Eq and Section references from the main manuscript where needed
% \usepackage{xr}
% \externaldocument{manuscript}

% package needed for optional arguments
\usepackage{xifthen}
% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }

\newenvironment{reply}
   {\medskip \noindent \begin{sf}\textbf{Reply}:\  }
   {\medskip \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\begin{document}

\section*{Response to the reviewers}

% Both Reviewers
We thank the reviewers for their critical assessment of our work.

% Reviewer 1
\reviewersection

\subsection*{Related work}

\begin{point}
The authors should also briefly introduce the TM-score as a metric, because the authors use this metric later.
\label{pt:rw1}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
The authors should also briefly discuss and cite other pairwise structure alignment tools like TM-align and DALI.
\label{pt:rw2}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
Did you consider DALI (http://ekhidna2.biocenter.helsinki.fi/dali/) when determining which methods you would include in your comparison?
\label{pt:rw3}
\end{point}

\begin{reply}
Our reply
\end{reply}

\subsection*{Methods}

\begin{point}
The Strand and Bend/Coil parts in Fig 2 are divided into three sections, but there are only two DSSP assignment codes of these two secondary structure. The author should give an explanation with more details.
\label{pt:m1}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
The length of a shingling in this work is 3, and the length in authors’ previous work is 4. How does the length impact on the search result?
\label{pt:m2}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
We think that the authors should give clear definitions of ‘a run’ and the length of ‘a run’.
\label{pt:m3}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
The authors choose 8000, 2000, 400 as cut-offs in search, we think that the authors should give an explanation about these cut-offs. Maybe it is better to decide the number of results based on TM-score or RMSD.
\label{pt:m4}
\end{point}

\begin{reply}
Our reply
\end{reply}

\subsection*{Results}

\begin{point}
The authors use CE to get TM-score and RMSD, but mTM-align use TM-align to get TM-score and RMSD. Maybe it is unfair to RUPEE.
\label{pt:r1}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
Scop\_d360, scop\_d62 and cath\_d99 just select domains that other methods can return more than 100 or 50 results. The sieving may eliminate some hard targets.
\label{pt:r2}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
How diverse were your domains in scop\_d360 and scop\_d62?
\label{pt:r3}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
We think that the authors should compare your methods in some free-modeling targets.
\label{pt:r4}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
It is unfair to compare response time with different methods based on different platforms.
\label{pt:r5}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
The authors should also consider regular database updates, optimally on a weekly basis following the PDB releases.
\label{pt:r6}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
In our experience, TM-align is faster than CE. If the authors use TM-align to get pairwise alignments in Top-Aligned model, maybe it would be time-saving.
\label{pt:r7}
\end{point}

\begin{reply}
Our reply
\end{reply}

\subsection*{Web site}

\begin{point}
We use structure IDs (e.g. PDB ID: 8TIMA or SCOPe ID: d8TIMA\_) to search on the webserver, and there are no records.
\label{pt:ws1}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
It would be nice to provide an input example.
\label{pt:ws2}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
We would consider it essential to be able to download the results of the database search in a machine-readable (e.g. CSV) format.
\label{pt:ws3}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
It would be nice to provide demonstrations about header in table.
\label{pt:ws4}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
Occasionally, the link of CE provides an error result.
\label{pt:ws5}
\end{point}

\begin{reply}
Our reply
\end{reply}

% Reviewer 2
\reviewersection

\begin{point}
The paper says that the LCS of matched gram sequences will be applied for the top 8000 candidates for validation, and adjust the Jaccard similarity scores accordingly. How exactly does the adjustment work?
\label{pt:r21}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
In top-aligned mode, RUPEE performs unoptimized CE for the top 2000 matches and optimized CE alignments for the top 400 matches. What's the difference between unoptimized CE and optimized CE, and how the authors decided on the numbers of matches from fast mode for further validation?
\label{pt:r22}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
It is unclear how much the MinHash and LSH helped with the speed. RUPEE retains 8000 matches after applying these techniques. What's the reduction rate here (8000 out of how many structures)?\label{pt:r23}
\end{point}

\begin{reply}
Our reply
\end{reply}

\begin{point}
The authors compared the score curves (Fig 4) and precision curves (Fig. 5), and claimed that RUPEE performed better than mTM (even though mTM achieved higher precision than RUPEE) in capturing structural similarities that don't align with the SCOP hierarchy. I feel this argument is a little stretchy, and perhaps the authors can use some examples to demonstrate this point.
\label{pt:r24}
\end{point}

\begin{reply}
Our reply
\end{reply}

% Use the short-hand macros for one-liners.
%\shortpoint{ Typo in line xy. }
%\shortreply{ Fixed.}

\end{document}

### 2019-01-30 docs/rebuttal.tex
revisions

@@
 \begin{reply}
-Our reply
+We have added the following text along with citations at lines 46-52.
+\begin{quote}
+However, the RMSD score does not factor in the distance between unaligned residues nor does it consider the percentage of aligned residues, that is, alignment \emph{coverage}. 
+RMSD scores also have some dependence on the length of the aligned proteins. 
+On the other hand, the TM-score takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
+For this reason, TM-score is frequently used in the assessment of protein structure alignments. 
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+We have added the following text along with citations at lines 63-72. The second paragraph is part of our reply to \ref{pt:r7} and is shown here to provide further context. 
+\begin{quote}
+Besides CE and FATCAT, TM-align and DALI are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
+TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
+DALI compares intramolecular distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
+
+Of the pairwise alignment tools, CE, FATCAT, TM-align and DALI, we have found TM-align is the fastest while also providing high-quality pairwise structure alignments. 
+It is for this reason that we use TM-align for RUPEE in top-aligned mode. 
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+We have added the following text along with citations at lines 92-98. The last lines provides our justification for not comparing to DALI.
+\begin{quote}
+DALI also provides a heuristic structure search of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
+In the case of searching, DALI first identifies matched PDB-90 representatives and then walks a pre-calculated graph of structural similarities to identify further matches in the PDB to gradually build up the set of structures similar to the query structure.
+DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI.
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+This is a misunderstanding. 
+We made a number of edits at lines 139-152 to clarify this point. 
+The clusters of points do not correspond to individual DSSP assignment codes. 
+Each plot represents a clustering of points that corresponds to a \emph{set} of DSSP assignment codes. 
+The set of DSSP assignment codes are chosen for each plot because they have similar distributions of points. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+We did address this in the original paper but we did so at the wrong location and it also lacked clarity. 
+The text at lines 169-173 was moved and replaced with the following text at a more appropriate location at lines 193-198. 
+\begin{quote}
+In applying the Jaccard similarity to sets of shingles, the length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles.
+In [Ayoub2017], we used 4 consecutive descriptors for our shingles. 
+The additional requirements for structural similarity we introduce in the \emph{Operating modes} section below has the ultimate effect of reducing false positives, so this allowed us to decrease the shingle length to 3 to control better for false negatives.
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+We added the following clause to the first sentence of the paragraph following line 182 to address this. 
+\begin{quote}
+, where a run is a consecutive sequence of identical descriptors
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+We agree that RUPEE may be improved by a detailed examination of the distribution of scores to find an ideal cut-off but we do not believe this detracts from what the paper achieves.
+This can be addressed in future work.
+However, we agree that some justification should be given as to how we chose the filter sizes.
+We have added the following text at lines 276-281.
+Please note that the filter sizes have changed due to changes resulting from addressing \ref{pt:r7}.
+\begin{quote}
+The filter sizes of 8000 and 400 have been chosen based on quality of results and speed. 
+We have found that increasing the size of either of these filters results in only marginal improvements in the quality of results. 
+Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+This was a bug that we have fixed.  
 \end{reply}
@@
 \begin{reply}
-Our reply
+We have added help text right below the `Structure Id' field. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+We have added an `Export to CSV' link to the top of the results grid. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+We have added question icons and tooltips to the one- and two-letter column names. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+This was a bug that we have fixed. 
 \end{reply}

### 2019-01-30 docs/rebuttal.tex
revisions

@@
 \begin{reply}
-We have added the following text along with citations at lines 46-52.
+We added the following text along with citations at lines 46-52.
 \begin{quote}
@@
 \begin{reply}
-We have added the following text along with citations at lines 63-72. The second paragraph is part of our reply to \ref{pt:r7} and is shown here to provide further context. 
+We added the following text along with citations at lines 63-72. The second paragraph is part of our reply to \ref{pt:r7} and is shown here to provide further context. 
 \begin{quote}
@@
 \begin{reply}
-We have added the following text along with citations at lines 92-98. The last lines provides our justification for not comparing to DALI.
+We added the following text along with citations at lines 92-98. The last lines provides our justification for not comparing to DALI.
 \begin{quote}
@@
 \begin{reply}
-We did address this in the original paper but we did so at the wrong location and it also lacked clarity. 
+We addressed this in the previous version of this paper but we did so at the wrong location and it also lacked clarity. 
 The text at lines 169-173 was moved and replaced with the following text at a more appropriate location at lines 193-198. 
@@
 \begin{reply}
-We agree that RUPEE may be improved by a detailed examination of the distribution of scores to find an ideal cut-off but we do not believe this detracts from what the paper achieves.
+We agree that RUPEE may be improved by a detailed examination of the distribution of scores to find an ideal cut-off but we do not believe this detracts from what the paper accomplishes.
 This can be addressed in future work.
 However, we agree that some justification should be given as to how we chose the filter sizes.
-We have added the following text at lines 276-281.
+We added the following text at lines 276-281.
 Please note that the filter sizes have changed due to changes resulting from addressing \ref{pt:r7}.
@@
 \begin{reply}
-Our reply
+We no longer use CE.
+We now use TM-align for pairwise alignments. 
+This is addressed in \ref{pt:r7}. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+We added the following text along with citations at lines 305-309. 
+\begin{quote}
+At each point in our comparison to mTM, SSM, and CATHEDRAL, where a decision had to be made that may favor one tool over another, we were careful to make sure RUPEE is not favored. 
+For instance, while filtering the benchmarks based on the number of results returned may eliminate some hard targets, we note that in all cases RUPEE returns more than 100 results. 
+\end{quote}
+Aside from this, we do not think calculating scoring averages with varying numbers of data present at different ranks would be fair. 
+It may be the case that those missing numbers would be lower than the average if present and so calculating in their absence would unjustly give a higher scoring average for searches with missing data.
+The same would hold true for comparing precision. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+Whereas there may be outstanding issues to address regarding coverage of the benchmarks, the number of free-modeling targets available from CASP 13 are far more limited than our benchmarks and any evaluations using such a small sample size could be misleading.
+We also note that since RUPEE is purely geometric its approach to free-modelling targets will not be any different than for normal targets.
 \end{reply}
@@
 \begin{reply}
-Our reply
+We do not disagree with this point with respect to comparing `methods.'
+However, we do believe the response times give a fair comparison with respect to the user experience. 
+We have removed the text at lines 474-480 and replaced it with the following text at lines 441-453 at the beginning of the \emph{Response times} subsection. 
+We feel the response time comparisons are important to show since they demonstrate one of the strongest features of RUPEE. 
+\begin{quote}
+Response times to a large degree are a measure of the amount of resources available to an application. 
+Response times for RUPEE were gathered from the RUPEE web site running on a single Amazon Web Services (AWS) c5.2xlarge elastic compute (EC2) unit. 
+With more resources, RUPEE response times can be further improved since pairwise alignments can be run in parallel. 
+For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
+
+Given that our response time comparisons are made against the respective tools running in different environments, we cannot derive solid conclusions about the efficiency of the methods themselves. 
+Nevertheless, these response times do fairly compare the user experience of the respective tools. 
+Moreover, in some cases the response times differ dramatically, by an order of magnitude in the case of RUPEE fast. 
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+We do plan on updating RUPEE with each major update of SCOPe, CATH and ECOD. 
+Aside from this, our resources are currently limited. 
+With increased interest in RUPEE, that may change. 
 \end{reply}
@@
 \begin{reply}
-We have added help text right below the `Structure Id' field. 
+We added help text right below the `Structure Id' field. 
 \end{reply}
@@
 \begin{reply}
-We have added an `Export to CSV' link to the top of the results grid. 
+We added an `Export to CSV' link to the top of the results grid. 
 \end{reply}
@@
 \begin{reply}
-We have added question icons and tooltips to the one- and two-letter column names. 
+We added question icons and tooltips to the one- and two-letter column names. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+We agree that this was not adequately explained. 
+We made a number of edits at lines 251-265 to clarify this point. 
+The edited paragraph is shown below. 
+\begin{quote}
+In fast mode, the top 8000 matches from the min-hashing and LSH initial filtering are obtained.
+For each match, we adjust the Jaccard similarity to account for matched shingles that are out of sequence order. 
+For this adjustment, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
+As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
+This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
+The final step of fast mode is to sort the matches based on the adjusted Jaccard similarity scores and return the results. 
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Our reply
+Due to our response to \ref{pt:r7}, this comment no longer applies since we are no longer using CE. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+This comment was an indicator of an overall lack of clarity in the \emph{Min-hashing and LSH} subsection. 
+For this reason, we made extensive edits to lines 213-238 to clarify how and why we use min-hashing and LSH. 
 \end{reply}

### 2019-01-31 docs/rebuttal.tex
revisions

@@
 We thank the reviewers for their critical assessment of our work. 
+We address their concerns below. 
+Where line numbers are given, they refer to line numbers in the diff.
 
@@
 \begin{reply}
-We added the following clause to the first sentence of the paragraph following line 182 to address this. 
+To address this, we added the following clause to the first sentence of the paragraph following line 182.
 \begin{quote}
@@
 \begin{reply}
-We added the following text along with citations at lines 305-309. 
+We added the following text along with citations at lines 306-310. 
 \begin{quote}
@@
 \begin{reply}
-Our reply
+We added the following sentence at line 300.
+\begin{quote}
+scoo\_d360 contains domains from 262 distinct folds.
+\end{quote}
+We added the following sentence at line 302. 
+\begin{quote}
+scop\_d62 contains domains from 53 distinct folds. 
+\end{quote}
+In addition, to further explain how we arrived at our benchmarks, we added the following sentence at lines 295-298.
+\begin{quote}
+To avoid introducing our own bias, we were careful to derive each benchmark from an existing benchmark used in a previously published work or an existing list of protein domains provided by an independent third party.
+\end{quote}
 \end{reply}
@@
 \begin{reply}
-Whereas there may be outstanding issues to address regarding coverage of the benchmarks, the number of free-modeling targets available from CASP 13 are far more limited than our benchmarks and any evaluations using such a small sample size could be misleading.
-We also note that since RUPEE is purely geometric its approach to free-modelling targets will not be any different than for normal targets.
+There are only 31 free-modeling targets available from CASP 13, which is half of our smallest benchmark scop\_d62. 
+Filtering for single segment domains, there are only 24 free-modeling targets available.
+Evaluations using such a small sample size may not be meaningful. 
+We also note that since RUPEE is purely geometric, its approach to free-modelling targets will not be any different than for normal targets.
 \end{reply}
@@
 However, we do believe the response times give a fair comparison with respect to the user experience. 
-We have removed the text at lines 474-480 and replaced it with the following text at lines 441-453 at the beginning of the \emph{Response times} subsection. 
+We have removed the text at lines 475-481 and replaced it with the following text at lines 442-454 at the beginning of the \emph{Response times} subsection. 
 We feel the response time comparisons are important to show since they demonstrate one of the strongest features of RUPEE. 
@@
 \begin{reply}
-Our reply
+This paper benefited significantly from this comment.
+We have adopted the use of TM-align for pairwise alignments with RUPEE top-aligned. 
+This change has resulted in changes to the paper in several locations. 
+We justify our use of TM-align with the new paragraph at lines 70-72 in \emph{Related work}.
+We discuss our use of TM-align with edits to the paragraph at lines 266-275 in \emph{Methods}.
+Additionally, there are edits scattered throughout the entire Results section. 
+Most significantly, we have added a new subsection \emph{Alignment normalization} as the first subsection of \emph{Results} in order to explain the effect of our choice of alignment normalization on the results.
 \end{reply}
@@
 For this reason, we made extensive edits to lines 213-238 to clarify how and why we use min-hashing and LSH. 
+To address the reduction rate, we added the following sentence at lines 248-250.
+\begin{quote}
+In this way, RUPEE quickly compares the query structure to every structure in the database, which in the case of ECOD is greater than 600,000 protein domains.
+\end{quote}
+How this reduction is accomplished is clarified by the edits made to the \emph{Min-hashing and LSH} subsection. 
 \end{reply}
@@
 \begin{reply}
-Our reply
+With changes made to address \ref{pt:r7}, precision for RUPEE top-aligned has improved significantly. 
+Nevertheless, this comment encouraged us to check our assumptions.
+While RUPEE filters for different hierarchy levels and hierarchy level representatives are useful for exploring unexpected structural relationships across folds, this does not necessarily extend to RUPEE without filters applied since there are usually enough similar structures within the fold that can be matched.
+We made a number of edits at lines 21-32 to walk back these assertions and instead focus on the benefit of applying filters.
+Additionally, in our larger rework of the \emph{Precision} section we have removed lines 426-434 and we also removed text appearing at lines 539-543 of the \emph{Conclusion}.
 \end{reply}

### 2019-01-31 docs/rebuttal.tex
add bib

@@
 \usepackage{fullpage}
+\usepackage{natbib}
 
@@
 \begin{reply}
-We added the following text along with citations at lines 46-52.
+We added the following text at lines 46-52.
 \begin{quote}
@@
 RMSD scores also have some dependence on the length of the aligned proteins. 
-On the other hand, the TM-score takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
+On the other hand, the TM-score \citep{Zhang2004} takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
 For this reason, TM-score is frequently used in the assessment of protein structure alignments. 
@@
 \begin{reply}
-We added the following text along with citations at lines 63-72. The second paragraph is part of our reply to \ref{pt:r7} and is shown here to provide further context. 
+We added the following text at lines 63-72. The second paragraph is part of our reply to \ref{pt:r7} and is shown here to provide further context. 
 \begin{quote}
-Besides CE and FATCAT, TM-align and DALI are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
+Besides CE and FATCAT, TM-align \citep{Zhang2005} and DALI \citep{Sander1995} are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
 TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
@@
 \begin{reply}
-We added the following text along with citations at lines 92-98. The last lines provides our justification for not comparing to DALI.
+We added the following text at lines 92-98. The last lines provides our justification for not comparing to DALI.
 \begin{quote}
-DALI also provides a heuristic structure search of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
+DALI also provides a heuristic structure search \citep{Holm2010} of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
 In the case of searching, DALI first identifies matched PDB-90 representatives and then walks a pre-calculated graph of structural similarities to identify further matches in the PDB to gradually build up the set of structures similar to the query structure.
-DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI.
+DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI \citep{Dong2018}.
 \end{quote}
@@
 In applying the Jaccard similarity to sets of shingles, the length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles.
-In [Ayoub2017], we used 4 consecutive descriptors for our shingles. 
+In \citep{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
 The additional requirements for structural similarity we introduce in the \emph{Operating modes} section below has the ultimate effect of reducing false positives, so this allowed us to decrease the shingle length to 3 to control better for false negatives.
@@
 \begin{reply}
-We added the following text along with citations at lines 306-310. 
+We added the following text at lines 306-310. 
 \begin{quote}
@@
 
+\bibliography{rebuttal}
+\bibliographystyle{natbib}
+
 \end{document}

### 2019-01-31 docs/rebuttal.tex
rebuttal revisions

@@
 This is a misunderstanding. 
-We made a number of edits at lines 139-152 to clarify this point. 
+In order to avoid any confusion, we made a number of edits at lines 139-152.
 The clusters of points do not correspond to individual DSSP assignment codes. 
@@
 \begin{reply}
-We no longer use CE.
-We now use TM-align for pairwise alignments. 
-This is addressed in \ref{pt:r7}. 
+We now use TM-align for pairwise structure alignments since it is faster than CE while still providing high-quality alignments. 
+The change from CE to TM-align is addressed in \ref{pt:r7}. 
 \end{reply}
@@
 \begin{reply}
-We added the following text at lines 306-310. 
-\begin{quote}
-At each point in our comparison to mTM, SSM, and CATHEDRAL, where a decision had to be made that may favor one tool over another, we were careful to make sure RUPEE is not favored. 
-For instance, while filtering the benchmarks based on the number of results returned may eliminate some hard targets, we note that in all cases RUPEE returns more than 100 results. 
-\end{quote}
-Aside from this, we do not think calculating scoring averages with varying numbers of data present at different ranks would be fair. 
+We do not think calculating scoring averages with varying numbers of data present at different ranks would be fair. 
 It may be the case that those missing numbers would be lower than the average if present and so calculating in their absence would unjustly give a higher scoring average for searches with missing data.
@@
 However, we do believe the response times give a fair comparison with respect to the user experience. 
-We have removed the text at lines 475-481 and replaced it with the following text at lines 442-454 at the beginning of the \emph{Response times} subsection. 
+We have removed the text at lines 470-476 and replaced it with the following text at lines 437-449 at the beginning of the \emph{Response times} subsection. 
 We feel the response time comparisons are important to show since they demonstrate one of the strongest features of RUPEE. 
@@
 \begin{reply}
-Due to our response to \ref{pt:r7}, this comment no longer applies since we are no longer using CE. 
+We now use TM-align for pairwise structure alignments since it is faster than CE while still providing high-quality alignments. 
+We run TM-align with a reduced number of dynamic programming iterations in place of unoptimized CE alignments and with the default number of iterations in place of optimized CE alignments. 
+The distinction is now better explained in the paper at lines 266-275.
+The change from CE to TM-align is addressed in \ref{pt:r7}. 
 \end{reply}
@@
 We made a number of edits at lines 21-32 to walk back these assertions and instead focus on the benefit of applying filters.
-Additionally, in our larger rework of the \emph{Precision} section we have removed lines 426-434 and we also removed text appearing at lines 539-543 of the \emph{Conclusion}.
+Additionally, in our larger rework of the \emph{Precision} section we have removed lines 421-429 and we also removed text appearing at lines 534-538 of the \emph{Conclusion}.
 \end{reply}

### 2019-01-31 docs/rupee_revision.tex
rename

--- 2019-01-29 docs/rupee_2.tex
@@
 scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains in SCOPe 2.07 for which mTM returns 100 or more results.
+scoo\_d360 contains domains from 262 distinct folds.
 Similarly, scop\_d62 is derived from the d500 benchmark filtered for domains defined in SCOP 1.73 for which SSM returns 50 or more results.  
+scop\_d62 contains domains from 53 distinct folds. 
 In keeping with our description of RUPEE in \cite{Ayoub2017}, the cath\_d99 benchmark contains 99 superfamily representatives from the top 100 most diverse superfamilies defined in CATH v4.2 for which CATHEDRAL returns results in less than 12 hours.
-
-At each point in our comparison to mTM, SSM, and CATHEDRAL, where a decision had to be made that may favor one tool over another, we were careful to make sure RUPEE is not favored. 
-For instance, while filtering the benchmarks based on the number of results returned may eliminate some hard targets, we note that in all cases RUPEE returns more than 100 results.
 

### 2019-01-31 docs/rebuttal.tex
revisions

@@
 The same would hold true for comparing precision. 
+RUPEE always returns a sufficient number of results for the original d500 benchmark defined in \citep{Dong2018}. 
+We point this out with the following text at lines 303-304.
+\begin{quote}
+For all domains contained in the d500 benchmark, RUPEE returns 100 or more results. 
+\end{quote}
 \end{reply}
@@
 However, we do believe the response times give a fair comparison with respect to the user experience. 
-We have removed the text at lines 470-476 and replaced it with the following text at lines 437-449 at the beginning of the \emph{Response times} subsection. 
+We have removed the text at lines 471-477 and replaced it with the following text at lines 438-450 at the beginning of the \emph{Response times} subsection. 
 We feel the response time comparisons are important to show since they demonstrate one of the strongest features of RUPEE. 
@@
 We made a number of edits at lines 21-32 to walk back these assertions and instead focus on the benefit of applying filters.
-Additionally, in our larger rework of the \emph{Precision} section we have removed lines 421-429 and we also removed text appearing at lines 534-538 of the \emph{Conclusion}.
+Additionally, in our larger rework of the \emph{Precision} section we have removed lines 422-430 and we also removed text appearing at lines 534-538 of the \emph{Conclusion}.
 \end{reply}

### 2019-03-02 docs/rupee_revision.tex
revisions

@@
 \bigskip
-\textbf{1} School of Computing and Engineering, University of Missouri at Kansas City, USA
+\textbf{1} School of Computing and Engineering, University of Missouri at Kansas City, Kansas City, USA
 \\
@@
 To address these limitations we have developed RUPEE, a fast and accurate purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
-
 Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for purely geometric big data approaches to protein structure searches.
 RUPEE in top-aligned mode produces equal or better results than the best available protein structure searches, and RUPEE in fast mode demonstrates the fastest response times coupled with high quality results.
-
 The RUPEE protein structure search is available at \url{https://ayoubresearch.com}. 
@@
 scop\_d62 contains domains from 53 distinct folds. 
+For all domains contained in the d500 benchmark, RUPEE returns 100 or more results. 
 In keeping with our description of RUPEE in \cite{Ayoub2017}, the cath\_d99 benchmark contains 99 superfamily representatives from the top 100 most diverse superfamilies defined in CATH v4.2 for which CATHEDRAL returns results in less than 12 hours.
@@
 
-Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} and \nameref{S3_Fig}, respectively. 
-These additional figures lend further support to what has already been show above.
+Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S1_Fig} and \nameref{S2_Fig}, respectively. 
+These additional figures lend further support to what has already been shown above.
 
@@
 
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Scoring from CE pairwise alignments.}
+
 \paragraph*{S2 Fig.}
 \label{S2_Fig}
-{\bf Scoring from CE pairwise alignments.}
-
-\paragraph*{S3 Fig.}
-\label{S3_Fig}
 {\bf Scoring from FATCAT pairwise alignments.}
 
-\paragraph*{S4 Methods Addendum.}
-\label{S4_Methods}
+\paragraph*{S1 Methods.}
+\label{S1_Methods}
 {\bf Run factors for shingles instead of descriptors.}
@@
 
-\bibitem{BioJava2012}
-Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
-\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
-\newblock Bioinformatics. 2012;28(20):2693--2695.
-
 \end{thebibliography}

### 2019-08-11 docs/rupee.tex
start template

--- 2018-11-16 docs/rupee.tex
@@
 {\Large
-\textbf\newline{RUPEE: A fast and accurate purely geometric protein structure search} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Protein structure search to assist protein structure prediction} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \section*{Abstract}
-Given the close relationship between protein structure and function, protein structure searches have long played an established role in bioinformatics. 
-Despite their maturity, existing protein structure searches either use simplifying assumptions or compromise between fast response times and quality of results. 
-These limitations can prevent the easy and efficient exploration of relationships between protein structures, which is the norm in other areas of inquiry.
-We have developed RUPEE, a fast, scalable, and purely geometric structure search combining techniques from information retrieval and big data with a novel approach to encoding sequences of torsion angles.
-
-Comparing our results to the output of mTM, SSM, and the CATHEDRAL structural scan, it is clear that RUPEE has set a new bar for purely geometric big data approaches to protein structure searches.
-RUPEE in top-aligned mode produces equal or better results than the best available protein structure searches, and RUPEE in fast mode demonstrates the fastest response times coupled with high quality results.
-
-The RUPEE protein structure search is available at \url{http://www.ayoubresearch.com}. 
-Code and data are available at \url{https://github.com/rayoub/rupee}.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
@@
 \section*{Introduction}
+Lorem ipsum dolor sit~\cite{Crick1970} amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{Crick1970} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
-Proteins represent the functional end-product within the central dogma of molecular biology \cite{Crick1970}.
-As such, understanding protein structure is a central goal within structural bioinformatics. 
-Protein structure determination, prediction, alignment, and search all serve to advance this understanding. 
-Below, we present our approach to a fast, scalable, and purely geometric protein structure search we refer to with the acronym of \emph{RUn Position Encoded Encodings} of residue descriptors (RUPEE).
+\begin{eqnarray}
+\label{eq:schemeP}
+	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
+\end{eqnarray}
 
-Given a protein domain identifier, whole chain identifier or an uploaded PDB file, RUPEE can search for matches among domains defined in SCOPe 2.07 \cite{Fox2013}, CATH v4.2 \cite{Orengo1997}, ECOD develop210 \cite{Cheng2014}, or among whole chains defined in the PDB.
-RUPEE is able to search either of these databases using any identifier. 
-For instance, you can search SCOPe using a CATH domain identifier.
+\section*{Materials and methods}
+\subsection*{Etiam eget sapien nibh}
 
-RUPEE has two modes of operation, fast and top-aligned. 
-Fast mode is significantly faster than all other protein structure searches discussed below but at the expensive of accuracy.
-Despite this, we will show that the accuracy of RUPEE in fast mode is not far below that of the best available structure searches. 
-On the other hand, the accuracy and response times of RUPEE in top-aligned mode are comparable to currently available protein structure searches that are commonly considered fast.
+% For figure citations, please use "Fig" instead of "Figure".
+Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
 
-RUPEE stands out as not just another protein structure search, of which there are many. 
-RUPEE is the first, to our knowledge, purely geometric protein structure search to achieve results as good as the best available protein structure searches. 
-Additionally, it can be argued that the kinds of matches that RUPEE does return have more added value than the current state of the art in that with equal scores it is able to return results not biased toward a structure classification hierarchy such as SCOPe or sequence clusters such as the PDB-90.
-In this regard, RUPEE makes a fundamental contribution to protein structure research that lends itself to being leveraged in existing systems. 
-It also provided a path for further research activity in the direction of big data representations of protein structures.
-
-Besides our approach to protein structure search, we introduce a polar plot for torsion angles that may have wider applicability in the study of protein structure. 
-Further, the \emph{run position encoding} heuristic introduced below may have wider applicability to algorithms for character sequences containing long runs of repeats.
-
-We first discuss some related work to provide a context for our approach followed by a description of our method. 
-We end with a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website.
-
-\section*{Related work}
-
-Pairwise alignment involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric. 
-Most commonly, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
-
-The typical use case of aligning one protein structure to another does not impose tight response time requirements. 
-For this reason, pairwise alignments can focus on accuracy. 
-On the other hand, a protein structure search can involve thousands of comparisons and accuracy is often balanced against speed. 
-In this case, pairwise alignment is still useful for evaluating the results of a search, and this is the approach we take.
-
-For pairwise alignment, Combinatorial Extensions (CE) \cite{Shindyalov1998} and FATCAT \cite{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
-CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
-
-Whereas pairwise structure alignments only depend on the sequence of \ca coordinates, protein structure searches often introduce a further dependence on the sequence order of amino acids.
-This approach often takes the form of clustering proteins based on sequences and pre-calculating results for pairwise alignments among cluster representatives. 
-Then, these pre-calculated results are used for filtering the number of structures used for comparisons against a query protein.
-The exact formula for combining the use of representatives and pre-calculated results varies from system to system.
-However, all systems using this approach share the same disadvantage, an indirect dependence on amino acid sequences. 
-In the absence of a reliance on sequence representatives and pre-calculated results, and without sacrificing accuracy, response times suffer greatly, often taking upwards of an hour for queries to complete.
-
-For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
-Nonetheless, these searches are slow in comparison to mTM, SSM, and CATHEDRAL when pre-calculated results are not used. 
-If given a known protein domain, VAST can return structural neighbors in seconds using pre-calculated results. 
-However, if uploading a PDB file where pre-calculated results are not used, response times for VAST can exceed 30 minutes. 
-Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
-
-Given the above, there remains a need for a purely geometric protein structure search.
-For the serendipitous exploration of relations between protein structures performed in the trenches, this search should be fast. 
-Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \cite{gkw1000}, this search should be scalable. 
-At a minimum, RUPEE takes a significant step in this direction as will be shown below.
-
-\section*{Methods}
-
-Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features. 
-Min-hashing and locality sensitive hashing (LSH), techniques drawn from big data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and top-aligned.
-
-Protein structure searches that use linear encodings are not unique \cite{Carpentier2005,Daniluk2011,Ritchie2012}.
-The novelty of our approach lies in its remarkable performance given its simplicity. 
-Additionally, elements of our approach can be isolated and found to be useful in their own right.
-
-\subsection*{Regions of Torsion Angles}
-
-Our first step towards a linear encoding of protein structure is to identify separable regions of permissible torsion angles,
-but first we introduce a new plot of torsion angles better suited to this effort.
-
-Despite their utility and familiarity, Ramachandran plots \cite{Ramachandran1968} represent angular data using a square plot better suited for scalar data.
-This leads to the unwieldy arrangement where the top part of the plot is continuous with the bottom and the left is continuous with the right.
-
-To identify regions of torsion angles, we randomly sampled 10,000 residues from high-resolution CATH s35 representatives to account for precision and redundancy, respectively. 
-A Ramachandran plot of the sampled torsions angles is shown in the left plot of \figurename~\ref{fig:combined_torsion}. 
-As can be seen, a single cluster of residues, consisting primarily of $\beta$-strands, appears at all 4 corners of the Ramachandran plot.
-
-\begin{figure*}[!h]
-\caption{Ramachandran plot (right) and polar plot (left) of randomly sampled torsion angles}
-\label{fig:combined_torsion}
-\end{figure*}
-
-This continuity problem was partially addressed in \cite{Karplus2010} using \emph{wrapped} and \emph{mirrored} plots. 
-Both wrapped and mirrored plots take advantage of the sparsely populated areas of the Ramachandran plot at $\phi = 0\degree$ and $\psi = -120\degree$.
-However, with larger samples of torsion angles, the area at $\psi = -120\degree$ becomes less sparse. 
-The use of a polar plot resolves this elegantly by only requiring one break in continuity at $\phi = 0\degree$.
-
-In the right plot of \figurename~\ref{fig:combined_torsion}, we show the same torsion angles appearing in the Ramachandran plot using a polar plot. 
-In this plot, $\phi$ corresponds to the radius $r$ and $\psi$ corresponds to the angle $\theta$ in traditional polar plots. 
-Notice the residues appearing at the 4 corners of the Ramachandran plot now appear in one continuous region of the polar plot centered at $\phi = \pm180\degree$ and $\psi = \pm180\degree$.
-
-\subsection*{Linear Encoding of Protein Structure}
-
-The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
-The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.
-
-Polar plots for each group of DSSP assignment codes along with defined region and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively.
-For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
-The only exception is found in the bends and coil plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.
-
-\begin{figure*}[!h]
-\caption{Polar plots of randomly sampled torsion angles with designated descriptors for region and DSSP code combinations}
-\label{fig:regions}
-\end{figure*}
-
-As an example of our linear encoding, we apply our method to the $\beta$-turn-$\beta$ motif shown in \figurename~\ref{fig:beta_turn}.
-The corresponding sequence of residue descriptors is shown below.
-\begin{gather}\label{E:descrseq} 
-    [\, 5, 5, 5, 5, 5, 5, 7, 5, 11, 11, 5, 5, 5, 5, 5, 5 \,]
-\end{gather}
-
+% Place figure captions after the first paragraph in which they are cited.
 \begin{figure}[!h]
-\caption{$\beta$-turn-$\beta$ motif from CATH domain 1nycA00}
-\label{fig:beta_turn}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig1}
 \end{figure}
 
-\subsection*{Bag representation of protein structure}
+% Results and Discussion can be combined.
+\section*{Results}
+Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
 
-Once a linear encoding for a protein structure is obtained, it needs to be further transformed into a representation suitable for fast and scalable similarity comparisons to other structures.
-The processing of text documents within Information Retrieval~(IR) has long been used to satisfy these requirements using bag representations.
-There are two distinct categories of representations for documents, syntactic and semantic, and much of the research applying IR to protein structure search has focused on the latter \cite{Aungand2004,Zhang2010,Budowski2010}.
+% Place tables after the first paragraph in which they are cited.
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
+$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
+$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+\end{tabular}
+\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\end{flushleft}
+\label{table1}
+\end{adjustwidth}
+\end{table}
 
-We have adapted the syntactic approach to document similarity, often referred to as shingling \cite{Broder1997a}, to our linear encoding of protein structure. 
-We transform a linear sequence of descriptors into a multiset of shingles consisting of 3 consecutive descriptors.
-The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
+%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
+\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
+\subsubsection*{3rd level heading} 
+Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+Sed non aliquet felis.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Mauris commodo justo ac dui pretium imperdiet.
+Sed suscipit iaculis mi at feugiat.
 
-The length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles. 
-In \cite{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
-With the additions discussed in the \emph{Operating modes} section below, we have found RUPEE is more tolerant of false positives and so accordingly we have cast a wider net by decreasing the shingle length to 3.
+\begin{enumerate}
+	\item{react}
+	\item{diffuse free particles}
+	\item{increment time by dt and go to 1}
+\end{enumerate}
 
-By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
-As an example, the sequence in (\ref{E:descrseq}) is transformed into the following bag of shingles. 
-\begin{align}\label{E:shinglebag}
-    \begin{split}
-        \{\,&[5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 7] \\
-            & [5, 7, 5], [7, 5, 11], [5, 11, 11], [11, 11, 5], [11, 5, 5] \\
-            & [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5] \,\}
-    \end{split}
-\end{align}
+\subsection*{Sed ac quam id nisi malesuada congue}
 
-Next, each shingle $s$ is hashed to an integer as shown in~(\ref{E:hashdef}). 
-The hash function used is a simplification of the hash function used in the Rabin-Karp algorithm \cite{Karp1987}.
-The prime number $13$ is used as the base since it is large enough to spread the descriptor values out in hash space without collisions. 
-\begin{gather}\label{E:hashdef}
-    s_{hash} = s_1 \times 13^2 + s_2 \times 13 + s_3
-\end{gather}
-Subsequently, the multiset in (\ref{E:shinglebag}) becomes the following bag of integers.
-\begin{align}\label{E:hashbag}
-    \begin{split}
-    \{\,&915, 915, 915, 915, 917, 941, 1259 \\
-        &999, 2007, 1929, 915, 915, 915, 915 \,\}
-    \end{split}
-\end{align}
-This final step completes the transformation of an ordered list of descriptors to a multiset of integers that still retains some of the order information present in the original list.
+Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
 
-Notice in (\ref{E:hashbag}) the value 915, corresponding to the shingle $[ 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
-Since most proteins are dominated by regular secondary structure, the abundance of shingles for $\beta$-strands as well as the three types of helices, end up dominating comparisons. 
-Moreover, since shingles are limited in length, this situation allows for structures with many short $\beta$-strands to match structures with fewer long $\beta$-strands.
-The same situation applies to helices.
-
-To address this lack of specificity, we introduce a heuristic we call \emph{run position encoding} (RPE). 
-To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run $i$.
-\begin{gather}
-    runfactor(i) = 
-    \begin{cases}
-        i               &\text{if $i < \lfloor l/2 \rfloor$}\\
-        l - i - 1       &\text{otherwise} 
-    \end{cases}
-\end{gather}
-where $i$ is zero-based and $l$ is the length of the run. 
-Multiplying by $10^5$ places the run factor as the left-most digit in the hash to avoid interference with the digits provided by the hash in (\ref{E:hashdef}).
-This placement is also convenient for visual inspection, since the run factor is isolated as the left-most digit.
-
-The run factors for the sequence in (\ref{E:descrseq}) are
-\begin{align}
-    [\, 0, 1, 2, 2, 1, 0, 0, 0, 0, 0, 0, 1, 2, 2, 1, 0 \,].
-\end{align}
-Applied to the bag of integers in (\ref{E:hashbag}) gives
-\begin{align}\label{E:rpebag}
-    \begin{split}
-    \{\,&00915, 10915, 20915, 20915, 10917, 00941, 01259 \\
-        &00999, 02007, 01929, 00915, 10915, 20915, 20915 \,\}
-    \end{split}
-\end{align}
-where the leading zero run factors are shown for clarity.
-
-This pyramidal approach preserves matches at the boundaries between secondary structure runs and loops that would not otherwise be preserved in the presence of differences in run lengths of one or more.
-
-Now that we have a representation of a protein structure as a bag of integers, similarity between any two structures $a$ and $b$ is defined as the Jaccard similarity \cite{Levan1971} for multisets,
-\begin{align}
-    J(a,b) = \frac{\sum_i min(a_i, b_i)}{\sum_i max(a_i,b_i)}\text{,}
-\end{align}
-where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively.
-
-\subsection*{Min-hashing and LSH}
-
-In IR, the bag of shingles representation of documents is used in the near dupe clustering of documents \cite{Broder1997b}.
-One application of near dupe clustering is in the review stage of Electronic-Discovery \cite{Joshi2008}, which is the most expensive stage in a discovery process. 
-Often millions of documents must be examined by a staff of attorneys to make a reasonable effort at providing all documents relevant to the discovery request. 
-Grouping documents into near dupe clusters and assigning all documents within a cluster to a single reviewer reduces duplication of effort.
-
-In the case of near dupe clustering, each document must be compared to every other document in the collection, taking quadratic time.
-For this task, min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} can be combined to reduce this to subquadratic time. 
-Although we do not near dupe cluster domains, we can still leverage the techniques of min-hashing and LSH to speed up protein structure search by a large constant factor.
-
-Min-hashing is used to randomly select items from a set of items by repeatedly randomly hashing the items, sorting the hashes into a list, and then selecting the minimum item in each permuted list.
-If the same random permutation of items is performed on each set of items in a collection, the key result is that the probability of matching min-hashes is equal to the Jaccard similarity \cite{Broder1998}.
-In order to approximate the Jaccard similarity for a given pair of sets, a sufficient number of min-hashes must be obtained.
-
-In our case, the items are bags of shingle hashes for protein structures from which we obtain 99 min-hashes as described in \cite{Rajaraman2012}. 
-Given the key result above, the Jaccard similarity can now be approximated by the proportion of matching min-hashes.
-
-Next, we use the LSH banding technique as described in \cite{Rajaraman2012}.
-The key result of the banding technique is that if \emph{any} band positions are a match for a given pair of structures, the probability that a specific similarity threshold has been met can be calculated.
-We use 33 bands of 3-min-hashes where the probability of a Jaccard similarity of 60\% or greater is approximately 99\%. 
-Banding allows the problem of finding similar items to be parallelized across bands since all that is needed for a match is a single band match.
-
-Together, min-hashing and LSH provide the foundation for both operating modes of RUPEE, fast and top-aligned.
-
-\subsection*{Operating modes}
-
-RUPEE provides two modes, fast and top-aligned. 
-Each operating mode builds on the results provided by the min-hashing and LSH system described above. 
-When a structure search is executed in either mode, a number of concurrent tasks are executed corresponding to the number of bands used for LSH. 
-These concurrent tasks identify candidate matches based on a single band match and then validate the matches based on a comparison of min-hashes.
-
-In fast mode, the top 8,000 matches are obtained along with the original gram sequences defined for the structures.
-A further validation is done by performing a longest common subsequence (LCS) analysis of the matched gram sequences and adjusting the Jaccard similarity scores accordingly.
-This step accounts for possible gram matches among pairs of structures that are out of order since the min-hashing and LSH techniques themselves do not consider the order of the gram matches.
-The final step of fast mode is to sort the matches based on the adjusted scores and return the results.
-
-Top-aligned is an additional step following fast mode. 
-First, unoptimized CE alignments are performed on the top 2,000 matches obtained from fast mode. 
-Then optimized CE alignments are performed on the top 400 matches and these are finally returned sorted either by RMSD or TM-Score. 
-Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.
-
-\section*{Results}
-
-Protein structure searches can be evaluated using pairwise alignment scores or by comparison of results against the hierarchy of a protein structure classification database.
-The RMSD of aligned residues is widely used in evaluations but is not perfectly suited to full-length comparisons between structures since distances between unaligned residues are not factored into the score.
-On the other hand, the TM-score \cite{Zhang2004} takes all residues into account. 
-Among protein structure classification databases for which corresponding structure searches exist, SCOPe \cite{Fox2013} and CATH \cite{Orengo1997} are the most popular.
-
-For our results, we have created 3 benchmarks, scop\_d360, scop\_d62, and cath\_d99, for pairwise evaluations to mTM, SSM, and CATHEDRAL, respectively.
-scop\_d360 is derived from the d500 benchmark used in \cite{Dong2018} filtered for domains in SCOPe 2.07 for which mTM returns 100 or more results.
-Similarly, scop\_d62 is derived from the d500 benchmark filtered for domains defined in SCOP 1.73 for which SSM returns 50 or more results.  
-In keeping with our description of RUPEE in \cite{Ayoub2017}, the cath\_d99 benchmark contains 99 superfamily representatives from the top 100 most diverse superfamilies defined in CATH v4.2 for which CATHEDRAL returns results in less than 12 hours.
-
-We perform pairwise evaluations to ensure the fairness of our comparisons. 
-First, for domain searches, SSM is working with the SCOP 1.73 database, so accordingly we operate RUPEE on SCOP 1.73 domains to ensure RUPEE does not have more domains to work with for scoring and precision evaluations.
-Second, mTM is updated to work with SCOPe 2.07 domain definitions but still retains domains from 2.06 that have since been redefined either through mergers or splits in 2.07. 
-On the other hand, CATHEDRAL presents no such challenges but still requires a separate benchmark since it is working with a distinct hierarchy, CATH v4.2.
-
-All benchmark definitions can be found in \nameref{S3_Benchmarks}.
-
-\subsection*{Scoring}
-
-\figurename~\ref{fig:combined_scoring_ce} shows average cumulative values for each ranked result averaged over all searches.
-Both RMSD and TM-score values are shown, provided as outputs from optimized CE pairwise alignments. 
-A TM-score above 0.5 is a good predictor for whether or not two domains are in the same fold \cite{Xu2010}.
-TM-scores greater than 0.17 are considered potentially meaningful whereas TM-scores less than 0.17 are considered to be due to random alignment \cite{Zhang2004}.
-
-\begin{figure*}[!h]
-\caption{Scoring from CE pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
-\label{fig:combined_scoring_ce}
-\end{figure*}
-
-A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S1_Fig}. 
-The same relative relationships hold with only small variations.
-
-RUPEE fast, top-aligned sorted by RMSD, and top-aligned sorted by TM-Score, perform better than SSM and CATHEDRAL.
-The scoring in the cath\_d99 benchmark comparisons are notably lower than for the other two benchmarks. 
-This is expected since CATHEDRAL only returns CATH s35 representatives.
-Likewise, for this comparison RUPEE is filtered for s35 representatives to match. 
-Given that the cath\_d99 benchmark is evaluated against representatives, there are fewer highly similar structures returned in the results.
-
-In our evaluation, mTM faired better than SSM and CATHEDRAL. 
-mTM also performed better than RUPEE fast, although RUPEE fast is still within 0.08 TM-Score points of mTM at the 100\textsuperscript{th} result, which is notable considering its speed.
-
-For TM-Score, RUPEE top-aligned and mTM are nearly identical with RUPEE slightly better for ranks less than 50 and mTM better for ranks greater than 50. 
-For RMSD, RUPEE top-aligned does perform better than mTM but this can most likely be attributed to the fact that mTM only sorts by TM-Score. 
-If mTM sorted by RMSD we suspect the results again would be nearly identical.
-Nevertheless, it is worth noting that the initial LSH and min-hashing technique does not explicitly bias results towards one particular measure.
-
-\subsection*{Precision}
-
-\figurename~\ref{fig:combined_precision} shows precision (i.e.
-positive predictive value or PPV) averaged over all searches, where positive results are defined as domains with the same classification for the indicated hierarchy level as the query domain.
-A plot of recall is unnecessary since \figurename~\ref{fig:combined_precision} provides precision at specific ranks for identical sets of searches. 
-Hence, recall curves have the same relative relationships as those shown for precision.
-
-\begin{figure*}[!h]
-\caption{Precision for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
-\label{fig:combined_precision}
-\end{figure*}
-
-We should expect a structure search to have reasonable precision with respect to the hierarchy levels of the structure classification it is searching. 
-However, it is not clear how to define reasonable. 
-On the other hand, if precision is too high, the search provides little value beyond that provided by the structure classification hierarchy it is searching. 
-Towards the extreme end of high precision, it would be sufficient for a search to return the best match and from there refer to the hierarchy for additional results.
-
-Similar to the scoring evaluations above, RUPEE fast and top-aligned, sorted by both RMSD and TM-Score, show higher precision than SSM and CATHEDRAL with the exception of RUPEE top-aligned sorted by RMSD for ranks lower than 10 compared against SSM.
-
-Again, mTM faired better than SSM and CATHEDRAL. 
-Notably, mTM also shows clearly higher precision than RUPEE top-aligned, sorted by both RMSD and TM-Score. 
-In the absence of \figurename~\ref{fig:combined_scoring_ce}, one may be led to regard this as a negative result. 
-However, to the contrary, in the presence of \figurename~\ref{fig:combined_scoring_ce}, where it is shown that RUPEE and mTM have almost identical scoring, this result is remarkable. 
-This disparity suggest that RUPEE is better able to find significantly similar matches not necessarily aligned with the SCOPe hierarchy. 
-In fact, since the initial min-hashing and LSH technique used by RUPEE check for similarity to all available structures, no structure is able to hide behind a sequence based cluster representative. 
-So this result is in keeping with how RUPEE is intended to work and how it is described above.
-
-\subsection*{Response Times}
-
-\figurename~\ref{fig:combined_response} shows response times in seconds for the scop\_d62 and cath\_d99 benchmarks. 
-Here, we are able to show RUPEE fast and top-aligned, mTM and SSM on the same plot because scop\_d62 is a subset of the scop\_d360 benchmark. 
-Both plots are shown with a logarithmic scale in order to include all outliers while still being able to view the overall trends in response times. 
-Loess regression curves are also provided to further highlight the overall trends.
-
-\begin{figure*}[h!]
-\caption{Response times for RUPEE fast and RUPEE top-aligned. The response times for RUPEE top-aligned are dominated by pairwise structure alignments and do not depend on the sort order.}
-\label{fig:combined_response}
-\end{figure*}
-
-In all cases, RUPEE fast is considerably faster than all other searches. 
-It is also clear that fast mode is not as sensitive to increasing residue counts in contrast to CATHEDRAL and RUPEE top-aligned.
-Response times for SSM are not affected by residue counts at all and always returns results in less than 100 seconds but this is at the expense of performance as shown in \figurename~\ref{fig:combined_scoring_ce}.
-
-In the left plot of \figurename~\ref{fig:combined_response}, it is shown that RUPEE top-aligned is faster than mTM for residue counts below 200, but then response times for RUPEE increase beyond that of mTM.
-Down the stretch, mTM provides increasingly better response times than RUPEE, while RUPEE is still able to provide reasonable response times. 
-The right plot of \figurename~\ref{fig:combined_response} shows RUPEE top-aligned is significantly faster than CATHEDRAL for all residue counts.
-
-The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.
-
-Response times to a large degree are a measure of the amount of resources available to an application. 
-In the case of RUPEE, our response times were gathered from RUPEE running on a fairly old laptop with a 2nd generation Intel\textregistered{} Core\texttrademark{} i7-2720QM Quad-Core CPU and 8 GB of memory.
-With more resources the response times of RUPEE can be further improved since pairwise alignments can be run in parallel. 
-For mTM, SSM, and CATHEDRAL, we gathered response times by automating their respective web sites using the Selenium WebDriver API.
+\begin{itemize}
+	\item First bulleted item.
+	\item Second bulleted item.
+	\item Third bulleted item.
+\end{itemize}
 
 \section*{Discussion}
-
-As shown above, a purely geometric big data approach to protein structure search can compete with the best available protein structure searches.
-Nonetheless, there remain avenues for further improvement and investigation.
-
-While our min-hashing and LSH scheme does allow for some flexibility in the size of matched protein structures, it is not specifically designed for containment searches. 
-However, the initial min-hashing and LSH search does operate fast enough, within seconds, that it does present the possibility of executing multiple searches within the context of a single query. 
-With more resources, we can distribute min-hash and band data across multiple compute units, with each data set representing a subset of chopped structure representations. 
-With a 75\% overlap of these subsets, RUPEE searches effectively become containment searches.
-
-We have tried the overlapping subset idea and have found it to be effective. 
-However, on a single compute unit, the time required is more than we are willing to accept for this first iteration of RUPEE.
-
-One possible drawback of RUPEE is that in both fast and top-aligned modes, it only returns the top 400 results. 
-Again, with more resources, this number can be increased, but there still remains a need for some kind of cut-off. 
-Nonetheless, in most search tools, having to looking past the first few hundred results usually indicates an ineffective search strategy.
-To this end, RUPEE provides filters that can be used for traversing structure space more efficiently. 
-For SCOPe, CATH, and ECOD you can instruct the search to only return domains that differ from the query structure at a chosen hierarchy level classification. 
-Additionally, for CATH you can filter results based on hierarchy level representatives. 
-Since RUPEE does not rely on sequence clusters, these kinds of filters are easy to implement, do not reduce the number of returned results, and allow for the discovery of unexpected structural similarities across classification hierarchies.
-
-One area that stands out for possible improvement is our longest common subsequence (LCS) scoring adjustment to the results initially returned by RUPEE. 
-While the LCS step has been shown to be effective, it is notable for its simplicity. 
-A more complex step of validating the sequence of gram matches can take a form similar to the path extension algorithm used by CE. 
-In this case, sequences of matches would only be extended when the difference of interresidue distances between gram pairs already in the sequence and a candidate pair to be added to the sequence fall below some threshold.
-
-On the other hand, it would be interesting to see where further analysis of the initial results returned by RUPEE before LCS and any sort of order enforcement beyond that of the grams themselves could lead.
-For instance, topological permutations such as circular permutations, segment-swapping and changing secondary structures within homologous proteins are not uncommon \cite{Andreeva2007}. 
-The initial RUPEE min-hashing and LSH algorithm provides candidate matches along with matched grams. 
-With some thought, an algorithm similar to FATCAT can be developed allowing for permutations in addition to twists.
-
-As can be observed from considering \figurename~\ref{fig:combined_scoring_ce} and \figurename~\ref{fig:combined_precision} together, there are good domain matches aligned with the SCOPe hierarchy that mTM is able to find that RUPEE does not.
-Conversely, there are good domain matches not aligned with the SCOPe hierarchy that RUPEE finds and mTM does not. 
-A comprehensive listing of these difference may find interesting similarities not previously known.
+Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero~\cite{Crick1970}.
 
@@
 
-With the growth rate of solved structures deposited in the PDB, the need for a fast and scalable structure search is growing. 
-Using run position encoded shingles of residue descriptors combined with min-hashing and LSH, we have shown that RUPEE fast is able to provide good results in seconds running on an Quad-Core laptop.
-Currently, RUPEE fast is the fastest available protein structure search providing the demonstrated level of accuracy. 
-For RUPEE top-aligned, we have shown that a purely geometric big data approach to protein structure search is able to produce results equal to or better than the current state of the art protein structure searches that variously depend on clustered sequences or protein structure classification hierarchies.
-Moreover, we have shown evidence that suggests the results from RUPEE top-aligned provide more added value by discovering high scoring protein structure matches not necessarily aligned with a particular protein structure classification hierarchy or hiding behind cluster representatives.
-The ability for RUPEE to quickly examine all structures among hundreds of thousands sets it apart as a tool that can be used for discovering previously undetected structural similarities.
+CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+
+Sed non aliquet felis.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Mauris commodo justo ac dui pretium imperdiet.
+Sed suscipit iaculis mi at feugiat.
+Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
+Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+Nam condimentum sem eget mollis euismod.
+Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
+Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
+Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
+For more information, see \nameref{S1_Appendix}.
 
@@
 
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
 \paragraph*{S1 Fig.}
 \label{S1_Fig}
-{\bf Scoring from FATCAT pairwise alignments.}
+{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 
-\paragraph*{S2 Methods.}
-\label{S2_Methods}
-{\bf Run factors for shingles instead of descriptors.}
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
 
-\paragraph*{S3 Benchmarks.}
-\label{S3_Benchmarks}
-{\bf Domains included in benchmarks used for evaluation.}
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Video.}
+\label{S1_Video}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Appendix.}
+\label{S1_Appendix}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Table.}
+\label{S1_Table}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\section*{Acknowledgments}
+Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
 
@@
 % 
-\begin{thebibliography}{10}
+%\begin{thebibliography}{10}
 
-\bibitem{Crick1970}
-Crick F.
-\newblock Central dogma of molecular biology.
-\newblock Nature. 1970;227(5258):561--563.
+%\end{thebibliography}
 
-\bibitem{Fox2013}
-Fox NK, Brenner SE, Chandonia JM.
-\newblock {SCOP}e: Structural Classification of Proteins - extended,
-  integrating {SCOP} and {ASTRAL} data and classification of new structures.
-\newblock Nucleic Acids Res. 2014;42(1):304--309.
-
-\bibitem{Orengo1997}
-Orengo C, Mitchie A, Jones S, Jones DT, Swindells M, Thornton JM.
-\newblock {CATH} - A hierarchic classification of protein domain structures.
-\newblock Structure. 1997;5(8):1093--1109.
-
-\bibitem{Cheng2014}
-Cheng H, Schaeffer RD, Liao Y, Kinch LN, Pei J, Shi S, et~al.
-\newblock {ECOD: An Evolutionary Classification of Protein Domains}.
-\newblock PLoS Computational Biology. 2014;10(12).
-
-\bibitem{Dong2018}
-Dong R, Pan S, Peng Z, Zhang Y, Yang J.
-\newblock {mTM-align: a server for fast protein structure database search and
-  multiple protein structure alignment}.
-\newblock Nucleic Acids Research. 2018;46(July):380--386.
-
-\bibitem{Krissinel2004}
-Krissinel E, Henrick K.
-\newblock {Secondary-structure matching (SSM), a new tool for fast protein
-  structure alignment in three dimensions}.
-\newblock Acta Crystallographica Section D: Biological Crystallography.
-  2004;60(12 I):2256--2268.
-
-\bibitem{Redfern2007}
-Redfern OC, Harrison A, Dallman T, Pearl FMG, Orengo CA.
-\newblock {CATHEDRAL}: A Fast and Effective Algorithm to Predict Folds and
-  Domain Boundaries from Multidomain Protein Structures.
-\newblock {PL}o{S} Comput Biol. 2007;3(11):e232.
-
-\bibitem{Shindyalov1998}
-Shindyalov IN, Bourne PE.
-\newblock Protein structure alignment by incremental combinatorial extension
-  ({CE}) of the optimal path.
-\newblock Protein Eng Des Sel. 1998;11(9):739--747.
-
-\bibitem{Ye2003}
-Yuzhen~Ye AG.
-\newblock Flexible structure alignment by chaining aligned fragment pairs
-  allowing twists.
-\newblock Bioinformatics. 2003;19(2):246--255.
-
-\bibitem{Gilbrat1996}
-Gilbrat JF, Madej T, Bryant SH.
-\newblock Surprising similarities in structure comparison.
-\newblock Curr Opin Struct Biol. 1996;6(3):377--385.
-
-\bibitem{Ye2004}
-Yuzhen~Ye AG.
-\newblock {FATCAT}: a web server for flexible structure comparison and
-  structure similarity searching.
-\newblock Nucleic Acids Res. 2004;32(2):582--585.
-
-\bibitem{Prlic2010}
-Prli{\'c} A, Bliven S, Rose PW, Bluhm WF, Bizon C, Godzik A, et~al.
-\newblock Pre-calculated protein structure alignments at the {RCSB} {PDB}
-  website.
-\newblock Bioinformatics. 2010;26(23):2983--2985.
-
-\bibitem{gkw1000}
-Rose PW, Prli{\'c} A, Altunkaya A, Bi C, Bradley AR, Christie CH, et~al.
-\newblock The {RCSB} protein data bank: integrative view of protein, gene and
-  {3D} structural information.
-\newblock Nucleic Acids Res. 2017;45(D1):D271--D281.
-
-\bibitem{Carpentier2005}
-Carpentier M, Brouillet S, Pothier J.
-\newblock {YAKUSA}: A fast structural database scanning method.
-\newblock Proteins. 2005;61(1):137--151.
-
-\bibitem{Daniluk2011}
-Daniluk P, Lesyng B.
-\newblock A novel method to compare protein structures using local descriptors.
-\newblock BMC Bioinformatics. 2011;12(1):344.
-
-\bibitem{Ritchie2012}
-Mavridis L, Ritchie DW.
-\newblock In: {3D-Blast}: {3D} protein structure alignment, comparison, and
-  classification using spherical polar fourier correlations. World Scientific;
-  2012. p. 281--292.
-
-\bibitem{Ramachandran1968}
-Ramachandran GN, Sasisekharan V.
-\newblock Conformation of polypeptides and proteins.
-\newblock Adv Protein Chem. 1968;23:283--438.
-
-\bibitem{Karplus2010}
-Hollingsworth SA, Karplus PA.
-\newblock A fresh look at the {R}amachandran plot and the occurrence of
-  standard structures in proteins.
-\newblock Biomol Concepts. 2010;1:271--283.
-
-\bibitem{Kabsch1983}
-Kabsch W, Sander C.
-\newblock Dictionary of protein secondary structure: Pattern recognition of
-  hydrogen-bonded and geometrical features.
-\newblock Biopolymers. 1983;22(12):2577--2637.
-
-\bibitem{Aungand2004}
-Aungand Z, Tan KL.
-\newblock Rapid 3D protein structure database searching using information
-  retrieval techniques.
-\newblock Bioinformatics. 2004;20(7):1045--1052.
-
-\bibitem{Zhang2010}
-Zhang L, Bailey J, Konagurthu AS, Ramamohanarao K.
-\newblock A fast indexing approach for protein structure comparison.
-\newblock {BMC} Bioinformatics. 2010;11(Suppl 1):S46.
-
-\bibitem{Budowski2010}
-Budowski-Tal I, Nov Y, Kolodny R.
-\newblock {FragBag}, an accurate representation of protein structure, retrieves
-  structural neighbors from the entire {PDB} quickly and accurately.
-\newblock Proceedings of the National Academy of Sciences.
-  2010;107(8):3481--3486.
-
-\bibitem{Broder1997a}
-Broder AZ.
-\newblock On the resemblance and containment of documents.
-\newblock In: Proc. Compression and Complexity of Sequences. Positano, Italy;
-  1997. p. 21--29.
-
-\bibitem{Ayoub2017}
-Ayoub R, Lee Y.
-\newblock RUPEE: Scalable protein structure search using run position encoded
-  residue descriptors.
-\newblock In: 2017 IEEE International Conference on Bioinformatics and
-  Biomedicine (BIBM); 2017. p. 74--78.
-
-\bibitem{Karp1987}
-Karp RM, Rabin MO.
-\newblock Efficient randomized pattern-matching algorithms.
-\newblock {IBM} Journal of Research and Development. 1987;31(2):249--260.
-
-\bibitem{Levan1971}
-Levandowsky M, Winter D.
-\newblock Distance between Sets.
-\newblock Nature. 1971;234(5323):34--35.
-
-\bibitem{Broder1997b}
-Broder AZ, Glassman SC, Manasse MS, Zweig G.
-\newblock Syntactic clustering of the Web.
-\newblock Computer Networks and ISDN Systems. 1997;29(8-13):1157--1166.
-
-\bibitem{Joshi2008}
-Joshi S, Contractor D, Ng K, Deshpande PM, Hampp T.
-\newblock Auto-grouping emails for faster e-discovery.
-\newblock In: Proceedings of Very Large Databases Endowment 2011. vol.~4; 2011.
-  p. 1284--1294.
-
-\bibitem{Broder1998}
-Broder AZ, Charikar M, Frieze AM, Mitzenmacher M.
-\newblock Min-wise independent permutations.
-\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
-  327--336.
-
-\bibitem{Indyk1998}
-Indyk P, Motwani R.
-\newblock Approximate nearest neighbors: towards removing the curse of
-  dimensionality.
-\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
-  604--613.
-
-\bibitem{Rajaraman2012}
-Rajaraman A, Ullman JD.
-\newblock 3.
-\newblock In: Mining of Massive Datasets. Cambridge University Press; 2012. p.
-  53--70.
-
-\bibitem{Zhang2004}
-Zhang Y, Skolnick J.
-\newblock Scoring function for automated assessment of protein structure
-  template quality.
-\newblock Proteins. 2004;57(4):702--710.
-
-\bibitem{Xu2010}
-J~Xu YZ.
-\newblock How significant is a protein structure similarity with {TM}-score =
-  0.5?
-\newblock Bioinformatics. 2010;26(7):889--895.
-
-\bibitem{Andreeva2007}
-Andreeva A, Prli{\'c} A, Hubbard TJP, Murzin AG.
-\newblock {SISYPHUS}: structural alignments for proteins with non-trivial
-  relationships.
-\newblock Nucleic Acids Res. 2007;35(1):253--259.
-
-\bibitem{BioJava2012}
-Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
-\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
-\newblock Bioinformatics. 2012;28(20):2693--2695.
-
-\end{thebibliography}
+\bibliography{rupee}
 

### 2019-08-20 docs/rupee.tex
increment

@@
 \section*{Introduction}
-Lorem ipsum dolor sit~\cite{Crick1970} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{Crick1970} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
-\begin{eqnarray}
-\label{eq:schemeP}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
+[very rough outline of intro]Protein structure is strongly correlated to function. 
+Protein structure prediction is a central unsolved problem in science. 
+Recent advances by alphafold have refocused attention on this problem. 
+Nevertheless, more work has to be done and some thought can be put into tools to assist the process of prediction methods. 
+Protein structure search can be used to debug and guide. 
+Fold identification of prediction outputs.
 
-\section*{Materials and methods}
-\subsection*{Etiam eget sapien nibh}
+[transition paragraph]We first discuss some related work to provide a context for our approach followed by a description of our method. 
+This is followed by a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website.
+To further illustrate the performance of RUPEE, we show top scoring alignments found by RUPEE and not found by any of the other searches we compare against.
+
+[do i need related work. there is no related work specifically for a search to assist protein structure prediction]
+
+\section*{Methods}
+
+[NOTE: this assumes we have introduced top-aligned mode and all-aligned mode in the introduction]
+
+We first provide an brief outline of our linear encoding of protein structures described in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
+Then, we describe the addition of containment searches, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
+
+\subsection*{Linear encoding of protein structure}
+
+[NOTE: get rid of the bags]
+
+In \cite{Ayoub2019}, we introduced a linear encoding of protein structures based on separable regions of permissible torsion angles. 
+For instance, a $\beta$-turn-$\beta$ motif may be represented as a sequence of residue descriptors similar to that shown below. 
+\begin{gather}\label{E:descrseq} 
+    [\, 5, 5, 5, 5, 5, 5, 7, 5, 11, 11, 5, 5, 5, 5, 5, 5 \,]
+\end{gather}
+
+Next, we derive a multiset of overlapping 3-grams of residue descriptors. 
+This representation is often referred to as shingling and was developed in \cite{Broder1997a}. 
+The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
+
+By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
+As an example, the sequence in (\ref{E:descrseq}) becomes the following bag of shingles. 
+\begin{align}\label{E:shinglebag}
+    \begin{split}
+        \{\,&[5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 7] \\
+            & [5, 7, 5], [7, 5, 11], [5, 11, 11], [11, 11, 5], [11, 5, 5] \\
+            & [5, 5, 5], [5, 5, 5], [5, 5, 5], [5, 5, 5] \,\}
+    \end{split}
+\end{align}
+
+Next, each shingle $s$ is hashed to an integer as shown in~(\ref{E:hashdef}). 
+\begin{gather}\label{E:hashdef}
+    s_{hash} = s_1 \times 13^2 + s_2 \times 13 + s_3
+\end{gather}
+
+After hashing, the multiset in (\ref{E:shinglebag}) becomes the following bag of integers.
+\begin{align}\label{E:hashbag}
+    \begin{split}
+    \{\,&915, 915, 915, 915, 917, 941, 1259 \\
+        &999, 2007, 1929, 915, 915, 915, 915 \,\}
+    \end{split}
+\end{align}
+
+The hashing completes the transformation of an ordered list of descriptors to a multiset of integers that still retains some of the order information present in the original list.
+
+Notice in (\ref{E:hashbag}) the value 915, corresponding to the shingle $[ 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
+To address this lack of specificity, we introduced a heuristic we called \emph{run position encoding} (RPE), where a run is a consecutive sequence of identical descriptors. 
+To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run. 
+Applied to the bag of integers in (\ref{E:hashbag}) gives
+\begin{align}\label{E:rpebag}
+    \begin{split}
+    \{\,&00915, 10915, 20915, 20915, 10917, 00941, 01259 \\
+        &00999, 02007, 01929, 00915, 10915, 20915, 20915 \,\}
+    \end{split}
+\end{align}
+where the leading zero run factors are shown for clarity.
+
+The pyramidal approach for the run factors preserves matches at the boundaries between secondary structure runs and loops that would not otherwise be preserved in the presence of differences in run lengths of one or more.
+
+\subsection*{Containment searches}
+
+Originally, the RUPEE protein structure search focused on full-length matches. 
+If you wanted to search for structures similar to a domain, you could search one of the protein domain classification databases such as SCOPe, CATH, or ECOD.
+On the other hand, if you wanted to search for structures similar to a whole chain, you could search whole chains from the PDB. 
+While the ability of RUPEE to search multiple databases for any given structure is flexible, adding the ability to execute containment searches extends this flexibility.
+
+Introduce NW semiglobal algorithm here refering to list above.
+
+\subsection*{Top-aligned mode}
+
+Another comparison that is natural follows. Referring to list as bags above. 
+Similarity for a candidate pair of structures $a$ and $b$ can now naturally be defined as the Jaccard similarity \cite{Levan1971} for multisets,
+\begin{align}
+    J(a,b) = \frac{\sum_i min(a_i, b_i)}{\sum_i max(a_i,b_i)}\text{,}
+\end{align}
+where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively.
+
+Min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} are used by RUPEE as described in \cite{Rajaraman2012} to quickly estimate the Jaccard similarity of a query protein against all available structures in the searched database.
+Min-hashing and LSH still provide the initial filtering for top-aligned mode, introduced in \cite{Ayoub2019}, but are not used in all-aligned mode, which we introduce below.
+
+Since Jaccard similarity is measure of similarity for entire sets, in the context of protein structure search, it is more suitable for full-length searches rather than containment searches.
+
+While Jaccard similarity is a good similarity score for full-length matches, it does not naturally lends itself to containment comparisons. 
+h
+
+Since Jaccard similarity is measure of similarity for entire sets, in the context of protein structure search, it is more suitable for full-length searches rather than containment searches.
+
+Estimates of Jaccard similarity, a measure of similarity between 2 whole sets.  alone is not appropriate for performing containment searches 
+Given two sequences of run position encoded shingle hashes similar to the multiset shown in (\ref{E:rpebag}) but ordered, we perform a Needleman-Wunsh alignment
+
+\subsection*{All-aligned mode}
+Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
+
+% Place figure captions after the first paragraph in which they are cited.
+\begin{figure*}[!h]
+\includegraphics{Fig5}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig5}
+\end{figure*}
 
@@
 % Place figure captions after the first paragraph in which they are cited.
-\begin{figure}[!h]
+\begin{figure*}[!h]
+\includegraphics{Fig1}
 \caption{{\bf Bold the figure title.}
@@
 \label{fig1}
-\end{figure}
+\end{figure*}
 
@@
 
+% Place figure captions after the first paragraph in which they are cited.
+\begin{figure*}[!h]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\includegraphics{Fig2}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig2}
+\end{adjustwidth}
+\end{figure*}
+
 \begin{enumerate}
@@
 
+% Place figure captions after the first paragraph in which they are cited.
+\begin{figure*}[!h]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\includegraphics{Fig3}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig3}
+\end{adjustwidth}
+\end{figure*}
+
 \section*{Conclusion}
@@
 Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+
+% Place figure captions after the first paragraph in which they are cited.
+\begin{figure*}[!h]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\includegraphics{Fig4}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig4}
+\end{adjustwidth}
+\end{figure*}
 

### 2019-08-20 docs/rupee.tex
increment

@@
 
-We first provide an brief outline of our linear encoding of protein structures described in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
-Then, we describe the addition of containment searches, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
+We first provide a brief outline of our linear encoding of protein structures described in more detail in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
+Then, we describe the similarity scores we use for the initial filtering of full-length and containment searches, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
 
@@
 
-[NOTE: get rid of the bags]
-
-In \cite{Ayoub2019}, we introduced a linear encoding of protein structures based on separable regions of permissible torsion angles. 
-For instance, a $\beta$-turn-$\beta$ motif may be represented as a sequence of residue descriptors similar to that shown below. 
+In \cite{Ayoub2019}, we introduced a linear encoding of protein structures.
+For each pair of torsion angles combined with their secondary structure assignment, we assign an integer we refer to as a residue descriptor.
+For instance, a $\beta$-turn-$\beta$ motif may be represented as a sequence of residue descriptors, similar to that shown below. 
 \begin{gather}\label{E:descrseq} 
@@
 This representation is often referred to as shingling and was developed in \cite{Broder1997a}. 
-The overlap between shingles ensures some of the order information within the original sequence is preserved in the bag.
+The overlap between shingles ensures some of the order information within the original sequence is preserved in the multiset.
 
-By shingling, we obtain a multiset of ordered lists from an ordered list of numbers. 
-As an example, the sequence in (\ref{E:descrseq}) becomes the following bag of shingles. 
+By shingling, we obtain a multiset of ordered lists from an ordered list of residue descriptors. 
+As an example, the sequence in (\ref{E:descrseq}) becomes the following multiset of shingles. 
 \begin{align}\label{E:shinglebag}
@@
 
-After hashing, the multiset in (\ref{E:shinglebag}) becomes the following bag of integers.
+After hashing, the multiset in (\ref{E:shinglebag}) becomes the following multiset of integers.
 \begin{align}\label{E:hashbag}
@@
 
-The hashing completes the transformation of an ordered list of descriptors to a multiset of integers that still retains some of the order information present in the original list.
+The hashing completes the transformation of an ordered list of residue descriptors to a multiset of integers that still retains some of the order information present in the original list.
 
 Notice in (\ref{E:hashbag}) the value 915, corresponding to the shingle $[ 5, 5, 5 ]$, occurs frequently indicating the presence of $\beta$-strands. 
-To address this lack of specificity, we introduced a heuristic we called \emph{run position encoding} (RPE), where a run is a consecutive sequence of identical descriptors. 
+To address this lack of specificity, we introduced a heuristic we call \emph{run position encoding} (RPE), where a run is a consecutive sequence of identical descriptors. 
 To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run. 
-Applied to the bag of integers in (\ref{E:hashbag}) gives
+Applied to the multiset of integers in (\ref{E:hashbag}) gives
 \begin{align}\label{E:rpebag}
@@
 
-\subsection*{Containment searches}
+\subsection*{Similarity scores}
+
+In one case, RUPEE uses the multiset-of-integers representation of protein structures as shown in (\ref{E:rpebag}), and in another case RUPEE regards this multiset as an ordered list of integers.  
+We describe the context in which these cases occur in subsequent sections below, but first, we discuss the similarity scores that RUPEE uses for each representation.
+
+When representing each protein structure using a multiset of integers as shown in (\ref{E:rpebag}), full-length similarity for a candidate pair of structures $a$ and $b$ is defined using the Jaccard similarity \cite{Levan1971} for multisets,
+\begin{align}
+    J(a,b) = \frac{\sum_i min(a_i, b_i)}{\sum_i max(a_i,b_i)}\text{,}
+\end{align}
+where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively. 
+In words, the Jaccard similarity is the proportion of matched shingles to the total number of shingles.
+
+When regarding the multiset in (\ref{E:rpebag}) as an ordered list of integers, we assign a pair of protein structures a full-length similarity score using a simplified Needleman-Wunsch \cite{Needleman1970} algorithm where mismatches and gaps are penalized -1 points and matches are awarded +1 points.
 
@@
 While the ability of RUPEE to search multiple databases for any given structure is flexible, adding the ability to execute containment searches extends this flexibility.
+Therefore, in addition to searching for full-length matches, RUPEE now supports explicit containment searches for \emph{Contained-In} and \emph{Contains}  relationships.
 
-Introduce NW semiglobal algorithm here refering to list above.
+In the case where we regard the multiset in (\ref{E:rpebag}) as an ordered list of integers, we score containment using the same simplified Needleman-Wunsch \cite{Needleman1970} algorithm we use for full-length similarity with one small change.
+For containment searches, depending on whether or not the search type is Contained-In or Contains, one of the sides of the dynamic programming matrix is not penalized for the opening gap and end gap.
+This is often referred to as semi-global alignment and was developed in \cite{Brudno2003}. 
+As it turns out, semi-global alignment is a natural fit for containment comparisons as long as the directionality of containment is explicit.
 
 \subsection*{Top-aligned mode}
-
-Another comparison that is natural follows. Referring to list as bags above. 
-Similarity for a candidate pair of structures $a$ and $b$ can now naturally be defined as the Jaccard similarity \cite{Levan1971} for multisets,
-\begin{align}
-    J(a,b) = \frac{\sum_i min(a_i, b_i)}{\sum_i max(a_i,b_i)}\text{,}
-\end{align}
-where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively.
 

### 2019-08-21 docs/rupee.tex
increment

@@
 We first provide a brief outline of our linear encoding of protein structures described in more detail in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
-Then, we describe the similarity scores we use for the initial filtering of full-length and containment searches, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
+Then, we describe the types of similarity scores used for the initial filtering in the different search modes, the addition of search types, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
 
@@
 To distinguish between short and long runs, thereby increasing the specificity of the shingles, we add a factor of $10^5$ to each shingle hash as a function of the first residue's position in a run. 
-Applied to the multiset of integers in (\ref{E:hashbag}) gives
+Applying to the multiset of integers in (\ref{E:hashbag}) gives
 \begin{align}\label{E:rpebag}
@@
 
-When regarding the multiset in (\ref{E:rpebag}) as an ordered list of integers, we assign a pair of protein structures a full-length similarity score using a simplified Needleman-Wunsch \cite{Needleman1970} algorithm where mismatches and gaps are penalized -1 points and matches are awarded +1 points.
+When regarding the multiset in (\ref{E:rpebag}) as an ordered list of integers, we assign a pair of protein structures a full-length similarity score using a simplified Needleman-Wunsch \cite{Needleman1970} dynamic programming algorithm where mismatches and gaps are penalized -1 points and matches are awarded +1 points.
+
+\subsection*{Search types}
 
@@
 While the ability of RUPEE to search multiple databases for any given structure is flexible, adding the ability to execute containment searches extends this flexibility.
-Therefore, in addition to searching for full-length matches, RUPEE now supports explicit containment searches for \emph{Contained-In} and \emph{Contains}  relationships.
+Therefore, RUPEE now supports explicit search types for \emph{Contained-In} and \emph{Contains} searches in addition to the \emph{Full-Length} search type.
 
@@
 
-Min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} are used by RUPEE as described in \cite{Rajaraman2012} to quickly estimate the Jaccard similarity of a query protein against all available structures in the searched database.
-Min-hashing and LSH still provide the initial filtering for top-aligned mode, introduced in \cite{Ayoub2019}, but are not used in all-aligned mode, which we introduce below.
+For top-aligned mode, RUPEE uses min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} as described in detail in our previous work \cite{Ayoub2019} to quickly estimate the Jaccard similarity of a query protein against all available structures in the searched database.
+Then, the top scoring 40000 protein structures are obtained based on the Jaccard similarity estimates to complete the initial filtering.
 
+After the initial filtering, we obtain more accurate similarity scores for the filtered matches using the simplified Needleman-Wunsch algorithm. 
+Here, the dynamic programming matrix for Needleman-Wunsch is scored as described above based on the chosen search type, Contained-In, Contains, or Full-Length. 
+Then, we execute TM-align on the top scoring 8000 matches from Needleman-Wunsch using a reduced number of dynamic programming iterations in the TM-align algorithm. 
+We sort these initial alignments by TM-score and obtain the top 400 matches.
+Finally, we execute TM-align using the default number of dynamic programming iterations on the top 400 matches and return the results sorted by TM-score.
+
+The filter sizes of 40000, 8000 and 400 have been chosen based on quality of results and speed. 
+We have found that increasing the size of either of these filters results in only marginal improvements in the quality of results. 
+Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.
+
+\subsection*{All-aligned mode}
 Since Jaccard similarity is measure of similarity for entire sets, in the context of protein structure search, it is more suitable for full-length searches rather than containment searches.
@@
 Given two sequences of run position encoded shingle hashes similar to the multiset shown in (\ref{E:rpebag}) but ordered, we perform a Needleman-Wunsh alignment
-
-\subsection*{All-aligned mode}
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
 
@@
 \section*{Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero~\cite{Crick1970}.
 
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure*}[!h]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\includegraphics{Fig3}
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig3}
-\end{adjustwidth}
-\end{figure*}
+Top-aligned is not ideal for containment searches.
 
 \section*{Conclusion}
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure*}[!h]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\includegraphics{Fig4}
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig4}
-\end{adjustwidth}
-\end{figure*}
-
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
 

### 2019-08-22 docs/rupee.tex
increment

@@
 
-[very rough outline of intro]Protein structure is strongly correlated to function. 
-Protein structure prediction is a central unsolved problem in science. 
-Recent advances by alphafold have refocused attention on this problem. 
-Nevertheless, more work has to be done and some thought can be put into tools to assist the process of prediction methods. 
-Protein structure search can be used to debug and guide. 
-Fold identification of prediction outputs.
+Determining the structure of a protein is the key to understanding its function [cite]. 
+Current structure determination methods such as X-ray crystallography and nuclear magnetic resonance (NMR) are timing consuming methods. 
+Given the throughput of next gen sequencing methods, physical protein structure determination are unable to keep pace.
+The ability to predict a protein structure from its amino acid sequence would address this problem. 
+However, protein structure prediction remains a central unsolved problem in molecular biology.
 
-[transition paragraph]We first discuss some related work to provide a context for our approach followed by a description of our method. 
-This is followed by a comparison of results against the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007} available at the CATH website.
-To further illustrate the performance of RUPEE, we show top scoring alignments found by RUPEE and not found by any of the other searches we compare against.
+CASP is a biannual blind competition for protein structure prediction that started year x. 
+Progress has been slow until the success of coevolutionary methods in contact prediction in CASP11 [cite CASP eval paper].
+Additionally, the recent success of Alphabet's AlphaFold at CASP13 using deep learning combined with coevolutionary methods has refocused interest in the problem. 
+While AlphaFold's contribution was significant, the problem remains largely unsolved and more work remains to be done [cite alquarishi].
 
-[do i need related work. there is no related work specifically for a search to assist protein structure prediction]
+In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence sequences, clustering, and precalculate results. 
+We compared our results with the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches from a benchmark of known protein domains.
+Additionally, we showed RUPEE on average is able to return results faster than mTM-align and CATHEDRAL.
+
+Since the release of RUPEE, we have observed that the primary usage pattern for RUPEE has been to upload protein structures that have a very low maximum similarity to other structures in the PDB or any of the domain classifications databases.
+In most cases, these uploaded protein structures are the output of a protein structure prediction protocol. 
+While in \cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in development of protein structure prediction protocols.
+For instance, besides measuring the similarity of a predicted structure to a target structure, it is also natural to determine what known structure a predicted structure resembles most.
+
+Recognizing the need for being able to search on query structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 
+While top-aligned mode, introduced in \cite{Ayoub2019}, is comparitively good for low similarity searches, the all-aligned mode we introduce below provides a significant improvement over top-aligned mode in that case.
+In this paper, we again compare RUPEE's results mTM-align, SSM, and CATHEDRAL but this time we do so for all-aligned mode and we derive a benchmark from free-modelling predictions in CASP12. 
+Whereas in \cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, in this paper we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction protocols.
+
+Originally, the RUPEE protein structure search focused on full-length matches. 
+If you wanted to search for structures similar to a domain, you could search one of the protein domain classification databases such as SCOPe, CATH, or ECOD.
+On the other hand, if you wanted to search for structures similar to a whole chain, you could search whole chains from the PDB. 
+While the ability of RUPEE to search multiple databases for any given structure is flexible, adding the ability to execute containment searches extends this flexibility.
+Therefore, RUPEE now supports explicit search types for \emph{Contained-In} and \emph{Contains} searches in addition to the \emph{Full-Length} search type.
+
+Together, all-aligned mode and containment searches are siginificant additions to RUPEE that increase its utility and further demonstrates the advantage of a purely geomietric protein structure search without dependencies on sequence, precalculated results or clustering.
+
+\section*{Related work}
+
+Pairwise alignment involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric. 
+Traditionally, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
+However, the RMSD score does not factor in the distance between unaligned residues nor does it consider the percentage of aligned residues, that is, alignment \emph{coverage}. 
+RMSD scores also have some dependence on the length of the aligned proteins. 
+On the other hand, the TM-score \cite{Zhang2004} takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
+For this reason, TM-score is frequently used in the assessment of protein structure alignments.
+
+Pairwise alignments often favor accuracy over speed because the typical use case of aligning one protein structure to another does not impose tight response time requirements. 
+On the other hand, a protein structure search can involve thousands of comparisons and accuracy is often balanced against speed. 
+In this case, pairwise alignment is still useful for evaluating the results of a search, and this is the approach we take.
+
+For pairwise alignment, Combinatorial Extensions (CE) \cite{Shindyalov1998} and FATCAT \cite{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
+CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
+
+Besides CE and FATCAT, TM-align \cite{Zhang2005} and DALI \cite{Sander1995} are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
+TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
+DALI compares intramolecular distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
+
+Of the pairwise alignment tools, CE, FATCAT, TM-align and DALI, we have found TM-align is the fastest while also providing high-quality pairwise structure alignments. 
+It is for this reason that we use TM-align for RUPEE.
+
+Whereas pairwise structure alignments only depend on the sequence of \ca coordinates, protein structure searches often introduce a further dependence on the sequence order of amino acids.
+This approach often takes the form of clustering proteins based on sequences and pre-calculating results for pairwise alignments among cluster representatives. 
+Then, these pre-calculated results are used for filtering the number of structures used for comparisons against a query protein.
+The exact formula for combining the use of representatives and pre-calculated results varies from system to system.
+However, all systems using this approach share the same disadvantage, an indirect dependence on amino acid sequences. 
+In the absence of a reliance on sequence representatives and pre-calculated results, and without sacrificing accuracy, response times suffer greatly, often taking upwards of an hour for queries to complete.
+
+For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
+Nonetheless, these searches are slow in comparison to the structure searches we compare to in this paper, mTM, SSM, and CATHEDRAL, when pre-calculated results are not used. 
+If given a known protein domain, VAST can return structural neighbors in seconds using pre-calculated results. 
+However, if uploading a PDB file where pre-calculated results are not used, response times for VAST can exceed 30 minutes. 
+Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
+
+DALI also provides a heuristic structure search \cite{Holm2010} of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
+In the case of searching, DALI first identifies matched PDB-90 representatives and then walks a pre-calculated graph of structural similarities to identify further matches in the PDB to gradually build up the set of structures similar to the query structure.
+DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI \cite{Dong2018}.
+
+[Note: add how the need for protein structure prediction is needed extra accuracy. ]
+
+Given the above, there remains a need for a purely geometric protein structure search.
+For the serendipitous exploration of relations between protein structures performed in the trenches, this search should be fast. 
+Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \cite{gkw1000}, this search should be scalable. 
+At a minimum, RUPEE takes a significant step in this direction as will be shown below.
+
+These requirements were satisifed in \cite{Ayoub2019}. However, this is also a need for higher sensitivity / greater accuracy when it comes to protein structure prediciton output and protein design.
 
@@
 
+In addition to using global or semi-global alignment with the Needleman-Wunsch algorithm, for full-length and containment search types respectively, we also apply the same logic to how normalization is used in the TM-align algorithm.
+For the Full-Length searches we normalize by the average length of both structures, for Contained-In searches we normalize by the query structure and for Contains searches we normalize by the matched structure.
+The 3 types of normalization available in TM-align and how they affect searches are discussed in greater detail in the results section of \cite{Ayoub2019}.
+
 The filter sizes of 40000, 8000 and 400 have been chosen based on quality of results and speed. 
@@
 \subsection*{All-aligned mode}
-Since Jaccard similarity is measure of similarity for entire sets, in the context of protein structure search, it is more suitable for full-length searches rather than containment searches.
 
-While Jaccard similarity is a good similarity score for full-length matches, it does not naturally lends itself to containment comparisons. 
-h
+While top-aligned search mode may be sufficient for searching for known protein structures, as was shown in \cite{Ayoub2019} and will also be reinforced below, the need for greater sensitivity arises when searching with structures output from protein structure prediction protocols, where the resultant structure may only have a maximum TM-score of less than 0.50 when compared against all available structures.
+Furthermore, for top-aligned mode, the initial filtering is based on full-length matches using the Jaccard similarities, which is not suitable for containment searches.
+We address both of these concerns by the addition of all-aligned mode.
 
-Since Jaccard similarity is measure of similarity for entire sets, in the context of protein structure search, it is more suitable for full-length searches rather than containment searches.
+The first difference between all-aligned and top-aligned modes is that all-aligned modes skips the min-hashing and LSH step. 
+This has the effect of reducing the scalability of all-aligned mode. 
+However, we have found that with the current sizes of protein structure databases still being less than a million structures, fast alignments estimates can still be performed on the entire collection using effective multithreading and return within a reasonable amount of time, more often less than 10 minutes on structures with 300 or few residues.
 
-Estimates of Jaccard similarity, a measure of similarity between 2 whole sets.  alone is not appropriate for performing containment searches 
-Given two sequences of run position encoded shingle hashes similar to the multiset shown in (\ref{E:rpebag}) but ordered, we perform a Needleman-Wunsh alignment
+[I'm not sure if distinguished between TM-align and NW algorithms above in terms of NW being much faster than TM-align.
+perhaps this can be done in related work].
 

### 2019-08-22 docs/rupee.tex
increment

@@
 
-Determining the structure of a protein is the key to understanding its function [cite]. 
-Current structure determination methods such as X-ray crystallography and nuclear magnetic resonance (NMR) are timing consuming methods. 
-Given the throughput of next gen sequencing methods, physical protein structure determination are unable to keep pace.
-The ability to predict a protein structure from its amino acid sequence would address this problem. 
+Determining the structure of a protein is an important step towards understanding its function.
+Current experimental structure determination methods such as X-ray crystallography and nuclear magnetic resonance (NMR) are resource intensive and timing consuming.
+Given the higher throughput of current sequencing methods, experimental protein structure determination is unable to keep pace.
+Being able to predict a protein structure from its amino acid sequence would address this problem. 
 However, protein structure prediction remains a central unsolved problem in molecular biology.
 
-CASP is a biannual blind competition for protein structure prediction that started year x. 
-Progress has been slow until the success of coevolutionary methods in contact prediction in CASP11 [cite CASP eval paper].
-Additionally, the recent success of Alphabet's AlphaFold at CASP13 using deep learning combined with coevolutionary methods has refocused interest in the problem. 
-While AlphaFold's contribution was significant, the problem remains largely unsolved and more work remains to be done [cite alquarishi].
+CASP is a biannual blind competition for protein structure prediction that began in 1994 \cite{Moult1995}.
+Progress has been slow until the success of coevolutionary methods in contact prediction demonstrated in CASP11 \cite{Moult2016}.
+Now, the recent success of AlphaFold at CASP13 \cite{alq2019} using deep learning combined with coevolutionary methods has refocused interest on the problem. 
+While AlphaFold's performance was remarkable, the problem remains largely unsolved and more work remains to be done \cite{alq2019}.
 
-In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence sequences, clustering, and precalculate results. 
-We compared our results with the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches from a benchmark of known protein domains.
-Additionally, we showed RUPEE on average is able to return results faster than mTM-align and CATHEDRAL.
+In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence on sequences, clustering, and pre-calculated results. 
+We compared our results with the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches on a benchmark of known protein domains.
+Additionally, we showed RUPEE, on average, is able to return results faster than mTM-align and CATHEDRAL.
 
-Since the release of RUPEE, we have observed that the primary usage pattern for RUPEE has been to upload protein structures that have a very low maximum similarity to other structures in the PDB or any of the domain classifications databases.
+Since the release of RUPEE, we have observed that the primary usage pattern for RUPEE has been to upload protein structures that have a very low maximum similarity to other structures in the PDB.
 In most cases, these uploaded protein structures are the output of a protein structure prediction protocol. 
-While in \cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in development of protein structure prediction protocols.
-For instance, besides measuring the similarity of a predicted structure to a target structure, it is also natural to determine what known structure a predicted structure resembles most.
+While in \cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in the development of protein structure prediction methods.
+For instance, besides measuring the similarity of a predicted structure to a target structure in order to evaluate a protein structure prediction method in development, it is also natural to determine what known structure a predicted structure resembles most.
 
+[got here in my second pass]
 Recognizing the need for being able to search on query structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 

### 2019-08-22 docs/rupee.tex
intro

@@
 
-In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence on sequences, clustering, and pre-calculated results. 
+In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence on sequences, clustering, or pre-calculated results. 
 We compared our results with the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches on a benchmark of known protein domains.
@@
 
-Since the release of RUPEE, we have observed that the primary usage pattern for RUPEE has been to upload protein structures that have a very low maximum similarity to other structures in the PDB.
-In most cases, these uploaded protein structures are the output of a protein structure prediction protocol. 
+Since the release of RUPEE, we have observed that the primary usage for RUPEE has been for uploaded protein structures that have a low maximum similarity to other structures in the PDB.
+In most cases, these uploaded protein structures are the output of a protein structure prediction method. 
 While in \cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in the development of protein structure prediction methods.
-For instance, besides measuring the similarity of a predicted structure to a target structure in order to evaluate a protein structure prediction method in development, it is also natural to determine what known structure a predicted structure resembles most.
+For instance, besides measuring the similarity of a predicted structure to a target structure in order to evaluate a protein structure prediction method in development, it is also natural to determine what known structures a predicted structure resembles most.
 
-[got here in my second pass]
-Recognizing the need for being able to search on query structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 
-While top-aligned mode, introduced in \cite{Ayoub2019}, is comparitively good for low similarity searches, the all-aligned mode we introduce below provides a significant improvement over top-aligned mode in that case.
-In this paper, we again compare RUPEE's results mTM-align, SSM, and CATHEDRAL but this time we do so for all-aligned mode and we derive a benchmark from free-modelling predictions in CASP12. 
-Whereas in \cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, in this paper we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction protocols.
+Recognizing the need to search on structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 
+While top-aligned mode, introduced in \cite{Ayoub2019}, is also good for low similarity searches, the all-aligned mode we introduce below is a significant improvement over top-aligned mode in that case.
+
+In this paper, we again compare the results of RUPEE against mTM-align, SSM, and CATHEDRAL, but this time we do so for all-aligned mode.
+Furthermore, we derive a new benchmark for comparisons from protein structure predictions for free-modelling targets in CASP12 available at the CASP web site. 
+Whereas in \cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, here we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction methods.
 
@@
 
-Together, all-aligned mode and containment searches are siginificant additions to RUPEE that increase its utility and further demonstrates the advantage of a purely geomietric protein structure search without dependencies on sequence, precalculated results or clustering.
+Together, all-aligned mode and containment searches are significant additions to RUPEE that increase its utility and further demonstrates the advantage of a purely geometric protein structure search with no dependence on sequences, clustering, or pre-calculated results.
 
@@
 
-We first provide a brief outline of our linear encoding of protein structures described in more detail in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
+We first give a brief outline of our linear encoding of protein structures described in more detail in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
 Then, we describe the types of similarity scores used for the initial filtering in the different search modes, the addition of search types, changes to top-aligned mode, and the addition of all-aligned mode, in that order.

### 2019-08-22 docs/rupee.tex
methods

@@
 
-CASP is a biannual blind competition for protein structure prediction that began in 1994 \cite{Moult1995}.
-Progress has been slow until the success of coevolutionary methods in contact prediction demonstrated in CASP11 \cite{Moult2016}.
-Now, the recent success of AlphaFold at CASP13 \cite{alq2019} using deep learning combined with coevolutionary methods has refocused interest on the problem. 
-While AlphaFold's performance was remarkable, the problem remains largely unsolved and more work remains to be done \cite{alq2019}.
+CASP is a biannual blind competition for protein structure prediction that began in 1994~\cite{Moult1995}.
+Progress has been slow until the success of coevolutionary methods in contact prediction demonstrated in CASP11~\cite{Moult2016}.
+Now, the recent success of AlphaFold at CASP13~\cite{alq2019} using deep learning combined with coevolutionary methods has refocused interest on the problem. 
+While AlphaFold's performance was remarkable, the problem remains largely unsolved and more work remains to be done~\cite{alq2019}.
 
-In \cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence on sequences, clustering, or pre-calculated results. 
-We compared our results with the mTM-align structure search \cite{Dong2018}, the secondary structure matching (SSM) search \cite{Krissinel2004}, and the CATHEDRAL structural scan \cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches on a benchmark of known protein domains.
+In~\cite{Ayoub2019} we introduced RUPEE, a purely geometric protein structure search with no dependence on sequences, clustering, or pre-calculated results. 
+We compared our results with the mTM-align structure search~\cite{Dong2018}, the secondary structure matching (SSM) search~\cite{Krissinel2004}, and the CATHEDRAL structural scan~\cite{Redfern2007}, and found RUPEE is equal to or better than the best available structure searches on a benchmark of known protein domains.
 Additionally, we showed RUPEE, on average, is able to return results faster than mTM-align and CATHEDRAL.
@@
 In most cases, these uploaded protein structures are the output of a protein structure prediction method. 
-While in \cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in the development of protein structure prediction methods.
+While in~\cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in the development of protein structure prediction methods.
 For instance, besides measuring the similarity of a predicted structure to a target structure in order to evaluate a protein structure prediction method in development, it is also natural to determine what known structures a predicted structure resembles most.
@@
 Recognizing the need to search on structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 
-While top-aligned mode, introduced in \cite{Ayoub2019}, is also good for low similarity searches, the all-aligned mode we introduce below is a significant improvement over top-aligned mode in that case.
+While top-aligned mode, introduced in~\cite{Ayoub2019}, is also good for low similarity searches, the all-aligned mode we introduce below is a significant improvement over top-aligned mode in that case.
 
@@
 Furthermore, we derive a new benchmark for comparisons from protein structure predictions for free-modelling targets in CASP12 available at the CASP web site. 
-Whereas in \cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, here we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction methods.
+Whereas in~\cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, here we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction methods.
 
@@
 
-\section*{Related work}
-
-Pairwise alignment involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric. 
-Traditionally, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
-However, the RMSD score does not factor in the distance between unaligned residues nor does it consider the percentage of aligned residues, that is, alignment \emph{coverage}. 
-RMSD scores also have some dependence on the length of the aligned proteins. 
-On the other hand, the TM-score \cite{Zhang2004} takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
-For this reason, TM-score is frequently used in the assessment of protein structure alignments.
-
-Pairwise alignments often favor accuracy over speed because the typical use case of aligning one protein structure to another does not impose tight response time requirements. 
-On the other hand, a protein structure search can involve thousands of comparisons and accuracy is often balanced against speed. 
-In this case, pairwise alignment is still useful for evaluating the results of a search, and this is the approach we take.
-
-For pairwise alignment, Combinatorial Extensions (CE) \cite{Shindyalov1998} and FATCAT \cite{Ye2003} are among the most popular tools, representing rigid and flexible protein alignments, respectively.
-CE performs a rigid alignment in order to minimize RMSD and FATCAT allows for a constrained number of twists in the protein chain in order to find a more flexible alignment before minimizing RMSD.
-
-Besides CE and FATCAT, TM-align \cite{Zhang2005} and DALI \cite{Sander1995} are pairwise alignment tools also in wide use, both offering their own distinct approaches to structure alignment. 
-TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best full-length alignment. 
-DALI compares intramolecular distance matrices between two proteins to find a consistent set of matched submatrices that is used to align the proteins.
-
-Of the pairwise alignment tools, CE, FATCAT, TM-align and DALI, we have found TM-align is the fastest while also providing high-quality pairwise structure alignments. 
-It is for this reason that we use TM-align for RUPEE.
-
-Whereas pairwise structure alignments only depend on the sequence of \ca coordinates, protein structure searches often introduce a further dependence on the sequence order of amino acids.
-This approach often takes the form of clustering proteins based on sequences and pre-calculating results for pairwise alignments among cluster representatives. 
-Then, these pre-calculated results are used for filtering the number of structures used for comparisons against a query protein.
-The exact formula for combining the use of representatives and pre-calculated results varies from system to system.
-However, all systems using this approach share the same disadvantage, an indirect dependence on amino acid sequences. 
-In the absence of a reliance on sequence representatives and pre-calculated results, and without sacrificing accuracy, response times suffer greatly, often taking upwards of an hour for queries to complete.
-
-For protein structure searches, VAST \cite{Gilbrat1996} and the FATCAT server \cite{Ye2004} are among the most popular. 
-Nonetheless, these searches are slow in comparison to the structure searches we compare to in this paper, mTM, SSM, and CATHEDRAL, when pre-calculated results are not used. 
-If given a known protein domain, VAST can return structural neighbors in seconds using pre-calculated results. 
-However, if uploading a PDB file where pre-calculated results are not used, response times for VAST can exceed 30 minutes. 
-Similarly, the FATCAT server, that does not use pre-calculated results, can take over an hour to send results for a search against PDB-90 representatives \cite{Prlic2010}.
-
-DALI also provides a heuristic structure search \cite{Holm2010} of whole chains found in the PDB in addition to a tool for pairwise structure alignments using distance matrices as discussed above. 
-In the case of searching, DALI first identifies matched PDB-90 representatives and then walks a pre-calculated graph of structural similarities to identify further matches in the PDB to gradually build up the set of structures similar to the query structure.
-DALI is slow in comparison to SSM, and mTM has shown better quality results than DALI \cite{Dong2018}.
-
-[Note: add how the need for protein structure prediction is needed extra accuracy. ]
-
-Given the above, there remains a need for a purely geometric protein structure search.
-For the serendipitous exploration of relations between protein structures performed in the trenches, this search should be fast. 
-Moreover, with a $~10\%$ yearly growth rate of solved structures deposited in the PDB \cite{gkw1000}, this search should be scalable. 
-At a minimum, RUPEE takes a significant step in this direction as will be shown below.
-
-These requirements were satisifed in \cite{Ayoub2019}. However, this is also a need for higher sensitivity / greater accuracy when it comes to protein structure prediciton output and protein design.
-
 \section*{Methods}
 
-[NOTE: this assumes we have introduced top-aligned mode and all-aligned mode in the introduction]
-
-We first give a brief outline of our linear encoding of protein structures described in more detail in \cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
-Then, we describe the types of similarity scores used for the initial filtering in the different search modes, the addition of search types, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
+We first give a brief outline of our linear encoding of protein structures described in more detail in~\cite{Ayoub2019}, which still remains at the core of the RUPEE protein structure search. 
+Then, we describe the types of similarity scores and pairwise alignments used by RUPEE, changes to top-aligned mode, and the addition of all-aligned mode, in that order.
 
@@
 
-In \cite{Ayoub2019}, we introduced a linear encoding of protein structures.
+In~\cite{Ayoub2019}, we introduced a linear encoding of protein structures.
 For each pair of torsion angles combined with their secondary structure assignment, we assign an integer we refer to as a residue descriptor.
@@
 Next, we derive a multiset of overlapping 3-grams of residue descriptors. 
-This representation is often referred to as shingling and was developed in \cite{Broder1997a}. 
+This representation is often referred to as shingling and was developed in~\cite{Broder1997a}. 
 The overlap between shingles ensures some of the order information within the original sequence is preserved in the multiset.
@@
 
-\subsection*{Similarity scores}
+\subsection*{Similarity scores and alignments}
 
-In one case, RUPEE uses the multiset-of-integers representation of protein structures as shown in (\ref{E:rpebag}), and in another case RUPEE regards this multiset as an ordered list of integers.  
-We describe the context in which these cases occur in subsequent sections below, but first, we discuss the similarity scores that RUPEE uses for each representation.
+For both top-aligned mode and all-aligned mode, the final step in a structure search is to run pairwise structure alignments between the query structure and each matched result and return them in sorted order.
+However, before this final step, a few different filtering methods are used to pick the candidates for pairwise structure alignments.
+Here, we describe the filtering methods in order of increasing complexity and end with a description of what alignment tool RUPEE uses for pairwise structure alignments.
 
-When representing each protein structure using a multiset of integers as shown in (\ref{E:rpebag}), full-length similarity for a candidate pair of structures $a$ and $b$ is defined using the Jaccard similarity \cite{Levan1971} for multisets,
+When representing each protein structure using a multiset of integers as shown in (\ref{E:rpebag}), full-length similarity for a candidate pair of structures $a$ and $b$ is defined using the Jaccard similarity~\cite{Levan1971} for multisets,
 \begin{align}
@@
 where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively. 
-In words, the Jaccard similarity is the proportion of matched shingles to the total number of shingles.
+Determining the Jaccard similarity between two structures represented as multisets is very fast but is too coarse-grained a comparison to be of any greater use than as a first-pass filtering method.
 
-When regarding the multiset in (\ref{E:rpebag}) as an ordered list of integers, we assign a pair of protein structures a full-length similarity score using a simplified Needleman-Wunsch \cite{Needleman1970} dynamic programming algorithm where mismatches and gaps are penalized -1 points and matches are awarded +1 points.
+When regarding the multiset in (\ref{E:rpebag}) as an ordered list of integers, we assign a pair of protein structures a full-length similarity score using a simplified Needleman-Wunsch~\cite{Needleman1970} sequence alignment algorithm where mismatches and gaps are penalized -1 points and matches are awarded +1 points.
+For containment searches, depending on whether or not the search type is Contained-In or Contains, one of the sides of the dynamic programming matrix is not penalized for the opening gap and end gap.
+This is often referred to as semi-global sequence alignment and was developed in~\cite{Brudno2003}. 
+The relative order of scores for protein structure comparisons using this method is more accurate than the rough similarity estimates provided by the Jaccard similarity and are still very fast to perform.
+However, they are still only suitable for coarse-grained filtering.
 
-\subsection*{Search types}
+Pairwise structure alignment, the most accurate method for comparing protein structures, involves finding a set of spatial rotations and translations for two protein structures that minimizes a distance metric.
+Traditionally, the root mean squared deviation (RMSD) between \cas of aligned residues is minimized.
+However, the RMSD score does not factor in the distance between unaligned residues nor does it consider the percentage of aligned residues, that is, alignment \emph{coverage}. 
+RMSD scores also have some dependence on the length of the aligned proteins. 
+On the other hand, the TM-score~\cite{Zhang2004} takes all residues into account and normalizes for both coverage and length of the aligned proteins. 
+For this reason, TM-score is frequently used in scoring protein structure alignments and accordingly, we use it for sorting the final results provided by RUPEE.
 
-Originally, the RUPEE protein structure search focused on full-length matches. 
-If you wanted to search for structures similar to a domain, you could search one of the protein domain classification databases such as SCOPe, CATH, or ECOD.
-On the other hand, if you wanted to search for structures similar to a whole chain, you could search whole chains from the PDB. 
-While the ability of RUPEE to search multiple databases for any given structure is flexible, adding the ability to execute containment searches extends this flexibility.
-Therefore, RUPEE now supports explicit search types for \emph{Contained-In} and \emph{Contains} searches in addition to the \emph{Full-Length} search type.
+RUPEE uses TM-align~\cite{Zhang2005} for performing pairwise structure alignments.
+TM-align uses a rotation matrix designed to maximize the TM-score rather than minimizing the RMSD along with dynamic programming to find the best alignment. 
+In addition to using global or semi-global sequence alignment with the Needleman-Wunsch algorithm, for full-length and containment search types respectively, we apply the same logic to how normalization is used in the TM-align algorithm in order for it to be compatible with the initial filtering methods.
+For the Full-Length searches we normalize by the average length of both structures, for Contained-In searches we normalize by the query structure and for Contains searches we normalize by the matched structure.
+The 3 types of normalization available in TM-align and how they affect searches are discussed in greater detail in the results section of~\cite{Ayoub2019}.
 
-In the case where we regard the multiset in (\ref{E:rpebag}) as an ordered list of integers, we score containment using the same simplified Needleman-Wunsch \cite{Needleman1970} algorithm we use for full-length similarity with one small change.
-For containment searches, depending on whether or not the search type is Contained-In or Contains, one of the sides of the dynamic programming matrix is not penalized for the opening gap and end gap.
-This is often referred to as semi-global alignment and was developed in \cite{Brudno2003}. 
-As it turns out, semi-global alignment is a natural fit for containment comparisons as long as the directionality of containment is explicit.
+RUPEE makes use of the TM-align algorithm in a few different context during a search depending on the search mode and type. 
+These differents usages of TM-align will be discussed below as they occur. 
+ed in more detail below in the context in which it is used.
+
+[got here]
 
@@
 
-For top-aligned mode, RUPEE uses min-hashing \cite{Broder1998} and locality sensitive hashing (LSH) \cite{Indyk1998} as described in detail in our previous work \cite{Ayoub2019} to quickly estimate the Jaccard similarity of a query protein against all available structures in the searched database.
+For top-aligned mode, RUPEE uses min-hashing~\cite{Broder1998} and locality sensitive hashing (LSH)~\cite{Indyk1998} as described in detail in our previous work~\cite{Ayoub2019} to quickly estimate the Jaccard similarity of a query protein against all available structures in the searched database.
 Then, the top scoring 40000 protein structures are obtained based on the Jaccard similarity estimates to complete the initial filtering.
@@
 For the Full-Length searches we normalize by the average length of both structures, for Contained-In searches we normalize by the query structure and for Contains searches we normalize by the matched structure.
-The 3 types of normalization available in TM-align and how they affect searches are discussed in greater detail in the results section of \cite{Ayoub2019}.
+The 3 types of normalization available in TM-align and how they affect searches are discussed in greater detail in the results section of~\cite{Ayoub2019}.
 
@@
 
-While top-aligned search mode may be sufficient for searching for known protein structures, as was shown in \cite{Ayoub2019} and will also be reinforced below, the need for greater sensitivity arises when searching with structures output from protein structure prediction protocols, where the resultant structure may only have a maximum TM-score of less than 0.50 when compared against all available structures.
+While top-aligned search mode may be sufficient for searching for known protein structures, as was shown in~\cite{Ayoub2019} and will also be reinforced below, the need for greater sensitivity arises when searching with structures output from protein structure prediction protocols, where the resultant structure may only have a maximum TM-score of less than 0.50 when compared against all available structures.
 Furthermore, for top-aligned mode, the initial filtering is based on full-length matches using the Jaccard similarities, which is not suitable for containment searches.

### 2019-08-23 docs/rupee.tex
edits

@@
 Determining the structure of a protein is an important step towards understanding its function.
-Current experimental structure determination methods such as X-ray crystallography and nuclear magnetic resonance (NMR) are resource intensive and timing consuming.
+Current experimental methods for protein structure determination such as X-ray crystallography and nuclear magnetic resonance (NMR) are resource intensive and timing consuming.
 Given the higher throughput of current sequencing methods, experimental protein structure determination is unable to keep pace.
@@
 
-Since the release of RUPEE, we have observed that the primary usage for RUPEE has been for uploaded protein structures that have a low maximum similarity to other structures in the PDB.
+Since the release of RUPEE, we have observed that the primary usage for RUPEE has been for uploaded protein structures that have a low maximum similarity to other structures in the protein data bank (PDB).
 In most cases, these uploaded protein structures are the output of a protein structure prediction method. 
 While in~\cite{Ayoub2019} we recognized the desirability of a purely geometric protein structure search, we did not anticipate the utility of such a search to aid in the development of protein structure prediction methods.
-For instance, besides measuring the similarity of a predicted structure to a target structure in order to evaluate a protein structure prediction method in development, it is also natural to determine what known structures a predicted structure resembles most.
+For instance, in developing and evaluating a protein structure method, a person may want to identify the known structures a predicted structure resembles most, in addition to measuring the similarity of a predicted structure to a target structure.
 
 Recognizing the need to search on structures with low maximum similarity to known structures, we have added an additional search mode to RUPEE with increased sensitivity. 
-While top-aligned mode, introduced in~\cite{Ayoub2019}, is also good for low similarity searches, the all-aligned mode we introduce below is a significant improvement over top-aligned mode in that case.
+While RUPEE top-aligned mode, introduced in~\cite{Ayoub2019}, is also good for low similarity searches, the RUPEE all-aligned mode we introduce below is a significant improvement over top-aligned mode in that case.
 
 In this paper, we again compare the results of RUPEE against mTM-align, SSM, and CATHEDRAL, but this time we do so for all-aligned mode.
-Furthermore, we derive a new benchmark for comparisons from protein structure predictions for free-modelling targets in CASP12 available at the CASP web site. 
+Furthermore, for comparisons, we use a new benchmark derived from protein structure predictions of free-modelling targets in CASP12 available at the CASP web site. 
 Whereas in~\cite{Ayoub2019} we showed that RUPEE is equal or better than those we compared to for a benchmark of known protein structures, here we show that RUPEE, in all-aligned mode, is clearly better than those we compare to using a benchmark drawn from the structures output by protein structure prediction methods.
@@
 For each pair of torsion angles combined with their secondary structure assignment, we assign an integer we refer to as a residue descriptor.
-For instance, a $\beta$-turn-$\beta$ motif may be represented as a sequence of residue descriptors, similar to that shown below. 
+For example, Fig XXX shows a typical $\beta$-turn-$\beta$ motif annotated with the residue descriptors corresponding to the list shown below.
 \begin{gather}\label{E:descrseq} 
@@
 
-For both top-aligned mode and all-aligned mode, the final step in a structure search is to run pairwise structure alignments between the query structure and each matched result and return them in sorted order.
-However, before this final step, a few different filtering methods are used to pick the candidates for pairwise structure alignments.
-Here, we describe the filtering methods in order of increasing complexity and end with a description of what alignment tool RUPEE uses for pairwise structure alignments.
+The final step in both RUPEE top-aligned mode and all-aligned mode is to run pairwise structure alignments between the query structure and each matched result and return them in sorted order. 
+However, before this final step, top-aligned mode and all-aligned mode use a different mix of filtering methods to pick the candidates for pairwise structure alignments. 
+Here, we describe the similarity scores and alignments used in the filtering methods in order of increasing complexity and end with a description of the alignment tool RUPEE uses for pairwise structure alignments.
 
-When representing each protein structure using a multiset of integers as shown in (\ref{E:rpebag}), full-length similarity for a candidate pair of structures $a$ and $b$ is defined using the Jaccard similarity~\cite{Levan1971} for multisets,
+When representing each protein structure using a multiset of integers as shown in (\ref{E:rpebag}), full-length similarity for a candidate pair of structures $a$ and $b$ is defined using the Jaccard similarity for multisets~\cite{Levan1971},
 \begin{align}
@@
 where $i$ ranges over all possible shingle hashes $s_i$ and $a_i$ and $b_i$ give the counts of shingle hash $s_i$ in structures $a$ and $b$, respectively. 
-Determining the Jaccard similarity between two structures represented as multisets is very fast but is too coarse-grained a comparison to be of any greater use than as a first-pass filtering method.
+Determining the Jaccard similarity for multisets between two structures is very fast but is too rough of a comparison to be of any greater use than as a first-pass filtering method.
 
@@
 The relative order of scores for protein structure comparisons using this method is more accurate than the rough similarity estimates provided by the Jaccard similarity and are still very fast to perform.
-However, they are still only suitable for coarse-grained filtering.
+However, while these similarity estimates are more precise than the Jaccard similarity for multisets, they are still only suitable for a rough filtering.
 
@@
 RUPEE makes use of the TM-align algorithm in a few different context during a search depending on the search mode and type. 
-These differents usages of TM-align will be discussed below as they occur. 
-ed in more detail below in the context in which it is used.
+These different usages of TM-align will be discussed below in the context in which they occur.
 

### 2020-07-11 eval/figures/archive/combined_precision.R
directory reorg - grouping all eval stuff

@@ -1,0 +1,67 @@
+
+library(grid)
+library(gridExtra)
+
+source('precision.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = length(list(...)),
+           nrow = 1,
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+mtm_plot <- get_precision_plot(
+        'vs. mTM (scop_d360)',
+        'precision_mtm.txt',
+        c('RUPEE TM-Score', 'RUPEE RMSD', 'RUPEE Fast', 'mTM'), 
+        c(1, 100),
+        c(1, seq(10, 100, by = 10)),
+        'fold precision'
+)
+ssm_plot <- get_precision_plot(
+        'vs. SSM (scop_d62)',
+        'precision_ssm.txt',
+        c('RUPEE TM-Score', 'RUPEE RMSD', 'RUPEE Fast', 'SSM'), 
+        c(1, 50),
+        c(1, seq(5, 50, by = 5)),
+        'fold precision'
+)
+cathedral_plot <- get_precision_plot(
+        'vs. CATHEDRAL (cath_d99)',
+        'precision_cathedral.txt',
+        c('RUPEE TM-Score', 'RUPEE RMSD', 'RUPEE Fast', 'CATHEDRAL'), 
+        c(1, 100),
+        c(1, seq(10, 100, by = 10)),
+        'topology precision'
+)
+
[…]

### 2020-07-11 eval/figures/archive/combined_response.R

@@ -1,0 +1,64 @@
+
+library(grid)
+library(gridExtra)
+
+source('response.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = length(list(...)),
+           nrow = 1,
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(list(plots[[2]], plots[[3]]), function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol - 1, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+dummy_plot <- get_timing_plot(
+        'dummy timing',
+        'response_dummy.txt',
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'mTM', 'SSM','CATHEDRAL'), 
+        c('#e41a1c', '#4daf4a', '#984ea3', '#ff7f00', '#a65628'),
+        TRUE
+)
+scop_plot <- get_timing_plot(
+        'scop_d62 timing',
+        'response_scop_d62.txt',
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'mTM', 'SSM'), 
+        c('#e41a1c', '#4daf4a', '#984ea3', '#ff7f00'),
+        TRUE
+)
+cath_plot <- get_timing_plot(
+        'cath_d99 timing',
+        'response_cath_d99.txt',
+        c('RUPEE Top-Aligned', 'RUPEE Fast', 'CATHEDRAL'), 
+        c('#e41a1c', '#4daf4a', '#a65628'),
+        FALSE
+)
+
+combined <- grid_arrange_shared_legend(dummy_plot, scop_plot, cath_plot)
+
+ggsave('combined_response.eps', plot = combined, width = 7, height = 2.5)
+

### 2020-07-11 eval/figures/archive/response.R

@@ -1,0 +1,86 @@
+
+library(ggplot2)
+library(plyr)
+
+# clear environment
+rm(list = ls())
+
+get_timing_plot <- function(p_title, p_file, p_levels, p_colors, p_y_axis) {
+
+    # read in data file
+    df <- read.csv(p_file)
+
+    # reorder factor levels
+    df$app <- factor(df$app, levels = p_levels)
+
+    # *** plot
+
+    plot <- 
+
+        ggplot(df, aes(gram_count, timing, group = app, color = app)) +
+            
+        # geoms
+        geom_point(
+            size = rel(0.5)
+        ) + 
+        geom_smooth(     
+            size = rel(0.5),
+            show.legend = FALSE
+        ) + 
+
+        # scales
+        scale_color_manual(
+            values = p_colors,
+            labels = p_levels
+        ) + 
+        scale_y_continuous(
+            trans = "log10",
+            limits = c(1,10000)
+        ) + 
+    
+        # guides
+        guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
+
+        # axis labels
+        labs(
+             x = 'residue count', 
+             y = 'response time (seconds)'
+        ) + 
+        
+        # title
+        ggtitle(p_title)
+
+    # *** theme
+    
+    theme <-  
+
+        # default theme 
+        theme_bw() +
+
+        # default override
+        theme(
+            plot.title = element_text(size = 8, hjust = 0.5),
+            plot.margin = margin(5,15,0,5), 
+
+            panel.grid = element_blank(),
+            panel.spacing = unit(4,'mm'),
+
+            axis.text = element_text(size = 7), 
+            axis.title = element_text(size = 8), 
+            
+            legend.text = element_text(size = 7),
+            legend.title = element_blank(), 
+            legend.position = 'bottom',
+            legend.direction = 'horizontal',
+            legend.spacing = unit(0,'mm')
+        ) 
+
+    if (p_y_axis) {
+        theme <- theme + theme(axis.title.y = element_text(size = 8))
+    }
+    else {
+        theme <- theme + theme(axis.title.y = element_blank())
+    }
+
+    plot + theme
+}

### 2020-07-11 eval/figures/archive/scoring.R

@@ -1,0 +1,91 @@
+
+library(ggplot2)
+library(plyr)
+
+# clear environment
+rm(list = ls())
+
+get_scoring_plot <- function(p_title, p_file, p_levels, p_limits, p_breaks) {
+
+    # read in data files
+    df <- read.csv(p_file)
+    refs <- read.csv('scoring_refs.txt')
+
+    # reorder factor levels 
+    df$app <- factor(df$app, levels = p_levels)
+
+    # *** plot
+
+    plot <- 
+        
+        ggplot(df, aes(n, avg_cume_score, group = app, color = app, linetype = app)) +
+        
+        # geoms
+        geom_line(
+            size = rel(0.5)
+        ) + 
+
+        # scales        
+        scale_color_manual(
+            values = c("#e41a1c","#377eb8"),
+            labels = c("RUPEE All-Aligned","Compared To")
+        ) + 
+        scale_linetype_manual(
+            values = c("solid","dashed"),
+            labels = c("RUPEE All-Aligned","Compared To")
+        ) + 
+        scale_x_continuous(
+            limits = p_limits,
+            breaks = p_breaks
+        ) + 
+        scale_y_continuous(
+            limits = c(0.25,0.75)
+        ) + 
+
+        # guides
+        guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
+
+        # axis labels
+        labs(
+             x = 'rank', 
+             y = 'value'
+        ) +
+
+        # title
+        ggtitle(p_title)
+
+    # *** theme
+    
+    theme <-  
+
+        # default theme 
+        theme_bw() +
+
+        # default override
+        theme(
+            plot.title = element_text(size = 8, hjust = 0.5),
+            plot.margin = margin(5,15,0,0), 
+
+            panel.grid = element_blank(),
+            panel.spacing = unit(4,'mm'),
+            
+            axis.text = element_text(size = 7), 
+            axis.title = element_blank(),
+            
+            legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
+            legend.title = element_blank(), 
+            legend.position = 'bottom',
+            legend.direction = 'horizontal',
+            legend.spacing = unit(0,'mm')
+
+#            strip.background = element_blank(),
+#            strip.placement = 'outside'
+        ) 
+
+    theme <- theme + theme(strip.text = element_text(size = 8))
+
+    plot + theme
+}
+
+
+

### 2020-07-11 eval/figures/combined_scoring_mtm.R

@@ -1,0 +1,63 @@
+
+library(grid)
+library(gridExtra)
+
+source('scoring.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = 2, 
+           nrow = 1, 
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+plot1 <- get_scoring_plot(
+        'mTM-align',
+        'vs: mTM-align\nbenchmark: casp_mtm_d246\nRUPEE search type: Contained-In',
+        'TM-score (q)',
+        'scoring_mtm_ci.txt', # _rmsd, _ci
+        c('RUPEE All-Aligned','RUPEE Top-Aligned','mTM'), 
+        c(1, 100),
+        c(1,10,20,30,40,50,60,70,80,90,100),
+        c(0.10, 0.65)
+)
+plot2 <- get_scoring_plot(
+        'mTM-align',
+        'vs: mTM-align\nbenchmark: casp_mtm_d246\nRUPEE search type: RMSD',
+        'RMSD',
+        'scoring_mtm_rmsd.txt', # _rmsd, _ci
+        c('RUPEE All-Aligned','RUPEE Top-Aligned','mTM'), 
+        c(1, 10),
+        c(2,4,6,8,10),
+        c(0, 5)
+)
+
+combined <- grid_arrange_shared_legend(plot1, plot2)
+
+ggsave('combined_scoring_mtm.eps', plot = combined, width = 5.2, height = 2.4, dpi = 300)
+

### 2020-07-11 eval/figures/combined_scoring_rupee.R

@@ -1,0 +1,59 @@
+
+library(grid)
+library(gridExtra)
+
+source('scoring_rupee.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = 2, 
+           nrow = 1, 
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+plot1 <- get_scoring_plot(
+        'All vs. Top\nbenchmark: scop_d360',
+        'scoring_rupee_scop_d360.txt',
+        c('RUPEE All-Aligned','RUPEE Top-Aligned'),
+        c(1, 100),
+        c(1,10,20,30,40,50,60,70,80,90,100),
+        c(0.85, 1.0)
+)
+plot2 <- get_scoring_plot(
+        'All vs. Top\nbenchmark: casp_d250',
+        'scoring_rupee_casp_d250.txt', 
+        c('RUPEE All-Aligned','RUPEE Top-Aligned'),
+        c(1, 100),
+        c(1,10,20,30,40,50,60,70,80,90,100),
+        c(0.4, 0.55)
+)
+
+combined <- grid_arrange_shared_legend(plot1, plot2)
+
+ggsave('combined_scoring_rupee.eps', plot = combined, width = 5.2, height = 2.4, dpi = 300)
+

### 2020-07-11 eval/figures/combined_scoring_vast.R

@@ -1,0 +1,63 @@
+
+library(grid)
+library(gridExtra)
+
+source('scoring.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = 2, 
+           nrow = 1, 
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+plot1 <- get_scoring_plot(
+        'VAST',
+        'vs: VAST\nbenchmark: casp_vast_d199\nRUPEE search type: Full-Length\nVAST search type: VAST-score', 
+        'TM-score (avg)',
+        'scoring_vast_fl.txt', # _ce, _fatcat, _fl
+        c('RUPEE All-Aligned','RUPEE Top-Aligned','VAST'), 
+        c(1, 100),
+        c(1,10,20,30,40,50,60,70,80,90,100),
+        c(0.3, 0.6)
+)
+plot2 <- get_scoring_plot(
+        'VAST',
+        'vs: VAST\nbenchmark: casp_vast_d199\nRUPEE search type: RMSD\nVAST search type: RMSD', 
+        'RMSD',
+        'scoring_vast_ce.txt', # _ce, _fatcat, _fl
+        c('RUPEE All-Aligned','RUPEE Top-Aligned','VAST'), 
+        c(1, 100),
+        c(1,10,20,30,40,50,60,70,80,90,100),
+        c(0, 5) 
+)
+
+combined <- grid_arrange_shared_legend(plot1, plot2)
+
+ggsave('combined_scoring_vast.eps', plot = combined, width = 5.2, height = 2.4, dpi = 300)
+

### 2020-07-11 eval/figures/ramachandran.R

@@ -1,0 +1,79 @@
+
+library(ggplot2)
+library(plyr)
+
+get_ramachandran_plot <- function() {
+
+# clear environment
+rm(list = ls())
+
+# read in data file
+df <- read.csv('torsion.txt')
+
+# map values
+df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
+
+# reorder factor levels
+df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
+
+# color scale
+color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
+
+ramachandran_plot <- ggplot(df, aes(phi, psi, color = sse)) +
+    
+    # geoms
+    geom_point(
+        size = rel(0.01)
+    ) + 
+    
+    # scales
+    scale_x_continuous(
+        limits = c(-180,180),
+        expand = c(0,0),
+        breaks = c(-180,-90,0,90,180),
+        labels = c('-180\u00B0','-90\u00B0','0\u00B0','90\u00B0','180\u00B0')
+    ) + 
+    scale_y_continuous(
+        limits = c(-180,180),
+        expand = c(0,0),
+        breaks = c(-180,-90,0,90,180),
+        labels = c('-180\u00B0','-90\u00B0','0\u00B0','90\u00B0','180\u00B0')
+    ) + 
+    scale_color_manual(NULL, values = color_scale) + 
+    
+    # guides
+    guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
+
+    # coordinates
+    coord_fixed(
+       ratio = 1
+    ) +
+
+    # axis labels
+    labs(
+         x = expression(phi), 
+         y = expression(psi)
+    ) + 
+
+    # default theme 
+    theme_bw() +
+
+    # default override
+    theme(
+        plot.title = element_blank(), 
+        plot.margin = margin(5,0,0,0), 
+       
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_line(size = rel(0.2), color = 'grey50'),
+
+        axis.text = element_text(size = 7), 
+        axis.title = element_text(size = 8),
+        
+        legend.title = element_blank(), 
+        legend.text = element_text(size = 7),
+        legend.position = 'bottom',
+        legend.margin = margin(0,0,0,0),
+        legend.direction = 'horizontal'
+    )
+}
+

### 2020-07-11 eval/figures/regions.R

@@ -1,0 +1,115 @@
+
+library(ggplot2)
+library(plyr)
+
+# clear environment
+rm(list = ls())
+
+# read in data files
+df <- read.csv('torsion.txt')
+lines <- read.csv('region_lines.txt')
+annotes <- read.csv('region_annotes.txt')
+
+# map values
+df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
+
+# subset data
+df <- subset(df, df$sse == 'Helix' | df$sse == 'Strand' | df$sse == 'Bend/Coil')
+
+# reorder factor levels
+df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
+
+# wrap and translate torsion angles
+df$phi <- ifelse(df$phi < 0, df$phi + 360, df$phi)
+df$phi <- df$phi + 200
+
+# color scale
+color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
+
+ggplot(df, aes(phi, psi, color = sse)) +
+    
+    # geoms
+    geom_point(
+        size = rel(0.01)
+    ) + 
+    geom_vline(
+        xintercept = seq(200, 560, by = 90), 
+        colour = 'grey50', 
+        size = rel(0.2)
+    ) +
+    geom_hline(
+        yintercept = seq(-180, 180, by = 30), 
+        colour = 'grey50', 
+        size = rel(0.2)
+    ) +
+    geom_segment(
+        data = lines,
+        size = rel(0.4),
+        lineend = 'square',
+        aes(x, y, xend = xend, yend = yend),
+        inherit.aes = FALSE
+    ) + 
+    geom_text(
+        data = annotes, 
+        size = 3, 
+        color = 'black',
+        aes(x = phi, y = psi, label = label)
+    ) +
+    
+    # scales
+    scale_x_continuous(
+        limits = c(0,560),
+        expand = c(0,0),
+        breaks = c(200,290,380,470,560),
+        labels = c('0\u00B0','90\u00B0','\u00B1180\u00B0','-90\u00B0','0\u00B0')
+    ) + 
+    scale_y_continuous(
+        limits = c(-180,180),
+        expand = c(0,0),
+        breaks = c(-150,-120,-90,-60,-30,0,30,60,90,120,150,180),
[…]

### 2020-07-11 eval/figures/scoring.R

@@ -1,0 +1,83 @@
+
+library(ggplot2)
+library(plyr)
+
+# clear environment
+rm(list = ls())
+
+get_scoring_plot <- function(p_comp_to, p_title, p_ylab, p_file, p_levels, p_xlimits, p_xbreaks, p_ylimits) {
+
+    # read in data files
+    df <- read.csv(p_file)
+
+    # reorder factor levels 
+    df$app <- factor(df$app, levels = p_levels)
+
+    # *** plot
+
+    plot <- 
+        
+        ggplot(df, aes(n, avg_cume_score, group = app, color = app, linetype = app)) +
+        
+        # geoms
+        geom_line(
+            size = rel(0.5)
+        ) + 
+
+        # scales        
+        scale_color_manual(
+            values = c("#e41a1c","#377eb8","#4daf4a"),
+            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned", p_comp_to)
+        ) + 
+        scale_linetype_manual(
+            values = c("solid","dashed","dotted"),
+            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned", p_comp_to)
+        ) + 
+        scale_x_continuous(
+            limits = p_xlimits,
+            breaks = p_xbreaks
+        ) + 
+        scale_y_continuous(
+            limits = p_ylimits
+        ) + 
+
+        # guides
+        guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
+
+        # axis label
+        ylab(p_ylab) + 
+
+        # title
+        ggtitle(p_title)
+
+    # *** theme
+    
+    theme <-  
+
+        # default theme 
+        theme_bw() +
+
+        # default override
+        theme(
+            plot.title = element_text(size = 7),
+            plot.margin = margin(5,15,0,0), 
+
+            panel.grid = element_blank(),
+            panel.spacing = unit(4,'mm'),
+            
+            axis.text = element_text(size = 7), 
+            axis.title.x = element_blank(), 
+            axis.title.y = element_text(size = 7),
+            
+            legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
+            legend.title = element_blank(), 
+            legend.position = 'bottom',
+            legend.direction = 'horizontal',
+            legend.spacing = unit(0,'mm')
+        ) 
+
+    plot + theme
+}
+
+
+

### 2020-07-11 eval/figures/scoring_rupee.R

@@ -1,0 +1,83 @@
+
+library(ggplot2)
+library(plyr)
+
+# clear environment
+rm(list = ls())
+
+get_scoring_plot <- function(p_title, p_file, p_levels, p_xlimits, p_xbreaks, p_ylimits) {
+
+    # read in data files
+    df <- read.csv(p_file)
+
+    # reorder factor levels 
+    df$app <- factor(df$app, levels = p_levels)
+
+    # *** plot
+
+    plot <- 
+        
+        ggplot(df, aes(n, avg_cume_score, group = app, color = app, linetype = app)) +
+        
+        # geoms
+        geom_line(
+            size = rel(0.5)
+        ) + 
+
+        # scales        
+        scale_color_manual(
+            values = c("#e41a1c","#377eb8"),
+            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned")
+        ) + 
+        scale_linetype_manual(
+            values = c("solid","dashed"),
+            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned")
+        ) + 
+        scale_x_continuous(
+            limits = p_xlimits,
+            breaks = p_xbreaks
+        ) + 
+        scale_y_continuous(
+            limits = p_ylimits
+        ) + 
+
+        # guides
+        guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
+
+        # axis label
+        ylab('TM-score (avg)') + 
+
+        # title
+        ggtitle(p_title)
+
+    # *** theme
+    
+    theme <-  
+
+        # default theme 
+        theme_bw() +
+
+        # default override
+        theme(
+            plot.title = element_text(size = 7),
+            plot.margin = margin(5,15,0,0), 
+
+            panel.grid = element_blank(),
+            panel.spacing = unit(4,'mm'),
+            
+            axis.text = element_text(size = 7), 
+            axis.title.x = element_blank(), 
+            axis.title.y = element_text(size = 7),
+            
+            legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
+            legend.title = element_blank(), 
+            legend.position = 'bottom',
+            legend.direction = 'horizontal',
+            legend.spacing = unit(0,'mm')
+        ) 
+
+    plot + theme
+}
+
+
+

### 2020-07-11 eval/figures/torsion.R

@@ -1,0 +1,95 @@
+
+library(ggplot2)
+library(plyr)
+
+get_torsion_plot <- function () {
+
+# clear environment
+rm(list = ls())
+
+# read in data files
+df <- read.csv('torsion.txt')
+
+# map values
+df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
+
+# reorder factor levels
+df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
+
+# color scale
+color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
+
+# wrap and translate torsion angles
+df$phi <- ifelse(df$phi < 0, df$phi + 360, df$phi)
+df$phi <- df$phi + 200
+
+torsion_plot <- ggplot(df, aes(phi, psi, color = sse)) +
+    
+    # geoms
+    geom_point(
+        size = rel(0.01)
+    ) + 
+    geom_vline(
+        xintercept = seq(200, 560, by = 90), 
+        colour = 'grey50', 
+        size = rel(0.2)
+    ) +
+    geom_hline(
+        yintercept = seq(-180, 180, by = 30), 
+        colour = 'grey50', 
+        size = rel(0.2)
+    ) +
+    
+    # scales
+    scale_x_continuous(
+        limits = c(0,560),
+        expand = c(0,0),
+        breaks = c(200,290,380,470,560),
+        labels = c('0\u00B0','90\u00B0','\u00B1180\u00B0','-90\u00B0','0\u00B0')
+    ) + 
+    scale_y_continuous(
+        limits = c(-180,180),
+        expand = c(0,0),
+        breaks = c(-150,-120,-90,-60,-30,0,30,60,90,120,150,180),
+        labels = c('-150\u00B0','-120\u00B0','-90\u00B0','-60\u00B0','-30\u00B0','0\u00B0','30\u00B0','60\u00B0','90\u00B0','120\u00B0','150\u00B0','\u00B1180\u00B0')
+    ) + 
+    scale_color_manual(NULL, values = color_scale) + 
+    
+    # guides
+    guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
+
+    # coordinates 
+    coord_polar(
+       theta = 'y',
+       direction = -1
+    ) +
+
+    # axis labels
[…]

### 2020-07-11 eval/results/cathedral/cat_results.sh

@@ -1,0 +1,16 @@
+#! /bin/bash
+
+bm=$1
+ver=$2
+dir=${bm}_${ver}
+
+for id in $(find ${dir} -name '*.txt' -printf '%f\n'); do
+    tail ${dir}/${id} -n+8 | awk -v ver=${ver} -v id=${id%.txt} \
+        'BEGIN { 
+            FS = "[ \n]+"; 
+            RS = "Show related domains\n"; 
+            OFS = "," 
+        } 
+        { print ver, NR, id, $1, $4, $5 }'
+done;
+

### 2020-07-11 eval/results/rupee/casp.sh

@@ -1,0 +1,10 @@
+#! /bin/bash
+
+# this file needs to be edited for each type of benchmark
+
+bm=$1
+ver=$2
+id=$3
+
+java -jar ../../rupee-mgr/target/rupee-mgr-0.0.1-SNAPSHOT-jar-with-dependencies.jar -s UPLOAD,CHAIN,../../data/casp/eu_preds/${id}.pdb,400,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,ALL_ALIGNED,FULL_LENGTH > ./${bm}_${ver}/${id}.txt
+

### 2020-07-11 eval/results/rupee/casp_run.sh

@@ -1,0 +1,13 @@
+#! /bin/bash
+
+bm=$1
+ver=$2
+
+# delete output directory if it exist
+[ -d ./${bm}_${ver} ] && rm -r ${bm}_${ver}
+
+# create output directory
+mkdir ./${bm}_${ver}
+
+cut -d, -f2 ../benchmarks/${bm}.txt | xargs -L1 ./casp.sh ${bm} ${ver}
+

### 2020-07-11 eval/results/rupee/rupee.sh

@@ -1,0 +1,9 @@
+#! /bin/bash
+
+# this file needs to be edited for each type of benchmark
+
+bm=$1
+ver=$2
+id=$3
+
+java -jar ../../rupee-mgr/target/rupee-mgr-0.0.1-SNAPSHOT-jar-with-dependencies.jar -s DB_ID,SCOP,${id},100,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TOP_ALIGNED,TM_SCORE > ./${bm}_${ver}/${id}.txt

### 2020-07-11 eval/results/rupee/rupee_run.sh

@@ -1,0 +1,13 @@
+#! /bin/bash
+
+bm=$1
+ver=$2
+
+# delete output directory if it exist
+[ -d ./${bm}_${ver} ] && rm -r ${bm}_${ver}
+
+# create output directory
+mkdir ./${bm}_${ver}
+
+cut -d, -f2 ../benchmarks/${bm}.txt | xargs -L1 ./rupee.sh ${bm} ${ver}
+

### 2020-07-11 eval/results/ssap/ssap_run.sh

@@ -1,0 +1,4 @@
+#! /bin/bash
+
+xargs -a ssap_input.txt -L1 -P8 ./cath-ssap --pdb-path /home/ayoub/git/rupee/data/cath/pdb/ --min-score-for-files 101
+

### 2020-07-11 eval/results/ssm/cat_results.sh

@@ -1,0 +1,11 @@
+#! /bin/bash
+
+bm=$1
+ver=$2
+st=$3
+dir=${bm}_${ver}_${st}
+
+for id in $(find ${dir} -name '*.txt' -printf '%f\n'); do
+   awk -v ver=${ver} -v st=${st} -v db_id=${id%.txt} -e 'BEGIN { OFS = ","; } $0 ~ "SCOP" { print ver, $1, db_id, $17, $5, $2, st }' ${dir}/${id}
+done;
+

### 2020-07-11 eval/results/vast/cat_results.sh

@@ -1,0 +1,11 @@
+#! /bin/bash
+
+bm=$1
+ver=$2
+st=$3
+dir=${bm}_${ver}_${st}
+
+for id in $(find ${dir} -name '*.txt' -printf '%f\n'); do
+    awk -v ver=${ver} -v st=${st} -v db_id=${id%.txt} -e 'BEGIN { FS = ","; OFS = ","; } { print ver, NR, db_id, tolower(substr($1,1,4)) substr($1,6,1), $3, $5, st } ' ${dir}/${id}
+done;
+

### 2020-07-11 figures/combined_scoring_cathedral.R

@@ -1,73 +1,0 @@
-
-library(grid)
-library(gridExtra)
-
-source('scoring.R')
-
-grid_arrange_shared_legend <-
-  function(...,
-           ncol = 3, 
-           nrow = 1, 
-           position = c("bottom", "right")) {
-    
-    plots <- list(...)
-    position <- match.arg(position)
-    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
-    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-    lheight <- sum(legend$height)
-    lwidth <- sum(legend$width)
-    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
-    gl <- c(gl, ncol = ncol, nrow = nrow)
-    
-    combined <- switch(
-      position,
-      "bottom" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight)
-      ),
-      "right" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 2,
-        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
-      )
-    )
-  }
-
-plot1 <- get_scoring_plot(
-        'CATHEDRAL',
-        'vs: CATHEDRAL\nbenchmark: casp_cathedral_d247\nRUPEE search type: SSAP-score',
-        'SSAP-score',
-        'scoring_cathedral_ssap.txt', # _ce, _fatcat, _fl, _ssap
-        c('RUPEE All-Aligned','RUPEE Top-Aligned','CATHEDRAL'), 
-        c(1, 100),
-        c(1,10,20,30,40,50,60,70,80,90,100),
-        c(60, 75) # c(0, 5), c(0.30, 0.55) or c(60, 75)
-)
-plot2 <- get_scoring_plot(
-        'CATHEDRAL',
-        'vs: CATHEDRAL\nbenchmark: casp_cathedral_d247\nRUPEE search type: Full-Length',
-        'TM-score (avg)',
-        'scoring_cathedral_fl.txt', # _ce, _fatcat, _fl, _ssap
-        c('RUPEE All-Aligned','RUPEE Top-Aligned','CATHEDRAL'), 
-        c(1, 100),
[…]

### 2020-07-11 figures/combined_scoring_mtm.R

@@ -1,63 +1,0 @@
-
-library(grid)
-library(gridExtra)
-
-source('scoring.R')
-
-grid_arrange_shared_legend <-
-  function(...,
-           ncol = 2, 
-           nrow = 1, 
-           position = c("bottom", "right")) {
-    
-    plots <- list(...)
-    position <- match.arg(position)
-    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
-    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-    lheight <- sum(legend$height)
-    lwidth <- sum(legend$width)
-    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
-    gl <- c(gl, ncol = ncol, nrow = nrow)
-    
-    combined <- switch(
-      position,
-      "bottom" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight)
-      ),
-      "right" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 2,
-        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
-      )
-    )
-  }
-
-plot1 <- get_scoring_plot(
-        'mTM-align',
-        'vs: mTM-align\nbenchmark: casp_mtm_d246\nRUPEE search type: Contained-In',
-        'TM-score (q)',
-        'scoring_mtm_ci.txt', # _rmsd, _ci
-        c('RUPEE All-Aligned','RUPEE Top-Aligned','mTM'), 
-        c(1, 100),
-        c(1,10,20,30,40,50,60,70,80,90,100),
-        c(0.10, 0.65)
-)
-plot2 <- get_scoring_plot(
-        'mTM-align',
-        'vs: mTM-align\nbenchmark: casp_mtm_d246\nRUPEE search type: RMSD',
-        'RMSD',
-        'scoring_mtm_rmsd.txt', # _rmsd, _ci
-        c('RUPEE All-Aligned','RUPEE Top-Aligned','mTM'), 
-        c(1, 10),
-        c(2,4,6,8,10),
-        c(0, 5)
-)
-
-combined <- grid_arrange_shared_legend(plot1, plot2)
-
-ggsave('combined_scoring_mtm.eps', plot = combined, width = 5.2, height = 2.4, dpi = 300)
-

### 2020-07-11 figures/combined_scoring_rupee.R

@@ -1,59 +1,0 @@
-
-library(grid)
-library(gridExtra)
-
-source('scoring_rupee.R')
-
-grid_arrange_shared_legend <-
-  function(...,
-           ncol = 2, 
-           nrow = 1, 
-           position = c("bottom", "right")) {
-    
-    plots <- list(...)
-    position <- match.arg(position)
-    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
-    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-    lheight <- sum(legend$height)
-    lwidth <- sum(legend$width)
-    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
-    gl <- c(gl, ncol = ncol, nrow = nrow)
-    
-    combined <- switch(
-      position,
-      "bottom" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight)
-      ),
-      "right" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 2,
-        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
-      )
-    )
-  }
-
-plot1 <- get_scoring_plot(
-        'All vs. Top\nbenchmark: scop_d360',
-        'scoring_rupee_scop_d360.txt',
-        c('RUPEE All-Aligned','RUPEE Top-Aligned'),
-        c(1, 100),
-        c(1,10,20,30,40,50,60,70,80,90,100),
-        c(0.85, 1.0)
-)
-plot2 <- get_scoring_plot(
-        'All vs. Top\nbenchmark: casp_d250',
-        'scoring_rupee_casp_d250.txt', 
-        c('RUPEE All-Aligned','RUPEE Top-Aligned'),
-        c(1, 100),
-        c(1,10,20,30,40,50,60,70,80,90,100),
-        c(0.4, 0.55)
-)
-
-combined <- grid_arrange_shared_legend(plot1, plot2)
-
-ggsave('combined_scoring_rupee.eps', plot = combined, width = 5.2, height = 2.4, dpi = 300)
-

### 2020-07-11 figures/combined_torsion.R

@@ -1,46 +1,0 @@
-
-library(grid)
-library(gridExtra)
-
-source('ramachandran.R')
-source('torsion.R')
-
-grid_arrange_shared_legend <-
-  function(...,
-           ncol = length(list(...)),
-           nrow = 1,
-           position = c("bottom", "right")) {
-    
-    plots <- list(...)
-    position <- match.arg(position)
-    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
-    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-    lheight <- sum(legend$height)
-    lwidth <- sum(legend$width)
-    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
-    gl <- c(gl, ncol = ncol, nrow = nrow)
-    
-    combined <- switch(
-      position,
-      "bottom" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight)
-      ),
-      "right" = arrangeGrob(
-        do.call(arrangeGrob, gl),
-        legend,
-        ncol = 2,
-        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
-      )
-    )
-  }
-
-ramachandran_plot <- get_ramachandran_plot()
-torsion_plot <- get_torsion_plot()
-
-combined <- grid_arrange_shared_legend(ramachandran_plot, torsion_plot)
-
-ggsave('combined_torsion.eps', plot = combined, width = 7, height = 3)
-

### 2020-07-11 figures/ramachandran.R

@@ -1,79 +1,0 @@
-
-library(ggplot2)
-library(plyr)
-
-get_ramachandran_plot <- function() {
-
-# clear environment
-rm(list = ls())
-
-# read in data file
-df <- read.csv('torsion.txt')
-
-# map values
-df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
-
-# reorder factor levels
-df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
-
-# color scale
-color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
-
-ramachandran_plot <- ggplot(df, aes(phi, psi, color = sse)) +
-    
-    # geoms
-    geom_point(
-        size = rel(0.01)
-    ) + 
-    
-    # scales
-    scale_x_continuous(
-        limits = c(-180,180),
-        expand = c(0,0),
-        breaks = c(-180,-90,0,90,180),
-        labels = c('-180\u00B0','-90\u00B0','0\u00B0','90\u00B0','180\u00B0')
-    ) + 
-    scale_y_continuous(
-        limits = c(-180,180),
-        expand = c(0,0),
-        breaks = c(-180,-90,0,90,180),
-        labels = c('-180\u00B0','-90\u00B0','0\u00B0','90\u00B0','180\u00B0')
-    ) + 
-    scale_color_manual(NULL, values = color_scale) + 
-    
-    # guides
-    guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
-
-    # coordinates
-    coord_fixed(
-       ratio = 1
-    ) +
-
-    # axis labels
-    labs(
-         x = expression(phi), 
-         y = expression(psi)
-    ) + 
-
-    # default theme 
-    theme_bw() +
-
-    # default override
-    theme(
-        plot.title = element_blank(), 
-        plot.margin = margin(5,0,0,0), 
-       
-        panel.grid.minor = element_blank(),
-        panel.grid.major = element_line(size = rel(0.2), color = 'grey50'),
-
-        axis.text = element_text(size = 7), 
-        axis.title = element_text(size = 8),
-        
-        legend.title = element_blank(), 
-        legend.text = element_text(size = 7),
-        legend.position = 'bottom',
-        legend.margin = margin(0,0,0,0),
-        legend.direction = 'horizontal'
-    )
-}
-

### 2020-07-11 figures/regions.R

@@ -1,115 +1,0 @@
-
-library(ggplot2)
-library(plyr)
-
-# clear environment
-rm(list = ls())
-
-# read in data files
-df <- read.csv('torsion.txt')
-lines <- read.csv('region_lines.txt')
-annotes <- read.csv('region_annotes.txt')
-
-# map values
-df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
-
-# subset data
-df <- subset(df, df$sse == 'Helix' | df$sse == 'Strand' | df$sse == 'Bend/Coil')
-
-# reorder factor levels
-df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
-
-# wrap and translate torsion angles
-df$phi <- ifelse(df$phi < 0, df$phi + 360, df$phi)
-df$phi <- df$phi + 200
-
-# color scale
-color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
-
-ggplot(df, aes(phi, psi, color = sse)) +
-    
-    # geoms
-    geom_point(
-        size = rel(0.01)
-    ) + 
-    geom_vline(
-        xintercept = seq(200, 560, by = 90), 
-        colour = 'grey50', 
-        size = rel(0.2)
-    ) +
-    geom_hline(
-        yintercept = seq(-180, 180, by = 30), 
-        colour = 'grey50', 
-        size = rel(0.2)
-    ) +
-    geom_segment(
-        data = lines,
-        size = rel(0.4),
-        lineend = 'square',
-        aes(x, y, xend = xend, yend = yend),
-        inherit.aes = FALSE
-    ) + 
-    geom_text(
-        data = annotes, 
-        size = 3, 
-        color = 'black',
-        aes(x = phi, y = psi, label = label)
-    ) +
-    
-    # scales
-    scale_x_continuous(
-        limits = c(0,560),
-        expand = c(0,0),
-        breaks = c(200,290,380,470,560),
-        labels = c('0\u00B0','90\u00B0','\u00B1180\u00B0','-90\u00B0','0\u00B0')
-    ) + 
-    scale_y_continuous(
-        limits = c(-180,180),
-        expand = c(0,0),
-        breaks = c(-150,-120,-90,-60,-30,0,30,60,90,120,150,180),
[…]

### 2020-07-11 figures/scoring.R

@@ -1,83 +1,0 @@
-
-library(ggplot2)
-library(plyr)
-
-# clear environment
-rm(list = ls())
-
-get_scoring_plot <- function(p_comp_to, p_title, p_ylab, p_file, p_levels, p_xlimits, p_xbreaks, p_ylimits) {
-
-    # read in data files
-    df <- read.csv(p_file)
-
-    # reorder factor levels 
-    df$app <- factor(df$app, levels = p_levels)
-
-    # *** plot
-
-    plot <- 
-        
-        ggplot(df, aes(n, avg_cume_score, group = app, color = app, linetype = app)) +
-        
-        # geoms
-        geom_line(
-            size = rel(0.5)
-        ) + 
-
-        # scales        
-        scale_color_manual(
-            values = c("#e41a1c","#377eb8","#4daf4a"),
-            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned", p_comp_to)
-        ) + 
-        scale_linetype_manual(
-            values = c("solid","dashed","dotted"),
-            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned", p_comp_to)
-        ) + 
-        scale_x_continuous(
-            limits = p_xlimits,
-            breaks = p_xbreaks
-        ) + 
-        scale_y_continuous(
-            limits = p_ylimits
-        ) + 
-
-        # guides
-        guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
-
-        # axis label
-        ylab(p_ylab) + 
-
-        # title
-        ggtitle(p_title)
-
-    # *** theme
-    
-    theme <-  
-
-        # default theme 
-        theme_bw() +
-
-        # default override
-        theme(
-            plot.title = element_text(size = 7),
-            plot.margin = margin(5,15,0,0), 
-
-            panel.grid = element_blank(),
-            panel.spacing = unit(4,'mm'),
-            
-            axis.text = element_text(size = 7), 
-            axis.title.x = element_blank(), 
-            axis.title.y = element_text(size = 7),
-            
-            legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
-            legend.title = element_blank(), 
-            legend.position = 'bottom',
-            legend.direction = 'horizontal',
-            legend.spacing = unit(0,'mm')
-        ) 
-
-    plot + theme
-}
-
-
-

### 2020-07-11 figures/scoring_rupee.R

@@ -1,83 +1,0 @@
-
-library(ggplot2)
-library(plyr)
-
-# clear environment
-rm(list = ls())
-
-get_scoring_plot <- function(p_title, p_file, p_levels, p_xlimits, p_xbreaks, p_ylimits) {
-
-    # read in data files
-    df <- read.csv(p_file)
-
-    # reorder factor levels 
-    df$app <- factor(df$app, levels = p_levels)
-
-    # *** plot
-
-    plot <- 
-        
-        ggplot(df, aes(n, avg_cume_score, group = app, color = app, linetype = app)) +
-        
-        # geoms
-        geom_line(
-            size = rel(0.5)
-        ) + 
-
-        # scales        
-        scale_color_manual(
-            values = c("#e41a1c","#377eb8"),
-            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned")
-        ) + 
-        scale_linetype_manual(
-            values = c("solid","dashed"),
-            labels = c("RUPEE All-Aligned","RUPEE Top-Aligned")
-        ) + 
-        scale_x_continuous(
-            limits = p_xlimits,
-            breaks = p_xbreaks
-        ) + 
-        scale_y_continuous(
-            limits = p_ylimits
-        ) + 
-
-        # guides
-        guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
-
-        # axis label
-        ylab('TM-score (avg)') + 
-
-        # title
-        ggtitle(p_title)
-
-    # *** theme
-    
-    theme <-  
-
-        # default theme 
-        theme_bw() +
-
-        # default override
-        theme(
-            plot.title = element_text(size = 7),
-            plot.margin = margin(5,15,0,0), 
-
-            panel.grid = element_blank(),
-            panel.spacing = unit(4,'mm'),
-            
-            axis.text = element_text(size = 7), 
-            axis.title.x = element_blank(), 
-            axis.title.y = element_text(size = 7),
-            
-            legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
-            legend.title = element_blank(), 
-            legend.position = 'bottom',
-            legend.direction = 'horizontal',
-            legend.spacing = unit(0,'mm')
-        ) 
-
-    plot + theme
-}
-
-
-

### 2020-07-11 figures/scoring_test.R

@@ -1,42 +1,0 @@
-
-source('scoring.R')
-
-#plot <- get_scoring_plot(
-#        'vs. mTM',
-#        'scoring_mtm_ci.txt', # _rmsd, _ci
-#        c('RUPEE All-Aligned','RUPEE Top-Aligned','mTM'), 
-#        c(1, 100),
-#        c(1,10,20,30,40,50,60,70,80,90,100),
-#        c(0.20, 0.80), # c(0, 5) or c(0.20, 0.80)
-#        FALSE
-#)
-#plot <- get_scoring_plot(
-#        'vs. SSM',
-#        'scoring_ssm_q.txt', # _ce, _fatcat, _fl, _q
-#        c('RUPEE All-Aligned','RUPEE Top-Aligned','SSM'), 
-#        c(1, 100),
-#        c(1,10,20,30,40,50,60,70,80,90,100),
-#        c(0.05, 0.25), # c(0, 6), c(0.25, 0.55) or c(0.05, 0.25)
-#        FALSE
-#)
-#plot <- get_scoring_plot(
-#        'vs. CATHEDRAL',
-#        'scoring_cathedral_fl.txt', # _ce, _fatcat, _fl, _ssap
-#        c('RUPEE All-Aligned','RUPEE Top-Aligned','CATHEDRAL'), 
-#        c(1, 100),
-#        c(1,10,20,30,40,50,60,70,80,90,100),
-#        c(0.3, 0.55), # c(0, 5), c(0.30, 0.55) or c(60, 75)
-#        FALSE
-#)
-plot1 <- get_scoring_plot(
-        'vs. VAST',
-        'scoring_vast_fl.txt', # _ce, _fatcat, _fl
-        c('RUPEE All-Aligned','RUPEE Top-Aligned','VAST'), 
-        c(1, 100),
-        c(1,10,20,30,40,50,60,70,80,90,100),
-        c(0.1, 0.6), # c(0, 5) or c(0.1, 0.6)
-        TRUE
-)
-
-ggsave('scoring_test.eps', plot = plot, width = 3.25, height = 3.25, dpi = 300)
-

### 2020-07-11 figures/torsion.R

@@ -1,95 +1,0 @@
-
-library(ggplot2)
-library(plyr)
-
-get_torsion_plot <- function () {
-
-# clear environment
-rm(list = ls())
-
-# read in data files
-df <- read.csv('torsion.txt')
-
-# map values
-df$sse <- mapvalues(df$sse, from = c('Turn', 'Bridge', 'Bend', 'Coil'), to = c('Helix', 'Strand', 'Bend/Coil', 'Bend/Coil'))
-
-# reorder factor levels
-df$sse <- factor(df$sse, levels = c('Helix', 'Strand', 'Bend/Coil'))
-
-# color scale
-color_scale <- c('Helix' = 'red', 'Strand' = 'green', 'Bend/Coil' = 'black')
-
-# wrap and translate torsion angles
-df$phi <- ifelse(df$phi < 0, df$phi + 360, df$phi)
-df$phi <- df$phi + 200
-
-torsion_plot <- ggplot(df, aes(phi, psi, color = sse)) +
-    
-    # geoms
-    geom_point(
-        size = rel(0.01)
-    ) + 
-    geom_vline(
-        xintercept = seq(200, 560, by = 90), 
-        colour = 'grey50', 
-        size = rel(0.2)
-    ) +
-    geom_hline(
-        yintercept = seq(-180, 180, by = 30), 
-        colour = 'grey50', 
-        size = rel(0.2)
-    ) +
-    
-    # scales
-    scale_x_continuous(
-        limits = c(0,560),
-        expand = c(0,0),
-        breaks = c(200,290,380,470,560),
-        labels = c('0\u00B0','90\u00B0','\u00B1180\u00B0','-90\u00B0','0\u00B0')
-    ) + 
-    scale_y_continuous(
-        limits = c(-180,180),
-        expand = c(0,0),
-        breaks = c(-150,-120,-90,-60,-30,0,30,60,90,120,150,180),
-        labels = c('-150\u00B0','-120\u00B0','-90\u00B0','-60\u00B0','-30\u00B0','0\u00B0','30\u00B0','60\u00B0','90\u00B0','120\u00B0','150\u00B0','\u00B1180\u00B0')
-    ) + 
-    scale_color_manual(NULL, values = color_scale) + 
-    
-    # guides
-    guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
-
-    # coordinates 
-    coord_polar(
-       theta = 'y',
-       direction = -1
-    ) +
-
-    # axis labels
[…]

### 2020-07-11 pymol/rupee.py

@@ -1,28 +1,0 @@
-import csv
-
-from pymol import stored
-from pymol import cmd
-
-# to call
-# 1. set label_size 20
-# 2. label_residues 1nycA00, color
-
-def label_residues(entity, color):
-
-    with open(entity + '.labels') as label_file:
-        reader = csv.reader(label_file)
-        labels = {int(rows[0]):rows[1] for rows in reader}
-
-    selection_model = '/' + entity + '////ca' 
-    selection_atom = '/' + entity + '///{0}/{1}'
-
-    cmd.set('label_color', color, selection_model)
-
-    model = cmd.get_model(selection_model, 1)
-    for i in range(0, len(model.atom)):
-        residue_number = int(model.atom[i].resi)
-        if residue_number in labels:
-            cmd.label(selection_atom.format(residue_number, model.atom[i].name), labels[residue_number])
-
-# register
-cmd.extend(label_residues)

### 2020-07-11 results/cathedral/cat_results.sh

@@ -1,16 +1,0 @@
-#! /bin/bash
-
-bm=$1
-ver=$2
-dir=${bm}_${ver}
-
-for id in $(find ${dir} -name '*.txt' -printf '%f\n'); do
-    tail ${dir}/${id} -n+8 | awk -v ver=${ver} -v id=${id%.txt} \
-        'BEGIN { 
-            FS = "[ \n]+"; 
-            RS = "Show related domains\n"; 
-            OFS = "," 
-        } 
-        { print ver, NR, id, $1, $4, $5 }'
-done;
-

### 2020-07-11 results/rupee/casp.sh

@@ -1,10 +1,0 @@
-#! /bin/bash
-
-# this file needs to be edited for each type of benchmark
-
-bm=$1
-ver=$2
-id=$3
-
-java -jar ../../rupee-mgr/target/rupee-mgr-0.0.1-SNAPSHOT-jar-with-dependencies.jar -s UPLOAD,CHAIN,../../data/casp/eu_preds/${id}.pdb,400,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,ALL_ALIGNED,FULL_LENGTH > ./${bm}_${ver}/${id}.txt
-

### 2020-07-11 results/rupee/casp_run.sh

@@ -1,13 +1,0 @@
-#! /bin/bash
-
-bm=$1
-ver=$2
-
-# delete output directory if it exist
-[ -d ./${bm}_${ver} ] && rm -r ${bm}_${ver}
-
-# create output directory
-mkdir ./${bm}_${ver}
-
-cut -d, -f2 ../benchmarks/${bm}.txt | xargs -L1 ./casp.sh ${bm} ${ver}
-

### 2020-07-11 results/rupee/cat_results.sh

@@ -1,10 +1,0 @@
-#! /bin/bash
-
-bm=$1
-ver=$2
-dir=${bm}_${ver}
-
-for id in $(find ${dir} -name '*.txt' -printf '%f\n'); do
-    head -n 100 ${dir}/${id} | xargs -L1 printf "%s,%s\n" ${ver}
-done;
-

### 2020-07-11 results/rupee/rupee.sh

@@ -1,9 +1,0 @@
-#! /bin/bash
-
-# this file needs to be edited for each type of benchmark
-
-bm=$1
-ver=$2
-id=$3
-
-java -jar ../../rupee-mgr/target/rupee-mgr-0.0.1-SNAPSHOT-jar-with-dependencies.jar -s DB_ID,SCOP,${id},100,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TOP_ALIGNED,TM_SCORE > ./${bm}_${ver}/${id}.txt

### 2020-07-11 results/rupee/timing_run.sh

@@ -1,7 +1,0 @@
-#! /bin/bash
-
-bm=$1
-st=$2
-
-cut -d, -f2 ../benchmarks/${bm}.txt | xargs -L1 ./timing.sh ${bm} ${st}
-

### 2020-10-01 eval/figures/combined_scoring_ssm.R
results

@@ -5,7 +5,7 @@ source('scoring.R')
 
 plot <- get_scoring_plot(
         'SSM',
-        'vs: SSM\nbenchmark: casp_ssm_d248\nstructure database: SCOP v1.73\nRUPEE search type: Q-score',
+        'RUPEE vs: SSM\nbenchmark: casp_ssm_d248\nstructure database: SCOP v1.73\nRUPEE search type: Q-score',
         'Q-score',
         'scoring_ssm_q.txt', 
         c('All','Top','Fast','SSM'), 

### 2020-10-01 eval/figures/combined_scoring_vast.R

@@ -5,7 +5,7 @@ source('scoring.R')
 
 plot <- get_scoring_plot(
         'VAST',
-        'vs: VAST\nbenchmark: casp_vast_d199\nstructure database: PDB chains\nRUPEE search type: Full-Length', 
+        'RUPEE vs: VAST\nbenchmark: casp_vast_d199\nstructure database: PDB chains\nRUPEE search type: Full-Length', 
         'TM-score (avg)',
         'scoring_vast_fl.txt', 
         c('All','Top','Fast','VAST'), 

### 2020-10-01 eval/figures/scoring.R

@@ -42,6 +42,7 @@ get_scoring_plot <- function(p_comp_to, p_title, p_ylab, p_file, p_levels, p_xli
         guides(linetype = guide_legend(override.aes = list(size = rel(0.5)))) + 
 
         # axis label
+        xlab("results rank") + 
         ylab(p_ylab) + 
 
         # title
@@ -57,14 +58,12 @@ get_scoring_plot <- function(p_comp_to, p_title, p_ylab, p_file, p_levels, p_xli
         # default override
         theme(
             plot.title = element_text(size = 7),
-            plot.margin = margin(5,15,0,0), 
+            plot.margin = margin(5,15,0,5), 
 
             panel.grid = element_blank(),
-            panel.spacing = unit(4,'mm'),
             
             axis.text = element_text(size = 7), 
-            axis.title.x = element_blank(), 
-            axis.title.y = element_text(size = 7),
+            axis.title = element_text(size = 7), 
             
             legend.text = element_text(size = 7, margin = margin(0,10,0,0)),
             legend.title = element_blank(), 

### 2020-10-01 eval/figures/combined_response_rupee.R
response times

@@ -1,0 +1,55 @@
+
+library(grid)
+library(gridExtra)
+
+rm(list = ls())
+
+source('response_rupee.R')
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = 2, 
+           nrow = 1, 
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+  }
+
+mtm_plot <- get_timing_plot(
+        'RUPEE vs: RUPEE\nbenchmark: casp_d250\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
+        'response_rupee_casp.txt',
+        c('All','Top','Fast','Optimal')
+)
+ssm_plot <- get_timing_plot(
+        'RUPEE vs: RUPEE\nbenchmark: scop_d360\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
+        'response_rupee_scop.txt',
+        c('All','Top','Fast','Optimal')
+)
+
+combined <- grid_arrange_shared_legend(mtm_plot, ssm_plot)
+
+ggsave('combined_response_rupee.eps', plot = combined, width = 7, height = 2.5)
+

### 2020-10-01 eval/figures/response_rupee.R

@@ -2,84 +2,75 @@
 library(ggplot2)
 library(plyr)
 
-# clear environment
-rm(list = ls())
+get_timing_plot <- function(p_title, p_file, p_levels) {
 
-# read in data files
-df <- read.csv('response_rupee.txt')
+    # read in data file
+    df <- read.csv(p_file)
+
+    # reorder factor levels
+    df$app <- factor(df$app, levels = p_levels)
+
+    # *** plot
+
+    plot <- 
+
+        ggplot(df, aes(residue_count, time, group = app, color = app)) +
+            
+        # geoms
+        geom_point(
+            size = rel(0.30)
+        ) + 
+        geom_smooth(     
+            size = rel(0.30),
+            show.legend = FALSE
+        ) + 
+
+        # scales
+        scale_color_manual(
+            values = c("#e41a1c","#377eb8","#984ea3","#4daf4a"),
+            labels = c("All","Top","Fast","Optimal")
+        ) + 
+        scale_y_continuous(
+            trans = "log10",
+            limits = c(1,10000)
+        ) + 
     
-# reorder factor levels 
-df$app <- factor(df$app, levels = c('RUPEE Top-Aligned', 'RUPEE Test', 'mTM', 'SSM'))
+        # guides
+        guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
 
-# *** plot
-
-plot <- 
-
-    ggplot(df, aes(gram_count, timing, group = app, color = app)) +
+        # axis labels
+        labs(
+             x = 'residue count', 
+             y = 'response time (seconds)'
+        ) + 
         
-    # geoms
-    geom_point(
-        size = rel(0.5)
-    ) + 
-    geom_smooth(     
-        size = rel(0.5),
-        show.legend = FALSE
-    ) + 
+        # title
+        ggtitle(p_title)
 
-    # scales
-    scale_color_manual(
-        values = c('#e41a1c', '#4daf4a', '#984ea3', '#ff7f00'),
-        labels = c('RUPEE Top-Aligned', 'RUPEE Test', 'mTM', 'SSM')
-    ) + 
-    scale_y_continuous(
-        trans = "log10",
-        limits = c(1,10000)
-    ) + 
-
-    # guides
-    guides(color = guide_legend(override.aes = list(size = rel(1)))) + 
-
-    # axis labels
-    labs(
-         x = 'residue count', 
-         y = 'response time (seconds)'
-    ) + 
+    # *** theme
[…]

### 2020-10-06 eval/figures/combined_response.R
full name

@@ -41,7 +41,7 @@ grid_arrange_shared_legend <-
 mtm_plot <- get_timing_plot(
         'RUPEE vs: mTM-align\nbenchmark: casp_d250\nstructure database: PDB chains\nRUPEE search type: Full-Length',
         'response_mtm.txt',
-        c('All','Top','Fast', 'mTM')
+        c('All','Top','Fast', 'mTM-align')
 )
 ssm_plot <- get_timing_plot(
         'RUPEE vs: SSM\nbenchmark: casp_ssm_d248\nstructure database: SCOP v1.73\nRUPEE search type: Full-Length',

### 2020-10-06 eval/figures/combined_scoring_mtm.R

@@ -4,11 +4,11 @@ rm(list = ls())
 source('scoring.R')
 
 plot <- get_scoring_plot(
-        'mTM',
+        'mTM-align',
         'RUPEE vs: mTM-align\nbenchmark: casp_d250\nstructure database: PDB chains\nRUPEE search type: Contained-In',
         'TM-score (q)',
         'scoring_mtm_ci.txt',
-        c('All','Top','Fast','mTM'), 
+        c('All','Top','Fast','mTM-align'), 
         c(1, 100),
         c(1,10,20,30,40,50,60,70,80,90,100),
         c(0.10, 0.65)

### 2020-10-06 eval/figures/response.R

@@ -28,7 +28,7 @@ get_timing_plot <- function(p_title, p_file, p_levels) {
         # scales
         scale_color_manual(
             values = c("#e41a1c","#377eb8","#984ea3","#4daf4a"),
-            labels = c("All","Top", "Fast", "mTM (left), SSM (right)")
+            labels = c("All","Top", "Fast", "mTM-align (left), SSM (right)")
         ) + 
         scale_y_continuous(
             trans = "log10",

### 2020-10-07 eval/figures/combined_response_rupee.R
results

@@ -38,18 +38,18 @@ grid_arrange_shared_legend <-
     )
   }
 
-mtm_plot <- get_timing_plot(
-        'RUPEE vs: RUPEE\nbenchmark: casp_d250\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
-        'response_rupee_casp.txt',
-        c('All','Top','Fast','Optimal')
-)
-ssm_plot <- get_timing_plot(
-        'RUPEE vs: RUPEE\nbenchmark: scop_d360\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
+plot1 <- get_timing_plot(
+        'RUPEE vs: Exhaustive\nbenchmark: scop_d360\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
         'response_rupee_scop.txt',
-        c('All','Top','Fast','Optimal')
+        c('All','Top','Fast','Exhaustive')
+)
+plot2 <- get_timing_plot(
+        'RUPEE vs: Exhaustive\nbenchmark: casp_d250\nstructure database: SCOP v2.07\nRUPEE search type: Full-Length',
+        'response_rupee_casp.txt',
+        c('All','Top','Fast','Exhaustive')
 )
 
-combined <- grid_arrange_shared_legend(mtm_plot, ssm_plot)
+combined <- grid_arrange_shared_legend(plot1, plot2)
 
 ggsave('combined_response_rupee.eps', plot = combined, width = 7, height = 2.5)
 

### 2020-10-07 eval/figures/response_rupee.R

@@ -28,7 +28,7 @@ get_timing_plot <- function(p_title, p_file, p_levels) {
         # scales
         scale_color_manual(
             values = c("#e41a1c","#377eb8","#984ea3","#4daf4a"),
-            labels = c("All","Top","Fast","Optimal")
+            labels = c("All","Top","Fast","Exhaustive")
         ) + 
         scale_y_continuous(
             trans = "log10",

### 2020-10-07 eval/figures/scoring_rupee.R

@@ -24,11 +24,11 @@ get_scoring_plot <- function(p_title, p_file, p_levels, p_xlimits, p_xbreaks, p_
         # scales        
         scale_color_manual(
             values = c("#e41a1c","#377eb8","#984ea3","#4daf4a"),
-            labels = c("All","Top","Fast","Optimal")
+            labels = c("All","Top","Fast","Exhaustive")
         ) + 
         scale_linetype_manual(
             values = c("solid","dashed","dotdash","dotted"),
-            labels = c("All","Top","Fast","Optimal")
+            labels = c("All","Top","Fast","Exhaustive")
         ) + 
         scale_x_continuous(
             limits = p_xlimits,
